### 2019-03-19 paper.tex
Initial Overleaf Import

\documentclass[10pt,twocolumn,twoside]{genpaper}
\usepackage[numbers,sort&compress]{natbib}

\newcommand{\npscarf}{$\mathtt{npScarf}$}
\newcommand{\npscarfg}{$\mathtt{npScarf\_wag}$}
\newcommand{\npreader}{$\mathtt{npReader}$}
\newcommand{\npanalysis}{$\mathtt{npAnalysis}$}
\newcommand{\npbarcode}{$\mathtt{npBarcode}$}
\newcommand{\npgraph}{$\mathtt{npGraph}$}
\newcommand{\canu}{$\mathtt{Canu}$}
\newcommand{\unicycler}{$\mathtt{Unicycler}$}
\newcommand{\spades}{$\mathtt{SPAdes}$}
\newcommand{\albacore}{$\mathtt{Albacore}$}
\newcommand{\racon}{$\mathtt{Racon}$}
\newcommand{\metrichor}{$\mathtt{Metrichor}$}
\newcommand{\minimap}{$\mathtt{minimap2}$}
\newcommand{\miniasm}{$\mathtt{miniasm}$}
\newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}

\newcommand{\ec}{\emph{E.~coli}}
\newcommand{\sce}{\emph{S.~cerevisae}}
\newcommand{\kp}{\emph{K.~pneumoniae}}

\newcommand{\IE}{\emph{i.e.}}
\newcommand{\EG}{\emph{e.g.}}
\newcommand{\review}[1]{\textcolor{red}{#1}}

\newcommand{\cthead}[2]{\multicolumn{#1}{c}{\textbf{#2}}}
\definecolor{Gray}{gray}{0.9}
\newcommand{\cir}{$^\ast$}
\newcommand{\bres}[1]{{\bf #1}}

\usepackage{pdfpages} 
\usepackage{mathtools}
\usepackage{play}
\usepackage{makeidx}
\usepackage{xcolor,colortbl}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{pdflscape}

\usepackage{amsmath,amsfonts,amssymb} % this is handy for mathematicians and physicists
			      % see http://www.ams.org/tex/amslatex.html

% \usepackage{showkeys} % this shows what labels you are using for cross
		      % references

\usepackage{graphicx} % standard graphics package for inclusion of
		      % images and eps files into LaTeX document

\usepackage{multirow}

% For pseudocode
\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
% For code embedding (Bash, Java...)
\usepackage{listings}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}

\usepackage{float}
\usepackage[caption = false]{subfig}
% this code hacked from that of R Chandrasekhar from UWA
\newif\ifpdf
\ifx\pdfoutput\undefined
	\pdffalse    % we are not running pdfLaTeX
\else
	\pdfoutput=1 % we are running pdfLaTeX
	\pdftrue
\fi

\ifpdf
	\DeclareGraphicsExtensions{.pdf}  % this command defined in graphicx
	\pdfcompresslevel=9  % 0: no compression, 9: highest compression
			     % or, set compress_level 9 in file pdftex.cfg
\else
	\DeclareGraphicsExtensions{.ps}
\fi

\usepackage{xr}
\externaldocument{supplementary.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some functions provided  by the class

%Display line numbers on the margins
\lineno

%Display watermark DRAFT
%\watermark{DRAFT}

%% use \onecolumn for onecolumn paper
\onecolumn

%Set the title
\title{Online resolving assembly graph by long reads data}

%Set the short tittle
\shorttitle{An awesome paper}

%Authors
\author[1,$\dag$, $\ast$]{Author First}
\author[1,$\dag$]{Author Two} 
\author[1,2]{Author Three}
\author[1,2,$\ast$]{Author Last}

%Affiliation
\affil[1]{Affiliation One}
\affil[2]{Affiliation Two}

%Display equal author textrent focus is developing methods to determine evolutionary relationships, primarily usi
\equalauthors{\textsuperscript{$\dag$}These authors contributed equally to
this work.}

%Display correspondingauthor text 
\correspondingauthor{
\textsuperscript{$\ast$}To whom correspondence should be addressed. E-mails:
author.last\@email.com,author.first\@email.com}

%Display ``This manuscript was compiled on XXXX''
\compiledate

%Set abstract (see below)
\abstract{This is abstract}

%Set keywords
\keywords{Keyword 1, Keyword 2,Keyword 3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%Abstract and keywords have to be defined before \maketitle
\maketitle
\thispagestyle{fancy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
% \begin{itemize}
% \item The importance of having a real-time assembler for bacterial and small genomes: e.g. npscarf 
% \item The difficulty to resolve assembly graph in real-time.
% \item Available hybrid assembly methods using long reads: unicycler, ...
% \item an online algorithm to resolve assembly graph by long reads is needed, ...
% \item Requirements
%     \begin{itemize}
%     \item Support streaming: efficient with high yield (armortized analysis)
%     \item Statistically robust: online modification of the dynamic graph, back tracking edge deletion...
%     \item Standardisation : output GFA in real-time
%     \end{itemize}
% \end{itemize}
Streaming assembly methods have been proven to be useful in saving time and resources compared to the traditional batch algorithms with examples included \EG $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}. The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed. This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a DBG construction while waiting for the data being retrieved.

\npscarf{}, on the other hand, works on the available short-read assembly to scaffold the contigs using nanopore sequencing which is well-known by the real-time property. The completion of genome assembly along with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.  
However, due to the greedy approach of a streaming algorithm, as well as being an alignment-based-only scaffolding mechanism, running the tool with default settings suffers from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. In many case, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
To tackle the quality issue while maintaining its streaming execution, an assembly graph processing system is investigated as it would provide an additional high-quality source of linking information for the assembly operations.

After the construction of an assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained. In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
While the later approach employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal. For that reason, the first direction is more suitable for a real-time pipeline.

However, the challenges to adapt this approach into a real-time mechanism are obvious and mainly come from the heavy path-finding task and the complication of self-improvement step which is critical to a streaming algorithm. 
A modified DFS algorithm and a voting system with accumulating scores calculation has been implemented to overcome these issues.
This results in \npgraph{}, an user-friendly tool with GUI that can traverse the assembly graph and scaffold its components in real-time as long as the nanopore sequencing process is running and continuously generating long reads.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{\npgraph{} -- a tool to resolve assembly graph in real-time}
\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g. \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed. These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

\begin{figure}[!hpt]
\centering
\parbox{\textwidth}{
    \parbox{.57\textwidth}{
        \subfloat{\includegraphics[width=\hsize]{images/dashboard.png}}
    }
    \hskip1em
    \parbox{.44\textwidth}{%
        \subfloat{\includegraphics[width=\hsize]{images/graph-view.png}}
        \vskip1em
        \subfloat{\includegraphics[width=\hsize]{images/console-view.png}}  
    }
}
\caption[\npgraph{} user interface]{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}). The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}). From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
\label{figure:npgraph_gui}
\end{figure}

The GUI includes the dashboard for control the settings of the program and another pop-up window for a simple visualization of the assembly graph in real-time (Figure~\ref{figure:npgraph_gui}).
In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks. The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format. Another option is to run the alignment independently and provide SAM/BAM input for the next stage of bridging and assembly. This stage is controlled by buttons in box \textbf{4}: the START button ignites the process while the STOP button can prematurely terminate it and output the assembly result till that moment. The plots from the right panel (\textbf{5}) depicts real-time statistics of the assembly contigs inferred from the graph.
From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements. The number of different colors (other than white) indicates the amount of abundant groups being detected as population bins (\EG{} chromosome versus different plasmids, or different bins in metagenomics).

A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is similar to the previous developed pipelines~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.

\subsection{Hybrid assembly for synthetic data sets}
To evaluate the performance of the method, \npgraph{} was benchmarked against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on the latter's testing data~ \cite{Wick2017unicycler} . This data set were simulations of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references. 
Specifically, the synthetic Illumina data was generated by using a wrapper script of ART~\cite{HuangLMM2012} that allows uniform coverage for circular genome sequencing with justifiable depths.
PBSIM~\cite{OnoAH2012}, on the other hand, was used to simulate the long reads.

There were three settings for each of the synthetic raw data (\emph{good, medium, bad}) corresponding to the quality, yield and length of reads being generated. 
In the SGS simulation, the \emph{bad} data consist of 100bp paired-end reads with low and uneven coverage (40X) leading to many dead ends in the assembly graph due to missing regions in the genome. 
The read length was 125bp in the \emph{medium} setting with better depth distributions that could cover the genome better. 
Finally, the \emph{good} option provided best data sets with 150bp of read length and 100X coverage.
While the quality of SGS reads would determine the assembly graph nature, the nanopore data plays critical role in graph resolving.
The three settings leveled up the depth (8X, 16X, 32X) and at the same time, average length ($5$Kbp, $10$Kbp, $20$Kbp) and maximum identities (90\% ,95\% ,98\%) respectively.
We only considered the \emph{good} configurations of both platforms for the sequence data being tested.
Also, since the other comparative tools do not support streaming assembly, there were only batch-mode runs being carried out and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

\LTcapwidth=\linewidth
% \footnotesize
\begin{longtable}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
\caption[Comparison of assemblies using \npgraph{} and other comparative methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and the comparative methods on 5 synthetic data sets taken from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\

 \toprule
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mb)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kb)} &  
    \cthead{3}{(CPU hrs)} \\
\toprule    
\endfirsthead

\multicolumn{10}{c}%
{{\tablename\ \thetable{} -- continued from previous page}} \\
 \toprule
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mb)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kb)} &  
    \cthead{3}{(CPU hrs)} \\
\toprule    
\endhead

\hline \multicolumn{10}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

\rowcolor{Gray} \multicolumn{10}{l}
{ random sequence with repeats} \\*  
 & SPAdes  & 3.928 & 226  & 40.5  &  0 &  0.00 &  0.95 &  &  \\*
 & SPAdes-Hybrid  & 4.109 & 3  & 4,000.0  & 0  & 0.85  & 1.196  &  &  \\*
 & Unicycler  & 4.110 & 3  & 4,000.0  &  0 &  0.47 & 6.783  &  &  \\*
 & npScarf  & 4.251 &  9 & 3,952.2  &  27 &  8.74 &  0.95 & + & 0.39 \\*
 & npScarf\_wag & 4.554 & 9  &  3,999.6 &  37 &  6.16 &  0.95 & + &  0.45\\*
 & npGraph (bwa)  & 4.110 & 3  & 4,000.0  & 0  &  0.47 &  0.95 & + &  0.33\\*
 & ngGraph (minimap2)  & 4.110 & 3  & 4,000.0  & 0  & 0.47  &  0.95 & + &  0.02\\
\rowcolor{Gray} \multicolumn{10}{l}
{\emph{Mycobacterium tuberculosis} H37Rv} \\*  
 & SPAdes  & 4.371 & 114  &  125.5 &  1 & 1.51  &  1.55 &  &  \\*
 & SPAdes-Hybrid  & 4.411 & 1  & 4,411.2  & 0  & 1.73  & 1.68  &  &  \\*
 & Unicycler  & 4.412 &  1 &  4,411.5 & 0  &  2.56 &  6.36 &  &  \\*
 & npScarf  & 4.446 & 4  & 4,389.9  & 12  &  11.41 & 1.55  & + & 0.78 \\*
 & npScarf\_wag  & 4.408 & 1  & 4,407.6  &  2 &  7.01 & 1.55  & + & 0.79 \\*
 & npGraph (bwa)  & 4.411 &  1 & 4,411.6  &  0 & 7.28  &  1.55 & + & 0.63 \\*
 & ngGraph (minimap2)  & 4.411 & 1 & 4,411.4  &  0 &  7.01 & 1.55  & + &  0.02\\
\rowcolor{Gray} \multicolumn{10}{l}
{\ec{} O25b H4-ST131} \\*  
 & SPAdes  & 5.173 &  159 & 191.0  &  1 &  1.69 & 1.26  &  &  \\*
 & SPAdes-Hybrid  & 5.249 &  7 &  5,109.6 & 0  & 2.65  & 1.40  &  &  \\*
 & Unicycler  & 5.249 &  3 & 5,109.8  &  0 &  4.29 &  4.70 &  &  \\*
 & npScarf  & 5.354 & 7  & 5,087.5  &  14 & 29.12  &  1.26 & + &  0.78\\*
 & npScarf\_wag  & 5.413 &  7 & 5,108.1  & 6  &  30.29 & 1.26  & + & 0.78 \\*
 & npGraph (bwa)  & 5.252 & 3  &  5,112.3 &  0 & 16.37  & 1.26  & + &  0.66\\*
 & ngGraph (minimap2)  & 5.250 & 3  & 5,111.1  & 0  & 14.61  &  1.26 & + & 0.03 \\
\rowcolor{Gray} \multicolumn{10}{l}
{\emph{Streptococcus suis} BM407} \\*  
 & SPAdes  & 2.119 &  81 &  131.0 & 0  & 3.84  & 0.59  &  &  \\*
 & SPAdes-Hybrid  & 2.147 & 48  &  1,438.0 &  0 &  0.98 & 0.65  &  &  \\*
 & Unicycler  & 2.171 &  2 &  2,146.2 & 0  &  2.99 &  2.58  &  &  \\*
 & npScarf  & 2.220 &  4 &  2,120.0  & 9  & 97.20  & 0.59 & + & 0.31 \\*
 & npScarf\_wag  & 2.245 & 4  &  2,128.3  & 3  &  89.64 & 0.59 & + &  0.31\\*
 & npGraph (bwa)  & 2.167 & 6  & 2,146.7  &  0 &  26.77 & 0.59  & + &  0.21\\*
 & ngGraph (minimap2)  & 2.167 & 6  &  2,146.2 &  0 & 22.53  &  0.59 & + & 0.01 \\
\rowcolor{Gray} \multicolumn{10}{l}
{\emph{Acinetobacter} AB30} \\*  
 & SPAdes  & 4.134 & 265  & 42.5  &  0 &  3.23 & 0.95  &  &  \\*
 & SPAdes-Hybrid  & 4.287 & 49  &  3,308.0 &  0 & 5.04  & 1.84  &  &  \\*
 & Unicycler  & 4.333 & 1  &  4,333.0 &  1 & 6.95  &  5.27 &  &  \\*
 & npScarf  & 4.595 & 11  & 4,299.7  & 1  & 120.99  & 0.95  & + & 0.45 \\*
 & npScarf\_wag  & - & -  &  - & -  &  - &  - &  &  \\*
 & npGraph (bwa)  & 4.317 & 6  &  2,766.9 & 1  &  39.82 &  0.95 & + & 0.41 \\*
 & ngGraph (minimap2)  & 4.337 & 1  &  4,336.8 & 0  & 24.71  & 0.95  & + & 0.03 \\
\end{longtable}

\normalsize

Table~\ref{table:npgraph_compare} shows evaluation results for 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
On the other hand, \npgraph{} can use 2 different aligners, \bwa{} and \minimap{}, for its bridging phase thus both practices were included in this comparison.

In general, the graph integrated version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
The only exception where the number of mis-assemblies being increased was the simulation of a random sequence with many repeats. There were 10 more mistakes detected using the later version \npscarfg{}. However, with additional investigations, we found that the number of mis-assemblies on the true positive circular sequences (3 from the reference) has been significant reduced by applying assembly graph for \npscarf{}. The errors mostly came from redundant sequences output from the software due to the failure in estimation of contig multiplicity.
Even though using assembly graph for gap fillings, there were no changes in the way to determine if a contig is unique or not from \npscarfg{}. 
It still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
Redundant path findings for false positive replicons consequently returned additional wrong translocations in the final contigs which were reported by QUAST. 
Other than that, the method had successfully produced better assemblies than the original. Regarding \emph{Mycobacterium tuberculosis} H37Rv, the number of mis-assembled breakpoints had been trimmed down from 12 to 2, while the number of final contigs had reduced from 4 to only one as in the reference. Results in cases of \ec{} O25b H4ST131 and \emph{Streptococcus suis} BM407 also showed enhancements in terms of those categories as well as N50 statistics. 
There was improvements considering the nucleotide errors (mismatches and indels) as well from aforementioned data sets, except for the \ec{} when slightly more mismatches had been detected. However, these errors can be corrected by running polishing tools with the raw Illumina data afterward.

For \emph{Acinetobacter} AB30 synthetic data, it was an deficiency for \npscarfg{} in traversing the graph to find candidate paths for a bridge of long distance due to particular large search space.
The exhaustive, naive DFS implementation for this version of \npscarf{} required a lot of memory to traverse a complex assembly graph that usually exceed a normal desktop's capacity.
This issue has been fixed in \npgraph{} when Algorithm~\ref{algo:findpath} was used on the definitive graph. This resulted in completed runs of the assembly process for all data sets with the similar number of mis-assemblies compared to the best figures in this category.
As shown in Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}, the assembly graph based methods offered significant improvements when compared to \npscarf{}. Not only because of the clear drops with respect to mis-assemblies and errors, but it was also reflected by the number of final contigs and their N50 as well.

To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} was invoked in \npgraph{}. 
The former option was inherited from \npscarf{} pipeline with the intact parameters
%$-k11 -W20 -r10 -A1 -B1 -O1 -E1 -L0 -a -Y$
while the latter was used with the recommended settings (-$\mathtt{k}$15 -$\mathtt{w}$5) for the best sensitivity working on MinION data.
Even though, \bwa{} normally reported more hits than \minimap{} but at the same time, was responsible for more false positive alignments.
For instance, regarding the last data set from Table~\ref{table:npgraph_compare}, the assembly of \npgraph{} using \bwa{} was suffered from the ambiguous alignments thus more fragmented than the other counterparts. 
On the other hand, referring to more complicated graphs from \emph{Acinetobacter} A1 and the yeast \emph{Saccharomyces cerevisiae} S288c from Table~\ref{supp_tab:synthetic_benchmark}, the number of mis-assemblies from using \minimap{} were increased due to the lacks of appropriate alignments to support accurate bridging process.
However, under almost circumstances, using either aligners would result in final assemblies with similar qualities.
Furthermore, in terms of running time and resources required, \minimap{} proved to be the best option. 
The total CPU hours had been trimmed down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
This feature is certainly more favoured to a real-time assembly as well.
As the consequence, as long as \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it would likewise become the main aligner for \npgraph{} pipeline in the future.

It is noteworthy to discuss in more details the errors addressed in the above assembly methods.
This figure measured the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
As expected from hybrid assemblies where Illumina sequencing data were used as the main building blocks, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) for almost every case.
In addition, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
This phenomenon may root from homologous repeats or sequencing errors of the genome.
From all the hybrid assemblers, $\mathtt{hybridSPAdes}$ reported results with highest fidelity. This meant that the performance its decision-rule algorithm $\mathtt{exSPAnder}$~\cite{Prjibelski2014} was the most accurate amongst all path finding methods. As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies in cases of \emph{Streptococcus suis} or \emph{Acinetobacter} samples (Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}).
\unicycler{}, which employs an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads, returned the second best reliable and at the same time, closest-to-complete results overall.
\npscarf{}, on the other hand, exploited the long reads for the gap filling thus inherited the high error rates from them.
By integrating the assembly graph for the task, the errors were reduced in general (random sequences, \emph{M.~tuberculosis}, \emph{S.suis} from Table~\ref{table:npgraph_compare}) but not completely since the mis-placed contigs were still not resolved in other circumstances.
\npgraph{} significantly reduced the errors compared to \npscarf{}, however the figures were still higher than the those of the best counterparts.
This implied a more robust decision making system is needed in \npgraph{}'s real-time path finding module for even better output's accuracy.

\subsection{Hybrid assembly for real data sets}
Several sequencing data sets of actual bacterial samples~\cite{George2017M14} were used in this scenario.
The data included both Illumina paired-end and MinION sequencing based-call data for each sample.
Unlike previous settings, rather than the default output, the optimal \spades{} assembly graph detected by \unicycler{} were used for \npgraph{} algorithm as well.
This step had been proved to be useful in selecting the best graph available, amongst \spades{} runs with ranging $k$-mer values, that have dead-ends and number of contigs minimized~\cite{Wick2017unicycler}. Likewise, as mentioned before, the quality of the initial assembly graph would considerably influence the final results of \npgraph{}.

Due to the lack of available reference genomes, fewer statistics were reported by QUAST for the comparison of the results. 
Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies.
Table~\ref{tab:npgraph_real} shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.

\begin{table}[!hpt]
\centering
\caption[Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized SPAdes output]{Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized \spades{} output. Circular contigs are highlighted in \textbf{bold}, fragmented assemblies are presented as X$\vert$Y where X is the total length and Y is the number of supposed contigs making up X.}
\label{tab:npgraph_real}
\begin{tabular}{p{4cm}|r|r|l}
 & \unicycler{} & \npgraph{} & Replicons (based on $\mathtt{PlasmidFinder}$ 1.3) \\ \toprule
\emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
 & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
 & \textbf{85,575} & \textbf{85,575} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{43,621} & \textbf{43,621} & repA\_1\_pKPC-2\_CP013325 \\
 & \textbf{3,223} & \textbf{3,223} & - \\
 & \textbf{1,916} & \textbf{1,916} & ColRNAI\_1\_\_DQ298019 \\
 & 14,464$\vert$3 & 14,456$\vert$2 & - \\ \hline
\emph{Enterobacter cloacae} & 4,806,666$\vert$2 & 4,858,438$\vert$2 & Chromosome \\
CAV1411 & \textbf{90,451} & 90,693$\vert$2 & IncR\_1\_\_DQ449578 \\
 & \textbf{33,610} & \textbf{33,610} & repA\_1\_pKPC-2\_CP013325 \\
 & 13,129$\vert$2 & 14,542$\vert$4 & - \\ \hline
\emph{Klebsiella oxytoca}  & 6,153,947$\vert$5 & \textbf{6,155,762} & Chromosome \\
CAV1015 & \textbf{113,105} & \textbf{113,105} & \begin{tabular}[c]{@{}l@{}}IncFII(SARC14)\_1\_SARC14\_JQ418540;\\ IncFII(S)\_1\_\_CP000858\end{tabular} \\
 & \textbf{111,395} & \textbf{111,395} & - \\
 & \textbf{108,418} & 109,209$\vert$13 & IncFIB(K)\_1\_Kpn3\_JN233704 \\
 & \textbf{76,183} & \textbf{76,186} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{11,638} & 11,892$\vert$2 & - \\ \hline
\end{tabular}
\end{table}

From the first data set, there was high similarity between final contigs generated by two assemblers.
They shared the same number of circular ultimate sequences, including the chromosomal and other six replicons contigs. 
The only divergence lied on the biggest sequence ($\simeq 5.029$Mbp) when the \unicycler{}'s chromosome was 48 nucleotides longer than that of \npgraph{}.
Five out of six identical replicons were confirmed as plasmids based on the occurences of appropriate Origin of replication sequences (PlasmidFinder database).
In detail, two megaplasmids (longer than $100$Kpb) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kpb, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or newly replicon's DNA.
Lastly, there were still $14.5$Kbp unfinished sequences resulted in 3 linear contigs from \unicycler{} and 2 for \npgraph{} respectively.

The assembly task for \emph{Enterobacter~cloacae} was more challenging as the chromosomal DNA sequence was not been fully resolved using either method. 
The chromosome size was estimated to be approximately $4.8$Mbp but had been broken into two smaller pieces. 
\npgraph{} returned longer stretches of length $3.324$Mbp and $1.534$Mbp while the figures were $2.829$Mbp and $1.978$Mbp from \unicycler{}'s output.
However, the number of circular sequences detected by \unicycler{} was one more than the other ($2$ versus $1$). They were corresponding to 2 plasmids, namely IncR and repA.
While the latter were recognized by both methods, the longer plasmid sequence was fragmented running \npgraph{}.
Similar to the previous data set, there were around $14$Kpb of data were unable to be finished by the assemblers.

Finally, assembly for \emph{Klebsiella oxytoca} saw fragmented chromosome using \unicycler{} but it was a fully complete contig for \npgraph{} with $6.156$Mbp of size.
The two assemblers shared 3 common circular sequences where two of them were confirmed plasmids. 
The first identical sequences represented a megaplasmid ($\simeq 113$Kbp) with two variations of IncFII's origin of replication DNA being identified. 
The other agreed plasmid were IncL/M with $76$Kbp of length.
Particularly, there was one circular contig with length greater than $100$Kbp but returned no hits to the plasmid database, suggesting the importance of \emph{de novo} replicon assembly in combination with further interrogations.
\unicycler{} detected another megaplasmid of size $108.4$Kbp which was fractured by \npgraph{}. 
The dissolution was also observed in \npgraph{} for the final contig of length $11.6$Kbp where it failed to combine two smaller sequences into one.

In addition to what presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Appendix Figure~\ref{supp_fig:npgraph_dotplot}. Interestingly, beside all other agreements, there was a structural difference using two methods for \emph{E.~cloacae} CAV1411 genome assembly. This was caused by the inconsistency of a fragment's direction on the final output contigs. However, when compare to a reference genome of the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), contigs generated by \npgraph{} demonstrated a consistent alignment which was not the case for \unicycler{} results (Appendix Figure~\ref{supp_fig:npgraph_ref}). Even though this might reflect a novel variation between bacterial samples of the same strain, it was more likely a mis-assembly by using \unicycler{}.

Overall, by testing with synthetic and real data, \npgraph{} proved to be able to generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}.
Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly. The next section will address this utility and the interactive GUI bundled in \npgraph{}.

\subsection{Real-time mode hybrid assembly}
Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
\npscarf{}\_wg basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.

\begin{figure}[!hpt]
\centering
\subfloat[\emph{Citrobacter~freundii} CAV1374]{
	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
}
\hfill
\subfloat[\emph{Escherichia~coli} K12 MG1655]{
	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
}
\\
\subfloat[\emph{Klebsiella} 30660 NJST258]{
	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
}
\hfill
\subfloat[\emph{Klebsiella} NTUH K2044]{
	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
}
\caption[Real-time scaffolding by \npscarf{} versus \npgraph{}]{N50 statistics of real-time scaffolding by \npscarf{} versus \npgraph{}.}
\label{F:npgraph_rt}
\end{figure}

As can be observed from all the plots, \npgraph{} and \npscarf{} both converged to the same ultimate completeness but with different paces and patterns.
Apparently it took more data for \npgraph{} to finish the same genome than the other.
The reason stems from the fact that the new algorithm implemented a more `conservative' approach of bridge construction with at least 3 supporting long-reads for each to prevent any potential mis-bridging. 
Unlike \npscarf{} when the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
The plot for \ec{} data clarifies this behaviour when a fluctuation can be observed in \npscarf{} assembly at $\simeq 3$-folds data coverage.
On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
The sharp `jumping' patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm.
Once a unique path has been determined, the bridge can be formed to connect the fragments together into longer sequences.

\begin{figure}[!hpt]
\centering
\subfloat[Initial graph]{
	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_0.png}
}
\hfill
\subfloat[Resolved graph]{
	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_2.png}
}
\caption[Assembly graph resolving on \npgraph{} Graph View]{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View. The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
\label{F:npgraph_graphview}
\end{figure}

Figure~\ref{F:npgraph_graphview} shows an example of the real-time graph resolving process being displayed on GUI.
The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
Smaller fragments, even unfinished but with high remaining coverage, are also presented as potential candidates for further downstream analysis.
Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
Assembly graph is the data structure describing the assembly process at a lower level of more details.
The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block of the assembly construction method (\npgraph{}).

While the first approach showed improvements in terms of base's accuracy for the final results, it had limited ability in rectifying the mis-assemblies from the original version due to false positive alignments at contig level.
The issue can be tackled by applying the assembly graph completely as in \npgraph{}.
With a more conservative bridging method applied, the new method may consume more data to confidently construct the assembly but at the same time, the number of mis-located fragments has reduced significantly.
Furthermore, users can monitor the assembly in an interactive way providing the assembly GUI.

Compared to the other hybrid assemblers of similar methodology, such as $\mathtt{hybridSPAdes}$ and \unicycler{}, there are still rooms for further development of \npgraph{}. 
More comprehensive pre-processing step is needed for a better input graph possible since it would affect the completeness of final results. 
Importantly, a robust real-time voting system should be implemented to be able to detect the most probable path amongst all candidates in an efficient way.
This would alleviate the data consumption of the \npgraph{} while at the same time, maintain high confident and accurate scaffolding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}

Basically the work flow of \npgraph{} can be divided into 3 main phases: abundance binning, graph resolving and assembly output. 
The first step will try to bin the contigs into different groups of \emph{population} based on their coverage. 
Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
The binning phase would assist to differentiate between repetitive contigs and unique ones. By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time. Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
\subsection{Pre-processing: identify repeat and unique contigs}
The purpose of this step is to investigate the sequencing properties of contigs, \IE{} length and \emph{k-mer} count, in combination with the graph topology, for an initial binning algorithm to determine multiplicity for each of them.
%\paragraph{Correct coverage bias due to GC content}
%The read coverage from Illumina data could be rectified by applying GC-content correction model \cite{BenjaminiS2012}.
%To be implemented.

\paragraph{Initial binning contigs into groups of abundances}
Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
This step is to cluster the significant nodes (longer than $10$Kbp) into different sets, namely significant abundance groups, based on their coverage values.

DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
The idea is to consider a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.

Assume there are 2 Poisson distribution $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$ 
The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.

The log ratio of the density functions is
$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$

The metric we used is the distance defined as
$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$

\paragraph{Coverage re-estimation}
Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is implemented to alleviate this issue. The coverage measure of nodes (which represent contigs) are spread throughout the graph via edges that connect them for comparison and calibration. 
The assignment of coverage to edges is also helpful to identify multiplicity in later step.

The re-estimation is basically carried out by following two steps.
\begin{itemize}
\item[1.] From nodes coverage, estimate edges' value by quadratic unconstrained optimization of the least-square function:
$$\frac{1}{2}\sum_{i}{l_i((\sum{e^{+}_{i}}-c_i)^2+(\sum{e^{-}_{i}}-c_i)^2}$$
where $l_i$ and $c_i$ is the length and coverage of a node $i$ in the graph;

$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
The above function and be rewritten as:
$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
and then being minimized by using Newton or gradient method.
\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
\end{itemize}
The calibration is iterative until no further improvements are made or a threshold loop count is reached.
\paragraph{Multiplicity estimation}
Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values. 
For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.

\subsection{Untangling assembly graph by stream of nanopore data.}
\paragraph{Building bridges in real-time}
Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph). This approach was implemented in \npscarf{} gap-filling phase with assembly graph as in Supplementary Figure \ref{f:gapfilling}.
% how bridge is connected, transformed multiplicity (real-time)
Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences are identified and assigned in appropriate unique paths.

Other than \npscarf{}, a bridge in \npgraph{} has several completion levels. A bridge is only created with at least one unique contig as an end, if so it has level 1 of completion. If both ends are identified, the level is 2. The number is greater than that only if paths connecting two ends are found. A bridge is known as fully complete (level 4) if there is only one unique linking path left. Given a bridge with 2 ends, a path finding algorithm (described in next section) is invoked to find all candidate paths. Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer. As more nanopore data arrives, the divergence between candidates' score becomes greater and only the best ones are voted for the next round.

Whenever a bridge becomes complete thanks to the voting system, the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path. The assembly graph would have at least one edge less than the original after the reduction. The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications. 
\paragraph{Path finding algorithm}

\begin{algorithm}[!hpt]
\DontPrintSemicolon
\KwData{Assembly graph $G\{V,E\}$}
\KwIn{Bridge $B=(\overrightarrow{v_1}, \overrightarrow{v_2})$ with two ending unique bidirected nodes $\overrightarrow{v_1}, \overrightarrow{v_2}$}
\KwOut{Set of candidate paths $P$ connecting $B$}
\Begin{
$d$:=$B.length()$ \tcp*{length of the bridge or the distance between 2 ending nodes}
$M$:=$\mathtt{shortestTree}(\overrightarrow{v_2},d)$ \tcp*{build shortest tree from $\overrightarrow{v_2}$ with range $d$}
\If{$M.contain(\overrightarrow{v_1})$}{
    $S$:=new $Stack()$ \tcp*{stack of sets of edges to traverse}
    $edgesSet$:=$getEdges(\overrightarrow{v_1})$ \tcp*{get all bidirected edges going from $\overrightarrow{v_1}$}
    $S.push(edgesSet)$\;
    $p$:=new $Path(\overrightarrow{v_1})$ \tcp*{init a path that has $\overrightarrow{v_1}$ as root}
    \While{true}{
        $edgesSet$:=$S.peek()$\;
        \If{$edgesSet.isEmpty()$}{
            \If{$p.size() \leq 1$}{
                $\mathbf{break}$ \tcp*{stop the loop when there is no more edge to discover}
            }
        $S.pop()$\;
        $d$+=$p.peekNode.length()+p.popEdge().length()$\; 
        }
        \Else{
            $curEdge \coloneqq edgesSet.remove()$\;
            $\overrightarrow{v}$:=$curEdge.getOpposite(p.peekNode())$\;
            $S.push(getEdges(\overrightarrow{v}).includedIn(M))$\;
            $p.add(curEdge)$\;
            \If{reach $\overrightarrow{v_2}$ with reasonable $d$}{
                $P.add(p)$\;
            }
            $d$-=$\overrightarrow{v}.length()+curEdge.length()$\;
        }
    }
}

\Return{$P$}
}
\caption{Pseudo-code for finding paths connecting a bridge with 2 ends.}
\label{algo:findpath}
\end{algorithm}
% formal mathematical definition & DFS algorithm goes here...
In \npscarf{} with assembly graph, the path finding algorithm is the original DFS (depth first search) which becomes computationally expensive when the traversing depth increases. For \npgraph{}, we implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space.

Algorithm~\ref{algo:findpath} demonstrates the path finding module in general.
In which, function

$\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n$

from line 3 of the algorithm's pseudo code builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance regarding nanopore read error rate) is reached. This task is implemented based on Dijkstra algorithm.
This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.

Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover. During the traversal, a variable $d$ is updated as an estimation for the distance to the target. A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21). 
A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.

It is worth to mention that the $length()$ functions for node and edge are totally different. While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges). For example, in a \emph{k-mers} DBG-derived assembly graph, the value of an edge is $-k$.

\subsection{Result extraction and output}
\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result.
A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if every edge along the path, $e_i, \forall i=1,\ldots,k$, must be the only option to traverse from either $v_{i-1}$ or $v_i$ following the transition rule.
To decompose the graph, we can just simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}. These edges are defined as branching edges which stop straight paths from further extending.

\begin{figure}[!hpt]
\centering
\includegraphics[width=.6\textwidth]{images/decompose.pdf}
\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths. Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report. There would be 3 contigs extracted by traversing along the straight paths here.}
\label{figure:npgraph_decompose}
\end{figure}
The decomposed graph is only used to report the contigs that can be extracted from an assembly graph at certain time point. For that reason, the branching edges are only masked but not removed from the original graph as they would be used for further bridging.

The final assembly output contains files in both FASTA and GFA v1 format (\url{https://github.com/GFA-spec/GFA-spec}). While the former only retains the actual genome sequences from the final decomposed graph, the latter output file can store almost every properties of the ultimate un-masked graph such as nodes, links and potential paths between them.

\bibliographystyle{pnas2011}
\bibliography{library}

\end{document}

### 2019-05-07 paper.tex
jlkj
sfd

@@
 \usepackage{xr}
-\externaldocument{supplementary.tex}
+\externaldocument{supplementary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%Set the title
-\title{Online resolving assembly graph by long reads data}
-
-%Set the short tittle
-\shorttitle{An awesome paper}
+\title{Online resolving assembly graph by ONT long reads data}
+\shorttitle{Real-time Scaffolding with Assembly graph}
 
 %Authors
-\author[1,$\dag$, $\ast$]{Author First}
-\author[1,$\dag$]{Author Two} 
-\author[1,2]{Author Three}
-\author[1,2,$\ast$]{Author Last}
+\author[1,$\ast$]{Son Hoang Nguyen}
+%\author[]{Minh Duc Cao}
+\author[1,$\ast$]{Lachlan Coin}
 
 %Affiliation
-\affil[1]{Affiliation One}
-\affil[2]{Affiliation Two}
+\affil[1]{Institute for Molecular Bioscience, the University of Queensland, 
+St Lucia, Brisbane, QLD 4072 Australia}
 
-%Display equal author textrent focus is developing methods to determine evolutionary relationships, primarily usi
-\equalauthors{\textsuperscript{$\dag$}These authors contributed equally to
-this work.}
-
-%Display correspondingauthor text 
 \correspondingauthor{
-\textsuperscript{$\ast$}To whom correspondence should be addressed. E-mails:
-author.last\@email.com,author.first\@email.com}
+\textsuperscript{$\ast$}
+To whom correspondence should be addressed. 
+E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
+}
 
@@
 %Set keywords
-\keywords{Keyword 1, Keyword 2,Keyword 3}
+\keywords{hybrid assembly, assembly graph, real-time analysis, nanopore sequencing}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section*{Introduction}
 % \begin{itemize}
@@
 % \end{itemize}
-Streaming assembly methods have been proven to be useful in saving time and resources compared to the traditional batch algorithms with examples included \EG $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+Streaming assembly methods have been proven to be useful in saving time and resources compared to the traditional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
 The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{\npgraph{} -- a tool to resolve assembly graph in real-time}
+\section*{Results}
+\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
 \npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g.
@@
 
-\subsection{Hybrid assembly for synthetic data sets}
+\subsection*{Hybrid assembly for synthetic data sets}
 To evaluate the performance of the method, \npgraph{} was benchmarked against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on the latter's testing data~ \cite{Wick2017unicycler} .
@@
 
-\subsection{Hybrid assembly for real data sets}
+\subsection*{Hybrid assembly for real data sets}
 Several sequencing data sets of actual bacterial samples~\cite{George2017M14} were used in this scenario.
@@
 
-\subsection{Real-time mode hybrid assembly}
+\subsection*{Real-time mode hybrid assembly}
 Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
 This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
-\npscarf{}\_wg basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.
+\npscarfg{} basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.
 
@@
 On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
-The sharp `jumping' patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm.
+The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm.
 Once a unique path has been determined, the bridge can be formed to connect the fragments together into longer sequences.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
+\section*{Conclusions}
 Assembly graph is the data structure describing the assembly process at a lower level of more details.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methods}
+\section*{Materials and Methods}
 
@@
 The whole process can be managed by using either command-line interface or GUI.
-\subsection{Pre-processing: identify repeat and unique contigs}
-The purpose of this step is to investigate the sequencing properties of contigs, \IE{} length and \emph{k-mer} count, in combination with the graph topology, for an initial binning algorithm to determine multiplicity for each of them.
-%\paragraph{Correct coverage bias due to GC content}
-%The read coverage from Illumina data could be rectified by applying GC-content correction model \cite{BenjaminiS2012}.
-%To be implemented.
 
-\paragraph{Initial binning contigs into groups of abundances}
+\subsection*{Initial binning contigs into groups of abundances}
 Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
@@
 
-\paragraph{Coverage re-estimation}
+\subsection*{Coverage re-estimation}
 Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is implemented to alleviate this issue.
@@
 The calibration is iterative until no further improvements are made or a threshold loop count is reached.
-\paragraph{Multiplicity estimation}
+\subsection*{Multiplicity estimation}
 Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
@@
 
-\subsection{Untangling assembly graph by stream of nanopore data.}
-\paragraph{Building bridges in real-time}
+%\subsection*{Untangling assembly graph by stream of nanopore data.}
+\subsection*{Building bridges in real-time}
 Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph).
-This approach was implemented in \npscarf{} gap-filling phase with assembly graph as in Supplementary Figure \ref{f:gapfilling}.
-% how bridge is connected, transformed multiplicity (real-time)
 Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
@@
 The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications.
-\paragraph{Path finding algorithm}
+
+\subsection*{Path finding algorithm}
 
@@
 
-\subsection{Result extraction and output}
+\subsection*{Result extraction and output}
 \npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result.

### 2019-05-28 paper.tex
draft 0.2

@@
 %Set abstract (see below)
-\abstract{This is abstract}
+\abstract{
+A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses.
+The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies.
+Here we present another real-time hybrid assembler, \npgraph{}, that work on the assembly graph instead of the pre-assembled contigs.
+The results show improved accuracy while still minimize the required computational cost.
+The tool is available at \url{https://github.com/hsnguyen/assembly}.
+}
 

### 2019-06-13 paper.tex
abc
more methods

@@
 \author[1,$\ast$]{Son Hoang Nguyen}
-%\author[]{Minh Duc Cao}
+\author[2]{Minh Duc Cao}
 \author[1,$\ast$]{Lachlan Coin}
@@
 St Lucia, Brisbane, QLD 4072 Australia}
-
+\affil[2]{4catalyzer}
 \correspondingauthor{
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Materials and Methods}
+\section*{Methods}
 
-Basically the work flow of \npgraph{} can be divided into 3 main phases: abundance binning, graph resolving and assembly output. 
-The first step will try to bin the contigs into different groups of \emph{population} based on their coverage. 
+Basically the work flow of \npgraph{} consists of 3 main modules: abundance binning, graph resolving and assembly output. 
+The first step is to bin the contigs into different groups of \emph{population} based on their coverage. 
 Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
@@
 
-Assume there are 2 Poisson distribution $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
+Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
 The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:

### 2019-06-14 paper.tex
d

@@
 Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
-This step is to cluster the significant nodes (longer than $10$Kbp) into different sets, namely significant abundance groups, based on their coverage values.
+This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on their coverage values.
 
 DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
-The idea is to consider a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
+The rationale is to approximate a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
 The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.

### 2019-06-17 paper.tex
following flye

@@
 
-Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
-The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
-$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
-or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
-
-The log ratio of the density functions is
-$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
-$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-
-The metric we used is the distance defined as
-$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
+%%%Move to Supplementary
+%Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
+%The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
+%$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
+%or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
+%
+%The log ratio of the density functions is
+%$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+%take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
+%$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+%
+%The metric we used is the distance defined as
+%$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
 
@@
 $$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
-and then being minimized by using Newton or gradient method.
+and then being minimized by using gradient-based method.
 \item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.

### 2019-06-24 paper.tex
move maths to supp

--- 2019-06-14 paper.tex
@@
 \usepackage{multirow}
-
-% For pseudocode
-\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
-\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
-\SetCommentSty{mycommfont}
-% For code embedding (Bash, Java...)
-\usepackage{listings}
-\lstset{basicstyle=\ttfamily,
-  showstringspaces=false,
-  commentstyle=\color{red},
-  keywordstyle=\color{blue}
-}
 
@@
 
-Basically the work flow of \npgraph{} consists of 3 main modules: abundance binning, graph resolving and assembly output. 
-The first step is to bin the contigs into different groups of \emph{population} based on their coverage. 
-Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
-The binning phase would assist to differentiate between repetitive contigs and unique ones.
+Basically the work flow of \npgraph{} consists of 3 main modules: (1) assembly graph loading and preprocessing; (2) graph resolving; (3) postprocessing and reporting. 
+The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
 By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time.
-Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results.
-The whole process can be managed by using either command-line interface or GUI.
+Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
+Among three phases, only the first one must be performed prior to the MinION sequencing process in a streaming setup.
+\subsection*{Contigs binning}
+Each population is expected to include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
+In addition, the binning phase would assist to differentiate between repetitive contigs and unique ones.
 
-\subsection*{Initial binning contigs into groups of abundances}
-Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
-This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on their coverage values.
+Each contig is represented as a node in the assembly graph and an edge between two nodes indicate their overlap (link) properties.
+This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
+DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task by default.
+The rationale is to approximate a coverage value of a significant contig (which can be splitted into more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count).
+The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
+Other than that, external binning tools can be employed for more complicated binning task, \EG{} metagenomics, and the results can be integrated into \npgraph{} for better performance.
+More details can be found on Supplementary Note \ref{supp:note1}.
 
-DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
-The rationale is to approximate a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
-The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
+\subsection*{Multiplicity estimation}
+Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is carried out to alleviate this issue as shown in Supplementary Note \ref{supp:note2}.
+The coverage measures of nodes (which represent contigs) are spread throughout the graph via connecting edges for comparisons and calibrations prior to the multiplicity estimation.
+%The assignment of coverage to edges is also helpful to induce multiplicity of nodes in later step.
 
-Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
-The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
-$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
-or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
-
-The log ratio of the density functions is
-$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
-$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-
-The metric we used is the distance defined as
-$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
-
-\subsection*{Coverage re-estimation}
-Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is implemented to alleviate this issue.
-The coverage measure of nodes (which represent contigs) are spread throughout the graph via edges that connect them for comparison and calibration.
-The assignment of coverage to edges is also helpful to identify multiplicity in later step.
-
-The re-estimation is basically carried out by following two steps.
-\begin{itemize}
-\item[1.] From nodes coverage, estimate edges' value by quadratic unconstrained optimization of the least-square function:
-$$\frac{1}{2}\sum_{i}{l_i((\sum{e^{+}_{i}}-c_i)^2+(\sum{e^{-}_{i}}-c_i)^2}$$
-where $l_i$ and $c_i$ is the length and coverage of a node $i$ in the graph;
-
-$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
-The above function and be rewritten as:
-$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
-and then being minimized by using Newton or gradient method.
-\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
-\end{itemize}
-The calibration is iterative until no further improvements are made or a threshold loop count is reached.
-\subsection*{Multiplicity estimation}
 Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
@@
 
-\begin{algorithm}[!hpt]
-\DontPrintSemicolon
-\KwData{Assembly graph $G\{V,E\}$}
-\KwIn{Bridge $B=(\overrightarrow{v_1}, \overrightarrow{v_2})$ with two ending unique bidirected nodes $\overrightarrow{v_1}, \overrightarrow{v_2}$}
-\KwOut{Set of candidate paths $P$ connecting $B$}
-\Begin{
-$d$:=$B.length()$ \tcp*{length of the bridge or the distance between 2 ending nodes}
-$M$:=$\mathtt{shortestTree}(\overrightarrow{v_2},d)$ \tcp*{build shortest tree from $\overrightarrow{v_2}$ with range $d$}
-\If{$M.contain(\overrightarrow{v_1})$}{
-    $S$:=new $Stack()$ \tcp*{stack of sets of edges to traverse}
-    $edgesSet$:=$getEdges(\overrightarrow{v_1})$ \tcp*{get all bidirected edges going from $\overrightarrow{v_1}$}
-    $S.push(edgesSet)$\;
-    $p$:=new $Path(\overrightarrow{v_1})$ \tcp*{init a path that has $\overrightarrow{v_1}$ as root}
-    \While{true}{
-        $edgesSet$:=$S.peek()$\;
-        \If{$edgesSet.isEmpty()$}{
-            \If{$p.size() \leq 1$}{
-                $\mathbf{break}$ \tcp*{stop the loop when there is no more edge to discover}
-            }
-        $S.pop()$\;
-        $d$+=$p.peekNode.length()+p.popEdge().length()$\; 
-        }
-        \Else{
-            $curEdge \coloneqq edgesSet.remove()$\;
-            $\overrightarrow{v}$:=$curEdge.getOpposite(p.peekNode())$\;
-            $S.push(getEdges(\overrightarrow{v}).includedIn(M))$\;
-            $p.add(curEdge)$\;
-            \If{reach $\overrightarrow{v_2}$ with reasonable $d$}{
-                $P.add(p)$\;
-            }
-            $d$-=$\overrightarrow{v}.length()+curEdge.length()$\;
-        }
-    }
-}
-
-\Return{$P$}
-}
-\caption{Pseudo-code for finding paths connecting a bridge with 2 ends.}
-\label{algo:findpath}
-\end{algorithm}
-% formal mathematical definition & DFS algorithm goes here...
-In \npscarf{} with assembly graph, the path finding algorithm is the original DFS (depth first search) which becomes computationally expensive when the traversing depth increases.
-For \npgraph{}, we implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space.
-
-Algorithm~\ref{algo:findpath} demonstrates the path finding module in general.
-In which, function
-
-$\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n$
-
-from line 3 of the algorithm's pseudo code builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance regarding nanopore read error rate) is reached.
-This task is implemented based on Dijkstra algorithm.
-This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.
-
-Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover.
-During the traversal, a variable $d$ is updated as an estimation for the distance to the target.
-A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21).
-A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.
-
-It is worth to mention that the $length()$ functions for node and edge are totally different.
-While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges).
-For example, in a \emph{k-mers} DBG-derived assembly graph, the value of an edge is $-k$.
+We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note3}).
 

### 2019-07-05 paper.tex
sf

@@
 For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
-Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values.
-For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.
+Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variation of coverage values.
+For that reason, in \npgraph{}'s algorithm, they are only used as augmented information to calculate likelihood scores of candidate paths containing corresponding nodes.
 
@@
 Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
-This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences are identified and assigned in appropriate unique paths.
+This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences have been already identified and assigned in appropriate unique paths.
 
@@
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result.
-A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if every edge along the path, $e_i, \forall i=1,\ldots,k$, must be the only option to traverse from either $v_{i-1}$ or $v_i$ following the transition rule.
-To decompose the graph, we can just simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}.
-These edges are defined as branching edges which stop straight paths from further extending.
-
-\begin{figure}[!hpt]
-\centering
-\includegraphics[width=.6\textwidth]{images/decompose.pdf}
-\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths.
-Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report.
-There would be 3 contigs extracted by traversing along the straight paths here.}
-\label{figure:npgraph_decompose}
-\end{figure}
-The decomposed graph is only used to report the contigs that can be extracted from an assembly graph at certain time point.
-For that reason, the branching edges are only masked but not removed from the original graph as they would be used for further bridging.
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note4}).
 

### 2019-07-22 paper.tex
method modify

@@
 \subsection*{Multiplicity estimation}
-Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is carried out to alleviate this issue as shown in Supplementary Note \ref{supp:note2}.
-The coverage measures of nodes (which represent contigs) are spread throughout the graph via connecting edges for comparisons and calibrations prior to the multiplicity estimation.
+Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially for the shorter contigs, an optimization step is carried out to alleviate this issue as shown in Supplementary Note \ref{supp:note2}.
+The coverage measures of nodes (which represent contigs) are propated throughout the graph via connecting edges for calibrations prior to the multiplicity estimation.
 %The assignment of coverage to edges is also helpful to induce multiplicity of nodes in later step.
@@
 \subsection*{Building bridges in real-time}
-Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph).
-Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
-This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences have been already identified and assigned in appropriate unique paths.
+Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
+The real-time bridging method considers the dynamic aspect of multiplicity measures for each node, meaning that a $n$-times repetitive node might become a unique node at certain time point when its $(n-1)$ occurrences have been already identified in other distinct unique paths.
+Furthermore, the streaming fashion of this method allows the bridge constructions to be carried out progressively so that assembly decisions are made immediately after having sufficient supporting data.
+The detail implementation is addressed in Supplementary Note~\ref{supp:note3}.
 
-Other than \npscarf{}, a bridge in \npgraph{} has several completion levels.
-A bridge is only created with at least one unique contig as an end, if so it has level 1 of completion.
-If both ends are identified, the level is 2.
-The number is greater than that only if paths connecting two ends are found.
-A bridge is known as fully complete (level 4) if there is only one unique linking path left.
-Given a bridge with 2 ends, a path finding algorithm (described in next section) is invoked to find all candidate paths.
+A bridge in \npgraph{} has several completion levels.
+When created, it must be rooted from an \emph{anchor node} which represents a unique contig (level 1).
+A bridge is known as fully complete (level 4) if and only if there is a unique path connecting its two anchor nodes from two ends.
+
+\subsection*{Path finding algorithm}
+Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them.
 Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
-As more nanopore data arrives, the divergence between candidates' score becomes greater and only the best ones are voted for the next round.
+As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
+We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note4}).
 
-Whenever a bridge becomes complete thanks to the voting system, the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.
+It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments.
+In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is used for a \emph{pseudo} edge being created.
+\subsection{Resolve by reducing the graph complexity}
+
+Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.
 The assembly graph would have at least one edge less than the original after the reduction.
@@
 
-\subsection*{Path finding algorithm}
-
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note3}).
-
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note4}).
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note5}).
 

### 2019-07-24 paper.tex
edit pathfinding

@@
 
-Basically the work flow of \npgraph{} consists of 3 main modules: (1) assembly graph loading and preprocessing; (2) graph resolving; (3) postprocessing and reporting. 
+Basically the work flow of \npgraph{} consists of 3 main modules: (1) assembly graph loading and preprocessing; (2) graph resolving; (3) postprocessing and reporting results. 
 The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
@@
 Among three phases, only the first one must be performed prior to the MinION sequencing process in a streaming setup.
+The algorithm works on the assembly graph of Illumina contigs, so the terms \emph{contigs} and \emph{nodes} if not mentioned specifically, would be used interchangable throughout this context.
 \subsection*{Contigs binning}
@@
 
-Each contig is represented as a node in the assembly graph and an edge between two nodes indicate their overlap (link) properties.
+Each contig is represented as a single node in the assembly graph and an edge between two nodes indicate their overlap (link) properties.
 This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
@@
 Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
+A bridge must start from a unique contig, or \emph{anchor} node, and end at another when completed.
+Located inbetween are nodes known as \emph{steps} and distances between them are called \emph{spans} of the bridge.
+Stepping nodes are normally repetitive contigs and indicative for a path finding operation later on.
+In a complicated assembly graph, the more details the bridge, \emph{a.k.a.} more steps inbetween, the faster and more accurate the linking path it would resolve.
+A bridge's function is complete when it successfully return the ultimate linking path between 2 anchors.
+
 The real-time bridging method considers the dynamic aspect of multiplicity measures for each node, meaning that a $n$-times repetitive node might become a unique node at certain time point when its $(n-1)$ occurrences have been already identified in other distinct unique paths.
-Furthermore, the streaming fashion of this method allows the bridge constructions to be carried out progressively so that assembly decisions are made immediately after having sufficient supporting data.
+Furthermore, the streaming fashion of this method allows the bridge constructions (updating steps and spans) to be carried out progressively so that assembly decisions can be made immediately after having sufficient supporting data.
 The detail implementation is addressed in Supplementary Note~\ref{supp:note3}.

### 2019-07-25 paper.tex
sdfs

@@
 Furthermore, the streaming fashion of this method allows the bridge constructions (updating steps and spans) to be carried out progressively so that assembly decisions can be made immediately after having sufficient supporting data.
-The detail implementation is addressed in Supplementary Note~\ref{supp:note3}.
+The detail implementation is addressed in Supplementary Note~\ref{supp:note4}.
 
@@
 As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note4}).
+We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note5}).
 
@@
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note5}).
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note6}).
 

### 2019-09-26 paper.tex
Updates from Overleaf

--- 2019-07-22 paper.tex
@@
 
+% For pseudocode
+\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
+\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
+\SetCommentSty{mycommfont}
+% For code embedding (Bash, Java...)
+\usepackage{listings}
+\lstset{basicstyle=\ttfamily,
+  showstringspaces=false,
+  commentstyle=\color{red},
+  keywordstyle=\color{blue}
+}
+
 \usepackage{float}
@@
 \author[1,$\ast$]{Son Hoang Nguyen}
-\author[2]{Minh Duc Cao}
+\author[1]{Minh Duc Cao}
 \author[1,$\ast$]{Lachlan Coin}
@@
 St Lucia, Brisbane, QLD 4072 Australia}
-\affil[2]{4catalyzer}
 \correspondingauthor{
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Methods}
+\section*{Materials and Methods}
 
-Basically the work flow of \npgraph{} consists of 3 main modules: (1) assembly graph loading and preprocessing; (2) graph resolving; (3) postprocessing and reporting. 
-The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
+Basically the work flow of \npgraph{} can be divided into 3 main phases: abundance binning, graph resolving and assembly output. 
+The first step will try to bin the contigs into different groups of \emph{population} based on their coverage. 
+Each population would include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
+The binning phase would assist to differentiate between repetitive contigs and unique ones.
 By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time.
-Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
-Among three phases, only the first one must be performed prior to the MinION sequencing process in a streaming setup.
-\subsection*{Contigs binning}
-Each population is expected to include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
-In addition, the binning phase would assist to differentiate between repetitive contigs and unique ones.
+Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results.
+The whole process can be managed by using either command-line interface or GUI.
 
-Each contig is represented as a node in the assembly graph and an edge between two nodes indicate their overlap (link) properties.
-This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
-DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task by default.
-The rationale is to approximate a coverage value of a significant contig (which can be splitted into more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count).
+\subsection*{Initial binning contigs into groups of abundances}
+Each contig is represented as a node in the assembly graph and the edge between two nodes indicate their overlap (link) properties.
+This step is to cluster the significant nodes (longer than $10$Kbp) into different sets, namely significant abundance groups, based on their coverage values.
+
+DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task.
+The idea is to consider a coverage value of a significant contig (which consists of more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
 The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
-Other than that, external binning tools can be employed for more complicated binning task, \EG{} metagenomics, and the results can be integrated into \npgraph{} for better performance.
-More details can be found on Supplementary Note \ref{supp:note1}.
 
+Assume there are 2 Poisson distribution $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
+The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
+$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
+or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
+
+The log ratio of the density functions is
+$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
+$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+
+The metric we used is the distance defined as
+$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
+
+\subsection*{Coverage re-estimation}
+Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially the short ones, an optimization step is implemented to alleviate this issue.
+The coverage measure of nodes (which represent contigs) are spread throughout the graph via edges that connect them for comparison and calibration.
+The assignment of coverage to edges is also helpful to identify multiplicity in later step.
+
+The re-estimation is basically carried out by following two steps.
+\begin{itemize}
+\item[1.] From nodes coverage, estimate edges' value by quadratic unconstrained optimization of the least-square function:
+$$\frac{1}{2}\sum_{i}{l_i((\sum{e^{+}_{i}}-c_i)^2+(\sum{e^{-}_{i}}-c_i)^2}$$
+where $l_i$ and $c_i$ is the length and coverage of a node $i$ in the graph;
+
+$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
+The above function and be rewritten as:
+$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
+and then being minimized by using Newton or gradient method.
+\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
+\end{itemize}
+The calibration is iterative until no further improvements are made or a threshold loop count is reached.
 \subsection*{Multiplicity estimation}
-Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially for the shorter contigs, an optimization step is carried out to alleviate this issue as shown in Supplementary Note \ref{supp:note2}.
-The coverage measures of nodes (which represent contigs) are propated throughout the graph via connecting edges for calibrations prior to the multiplicity estimation.
-%The assignment of coverage to edges is also helpful to induce multiplicity of nodes in later step.
-
 Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
 For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
-Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variation of coverage values.
-For that reason, in \npgraph{}'s algorithm, they are only used as augmented information to calculate likelihood scores of candidate paths containing corresponding nodes.
+Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values.
+For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.
 
@@
 \subsection*{Building bridges in real-time}
-Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
-The real-time bridging method considers the dynamic aspect of multiplicity measures for each node, meaning that a $n$-times repetitive node might become a unique node at certain time point when its $(n-1)$ occurrences have been already identified in other distinct unique paths.
-Furthermore, the streaming fashion of this method allows the bridge constructions to be carried out progressively so that assembly decisions are made immediately after having sufficient supporting data.
-The detail implementation is addressed in Supplementary Note~\ref{supp:note3}.
+Bridge is the data structure designed for tracking the possible connections between two unique contigs (anchor nodes in the assembly graph).
+Here we take advantage of the graph topology and nodes' multiplicity information to employ a dynamic bridging mechanism.
+This procedure considers the dynamic changing of multiplicity property for each node, meaning that a $n$-times repetitive node can become a unique node at certain time point when its $(n-1)$ occurrences are identified and assigned in appropriate unique paths.
 
-A bridge in \npgraph{} has several completion levels.
-When created, it must be rooted from an \emph{anchor node} which represents a unique contig (level 1).
-A bridge is known as fully complete (level 4) if and only if there is a unique path connecting its two anchor nodes from two ends.
+Other than \npscarf{}, a bridge in \npgraph{} has several completion levels.
+A bridge is only created with at least one unique contig as an end, if so it has level 1 of completion.
+If both ends are identified, the level is 2.
+The number is greater than that only if paths connecting two ends are found.
+A bridge is known as fully complete (level 4) if there is only one unique linking path left.
+Given a bridge with 2 ends, a path finding algorithm (described in next section) is invoked to find all candidate paths.
+Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
+As more nanopore data arrives, the divergence between candidates' score becomes greater and only the best ones are voted for the next round.
 
-\subsection*{Path finding algorithm}
-Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them.
-Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
-As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note4}).
-
-It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments.
-In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is used for a \emph{pseudo} edge being created.
-\subsection{Resolve by reducing the graph complexity}
-
-Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.
+Whenever a bridge becomes complete thanks to the voting system, the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.
 The assembly graph would have at least one edge less than the original after the reduction.
@@
 
+\subsection*{Path finding algorithm}
+
+\begin{algorithm}[!hpt]
+\DontPrintSemicolon
+\KwData{Assembly graph $G\{V,E\}$}
+\KwIn{Bridge $B=(\overrightarrow{v_1}, \overrightarrow{v_2})$ with two ending unique bidirected nodes $\overrightarrow{v_1}, \overrightarrow{v_2}$}
+\KwOut{Set of candidate paths $P$ connecting $B$}
+\Begin{
+$d$:=$B.length()$ \tcp*{length of the bridge or the distance between 2 ending nodes}
+$M$:=$\mathtt{shortestTree}(\overrightarrow{v_2},d)$ \tcp*{build shortest tree from $\overrightarrow{v_2}$ with range $d$}
+\If{$M.contain(\overrightarrow{v_1})$}{
+    $S$:=new $Stack()$ \tcp*{stack of sets of edges to traverse}
+    $edgesSet$:=$getEdges(\overrightarrow{v_1})$ \tcp*{get all bidirected edges going from $\overrightarrow{v_1}$}
+    $S.push(edgesSet)$\;
+    $p$:=new $Path(\overrightarrow{v_1})$ \tcp*{init a path that has $\overrightarrow{v_1}$ as root}
+    \While{true}{
+        $edgesSet$:=$S.peek()$\;
+        \If{$edgesSet.isEmpty()$}{
+            \If{$p.size() \leq 1$}{
+                $\mathbf{break}$ \tcp*{stop the loop when there is no more edge to discover}
+            }
+        $S.pop()$\;
+        $d$+=$p.peekNode.length()+p.popEdge().length()$\; 
+        }
+        \Else{
+            $curEdge \coloneqq edgesSet.remove()$\;
+            $\overrightarrow{v}$:=$curEdge.getOpposite(p.peekNode())$\;
+            $S.push(getEdges(\overrightarrow{v}).includedIn(M))$\;
+            $p.add(curEdge)$\;
+            \If{reach $\overrightarrow{v_2}$ with reasonable $d$}{
+                $P.add(p)$\;
+            }
+            $d$-=$\overrightarrow{v}.length()+curEdge.length()$\;
+        }
+    }
+}
+
+\Return{$P$}
+}
+\caption{Pseudo-code for finding paths connecting a bridge with 2 ends.}
+\label{algo:findpath}
+\end{algorithm}
+% formal mathematical definition & DFS algorithm goes here...
+In \npscarf{} with assembly graph, the path finding algorithm is the original DFS (depth first search) which becomes computationally expensive when the traversing depth increases.
+For \npgraph{}, we implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space.
+
+Algorithm~\ref{algo:findpath} demonstrates the path finding module in general.
+In which, function
+
+$\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n$
+
+from line 3 of the algorithm's pseudo code builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance regarding nanopore read error rate) is reached.
+This task is implemented based on Dijkstra algorithm.
+This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.
+
+Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover.
+During the traversal, a variable $d$ is updated as an estimation for the distance to the target.
+A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21).
+A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.
+
+It is worth to mention that the $length()$ functions for node and edge are totally different.
+While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges).
+For example, in a \emph{k-mers} DBG-derived assembly graph, the value of an edge is $-k$.
+
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note5}).
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result.
+A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if every edge along the path, $e_i, \forall i=1,\ldots,k$, must be the only option to traverse from either $v_{i-1}$ or $v_i$ following the transition rule.
+To decompose the graph, we can just simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}.
+These edges are defined as branching edges which stop straight paths from further extending.
+
+\begin{figure}[!hpt]
+\centering
+\includegraphics[width=.6\textwidth]{images/decompose.pdf}
+\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths.
+Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report.
+There would be 3 contigs extracted by traversing along the straight paths here.}
+\label{figure:npgraph_decompose}
+\end{figure}
+The decomposed graph is only used to report the contigs that can be extracted from an assembly graph at certain time point.
+For that reason, the branching edges are only masked but not removed from the original graph as they would be used for further bridging.
 

### 2019-10-25 paper.tex
sbs

--- 2019-07-25 paper.tex
@@
 It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments.
-In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is used for a \emph{pseudo} edge being created.
-\subsection{Resolve by reducing the graph complexity}
+In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
+\subsection{Resolve the graph by reducing its complexity}
 

### 2019-10-29 paper.tex
adding more results

@@
 
-\begin{figure}[!hpt]
-\centering
-\subfloat[Initial graph]{
-	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_0.png}
-}
-\hfill
-\subfloat[Resolved graph]{
-	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_2.png}
-}
-\caption[Assembly graph resolving on \npgraph{} Graph View]{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
-The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
-\label{F:npgraph_graphview}
-\end{figure}
+\subsection*{Scaffolding metagenomics data set}
 
-Figure~\ref{F:npgraph_graphview} shows an example of the real-time graph resolving process being displayed on GUI.
-The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
-Smaller fragments, even unfinished but with high remaining coverage, are also presented as potential candidates for further downstream analysis.
-Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-01 paper.tex
sf

@@
 
-\title{Online resolving assembly graph by ONT long reads data}
+\title{Real-time resolving assembly graph by ONT long reads data}
 \shorttitle{Real-time Scaffolding with Assembly graph}
@@
 \abstract{
-A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses.
-The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies.
-Here we present another real-time hybrid assembler, \npgraph{}, that work on the assembly graph instead of the pre-assembled contigs.
-The results show improved accuracy while still minimize the required computational cost.
-The tool is available at \url{https://github.com/hsnguyen/assembly}.
+A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses.
+The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods.
+Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs.
+It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide.
+The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level.
+In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process.
+The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
 }
@@
 
-\subsection*{Scaffolding metagenomics data set}
+\subsection*{Metagenomics assembly}
+We further used \npgraph{} on three mock communities to study the performance of this approach in metagenomics co-assembly application.
 
@@
 \section*{Conclusions}
-Assembly graph is the data structure describing the assembly process at a lower level of more details.
-The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block of the assembly construction method (\npgraph{}).
+Assembly graph is the data structure describing the assembly components at  more details.
+The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block for the assembly construction method (\npgraph{}).
 
@@
 With a more conservative bridging method applied, the new method may consume more data to confidently construct the assembly but at the same time, the number of mis-located fragments has reduced significantly.
-Furthermore, users can monitor the assembly in an interactive way providing the assembly GUI.
+Furthermore, users can monitor the assembly in an interactive manner providing the assembly GUI.
 
@@
 More comprehensive pre-processing step is needed for a better input graph possible since it would affect the completeness of final results.
+
 Importantly, a robust real-time voting system should be implemented to be able to detect the most probable path amongst all candidates in an efficient way.
@@
 In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
-\subsection{Resolve the graph by reducing its complexity}
-
+\subsection*{Assembly graph resolving in real-time}
+\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that could be generated in real-time.
 Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.

### 2019-11-03 paper.tex
sfsfa
remake

--- 2019-10-29 paper.tex
@@
 The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies.
-Here we present another real-time hybrid assembler, \npgraph{}, that work on the assembly graph instead of the pre-assembled contigs.
+Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs.
 The results show improved accuracy while still minimize the required computational cost.

### 2019-11-15 paper.tex
add zymo
adding zymo result

--- 2019-11-01 paper.tex
@@
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
+%=======
+%A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses.
+The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies.
+Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs.
+The results show improved accuracy while still minimize the required computational cost.
+The tool is available at \url{https://github.com/hsnguyen/assembly}.
+%>>>>>>> 2d4c481dd93902dfb2dabe46534a62e8a8c2058c
 }
@@
 \subsection*{Metagenomics assembly}
-We further used \npgraph{} on three mock communities to study the performance of this approach in metagenomics co-assembly application.
+We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
+In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}.
+The total genome size was estimated as 61.96 Mbp.
+There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
+On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}.
+We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.
+
+\begin{table}[!hpt]
+\begin{center}
+\caption{NGA50 improvement from $\mathtt{metaSPAdes}$ to \npgraph{} assembly on two mock communities ZymoLog and ZymoEven.
+The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio references of individual isolates \cite{Nick2019zymo}.}
+\label{table:zymo}
+\begin{tabular}{|l|r|r|r|r|}
+\hline
+\multirow{2}{*}{\textbf{Community}} & \multicolumn{2}{|c|}{\textbf{ZymoEven}} & \multicolumn{2}{|c|}{\textbf{ZymoLog}} \\ \cline{2-5}
+& $\mathtt{metaSPAdes}$ & \npgraph{} & $\mathtt{metaSPAdes}$ & \npgraph{} \\ \hline
+\emph{B.~subtilis} & $23,386$ & $382,368$ & $35,390$ & $433,078$ \\ \hline
+\emph{E.~coli} & $34,776$ & $1,108,989$ & $-$ & $-$ \\ \hline
+\emph{E.~faecalis} & $23,340$ & $217,908$ & $-$ & $-$ \\ \hline
+\emph{L.~monocytogenes} & $26,480$ & $520,012$ & $23,146$ & $130,284$ \\ \hline
+\emph{P.~aeruginosa} & $59,372$ & $1,753,658$ & $161,816$ & $444,495$ \\ \hline
+\emph{S.~aureus} & $26,058$ & $175,908$ & $-$ &$-$ \\ \hline
+\emph{S.~cerevisiae} & $-$ & $-$ & $-$ & $-$ \\ \hline
+\emph{S.~enterica} & $33,363$ & $4,242,458$ & $-$ & $-$ \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+To run \npgraph{} on the metagenomics data set, we firstly augmented binning information from using $\mathtt{metaBAT}$ \cite{Kang2015metabat} on the Illumina raw reads, before applying our method to the assembly graph generated by $\mathtt{metaSPAdes}$.
+The default parameter setting was remained as it was for isolate assembly.
+
+In terms of Illumina data, Even community had been sequenced by MiSeq platform which generated about 43-fold coverage while the Log community`s short-read data had been obtained from an Illumina HiSeq 1500, for about 156X coverage.
+Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser.
+This due to the fact of under-presented microbial cells from rare species in the log population that require much more input to compensate, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).
+
+Table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$ initial graph.  
+As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
+There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
+\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} from $33$ Kbp to $4.2$ Mbp. 
+On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as huge as the other.
+The longest NGA50 contigs belongs to \emph{P.aeruginosa} of 445 Kbp, however, the counterpart from the Even community was 4-fold than that, at 1.75 Mbp.
+The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective figure was 433 Kbp for the zymo log.
+It is noteworthy that for this case, initially the $\mathtt{metaSPAdes}$ assembly for the former was slightly better compared to the latter.
 

### 2019-11-18 paper.tex
conclusion

@@
 The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level.
-In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process.
+In addition, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process.
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
@@
 % \end{itemize}
-Streaming assembly methods have been proven to be useful in saving time and resources compared to the traditional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+Streaming assembly methods had been proven to be useful in saving time and resources compared to the conventional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
 The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
-This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a DBG construction while waiting for the data being retrieved.
+This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
+\npscarf{}, on the other hand, is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
+It functions by scaffolding the contigs using nanopore sequencing which is well-known by the real-time property.
+The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
 
-\npscarf{}, on the other hand, works on the available short-read assembly to scaffold the contigs using nanopore sequencing which is well-known by the real-time property.
-The completion of genome assembly along with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
-However, due to the greedy approach of a streaming algorithm, as well as being an alignment-based-only scaffolding mechanism, running the tool with default settings suffers from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}.
-In many case, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well.
-To tackle the quality issue while maintaining its streaming execution, an assembly graph processing system is investigated as it would provide an additional high-quality source of linking information for the assembly operations.
+% Why hybrid???
+Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
+On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the former`s assembly.
+As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
+\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
 
-After the construction of an assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
+However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s concurrent results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
+Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
+To tackle the quality issue while maintaining its streaming execution, a bridging method by assembly graph traversing is proposed. 
+In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
+
 Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
@@
 The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
-While the later approach employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
+While the latter method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
 For that reason, the first direction is more suitable for a real-time pipeline.
 
-However, the challenges to adapt this approach into a real-time mechanism are obvious and mainly come from the heavy path-finding task and the complication of self-improvement step which is critical to a streaming algorithm.
-A modified DFS algorithm and a voting system with accumulating scores calculation has been implemented to overcome these issues.
-This results in \npgraph{}, an user-friendly tool with GUI that can traverse the assembly graph and scaffold its components in real-time as long as the nanopore sequencing process is running and continuously generating long reads.
+Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph.
+A modified DFS (depth-first search) algorithm and a voting system with comprehensive scoringn system has been implemented to overcome these issues.
+This results in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection*{Hybrid assembly for synthetic data sets}
-To evaluate the performance of the method, \npgraph{} was benchmarked against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on the latter's testing data~ \cite{Wick2017unicycler} .
-This data set were simulations of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references.
-Specifically, the synthetic Illumina data was generated by using a wrapper script of ART~\cite{HuangLMM2012} that allows uniform coverage for circular genome sequencing with justifiable depths.
-PBSIM~\cite{OnoAH2012}, on the other hand, was used to simulate the long reads.
-
-There were three settings for each of the synthetic raw data (\emph{good, medium, bad}) corresponding to the quality, yield and length of reads being generated. 
-In the SGS simulation, the \emph{bad} data consist of 100bp paired-end reads with low and uneven coverage (40X) leading to many dead ends in the assembly graph due to missing regions in the genome. 
-The read length was 125bp in the \emph{medium} setting with better depth distributions that could cover the genome better. 
-Finally, the \emph{good} option provided best data sets with 150bp of read length and 100X coverage.
-While the quality of SGS reads would determine the assembly graph nature, the nanopore data plays critical role in graph resolving.
-The three settings leveled up the depth (8X, 16X, 32X) and at the same time, average length ($5$Kbp, $10$Kbp, $20$Kbp) and maximum identities (90\% ,95\% ,98\%) respectively.
-We only considered the \emph{good} configurations of both platforms for the sequence data being tested.
-Also, since the other comparative tools do not support streaming assembly, there were only batch-mode runs being carried out and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
+\subsection*{Evaluation using synthetic data}
+To evaluate the performance of the method, \npgraph{} was tested against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on Unicycler`s synthetic data set~ \cite{Wick2017unicycler} .
+The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references.
+We ran all hybrid assembly methods in batch-mode and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
 
@@
 
-Table~\ref{table:npgraph_compare} shows evaluation results for 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
+Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
 In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
@@
 
-In general, the graph integrated version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
+In general, the graph version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
 The only exception where the number of mis-assemblies being increased was the simulation of a random sequence with many repeats.
@@
 The errors mostly came from redundant sequences output from the software due to the failure in estimation of contig multiplicity.
-Even though using assembly graph for gap fillings, there were no changes in the way to determine if a contig is unique or not from \npscarfg{}. 
-It still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
+Even though using assembly graph for gap fillings, there were no changes in the way \npscarfg{} determine if a contig is unique or not. 
+Its implementation still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
 Redundant path findings for false positive replicons consequently returned additional wrong translocations in the final contigs which were reported by QUAST. 
@@
 Furthermore, in terms of running time and resources required, \minimap{} proved to be the best option. 
-The total CPU hours had been trimmed down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
+The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
 This feature is certainly more favoured to a real-time assembly as well.
@@
 
-It is noteworthy to discuss in more details the errors addressed in the above assembly methods.
-This figure measured the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
-As expected from hybrid assemblies where Illumina sequencing data were used as the main building blocks, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) for almost every case.
-In addition, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
+To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
+As expected from hybrid assembly method embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
+Furthermore, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
 The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
@@
 \subsection*{Hybrid assembly for real data sets}
-Several sequencing data sets of actual bacterial samples~\cite{George2017M14} were used in this scenario.
-The data included both Illumina paired-end and MinION sequencing based-call data for each sample.
-Unlike previous settings, rather than the default output, the optimal \spades{} assembly graph detected by \unicycler{} were used for \npgraph{} algorithm as well.
-This step had been proved to be useful in selecting the best graph available, amongst \spades{} runs with ranging $k$-mer values, that have dead-ends and number of contigs minimized~\cite{Wick2017unicycler}.
-Likewise, as mentioned before, the quality of the initial assembly graph would considerably influence the final results of \npgraph{}.
-
-Due to the lack of available reference genomes, fewer statistics were reported by QUAST for the comparison of the results. 
+A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used in this scenario.
+The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
+Due to the unavailability of reference genomes, there were fewer statistics being reported by QUAST for the comparison of the results. 
 Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies.
@@
 
-The assembly task for \emph{Enterobacter~cloacae} was more challenging as the chromosomal DNA sequence was not been fully resolved using either method. 
+The assembly task for \emph{Enterobacter~cloacae} was observed more challenging as the chromosomal DNA sequence not been fully resolved using either method. 
 The chromosome size was estimated to be approximately $4.8$Mbp but had been broken into two smaller pieces. 
@@
 
-\subsection*{Real-time mode hybrid assembly}
+\subsection*{Assembly performance on streaming data}
 Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
@@
 
-\subsection*{Metagenomics assembly}
+\subsection*{Metagenomics assembly on mock community}
 We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
@@
 \begin{center}
-\caption{NGA50 improvement from $\mathtt{metaSPAdes}$ to \npgraph{} assembly on two mock communities ZymoLog and ZymoEven.
-The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio references of individual isolates \cite{Nick2019zymo}.}
+\caption{Assembly improvement, in terms of NGA50 statistics, from $\mathtt{metaSPAdes}$ to \npgraph{} contigs on two mock communities ZymoLog and ZymoEven \cite{Nick2019zymo}.
+The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio isolate assemblies used as reference \cite{Mcintyre2019zymo}.}
 \label{table:zymo}
@@
 Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser.
-This due to the fact of under-presented microbial cells from rare species in the log population that require much more input to compensate, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).
+This happened due to the fact of under-presented microbial cells from rare species in the Log population that require much more input for their reads to be sequenced, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).
+The assembly size for the two population are approximately 41 Mbp (66\%) and 22 Mbp (36\%). 
+During pre-processing step, \npgraph{} disregarded nodes which represent short, unconnected and extremely-low-coverage contigs which were indistinguishable from sequencing errors, artifacts or the actual rare species` genomes without additional works.
 
-Table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$ initial graph.  
+Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$ initial graph.  
 As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
 There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
-\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} from $33$ Kbp to $4.2$ Mbp. 
-On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as huge as the other.
+\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} boosted from $33$ Kbp to $4.2$ Mbp. 
+On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as distinct as for the balanced colony.
 The longest NGA50 contigs belongs to \emph{P.aeruginosa} of 445 Kbp, however, the counterpart from the Even community was 4-fold than that, at 1.75 Mbp.
-The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective figure was 433 Kbp for the zymo log.
-It is noteworthy that for this case, initially the $\mathtt{metaSPAdes}$ assembly for the former was slightly better compared to the latter.
+The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective statistics was 433 Kbp for the zymo log.
+However for this isolate, the initial $\mathtt{metaSPAdes}$ assembly of the former was slightly better compared to the latter`s.
+
+%how much nanopore needed indeed
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusions}
-Assembly graph is the data structure describing the assembly components at  more details.
-The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block for the assembly construction method (\npgraph{}).
+\section*{Conclusion}
+%npgraph: how important hybrid assembly
+Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
+On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield, however, the sequencing cost per base is still high.
+Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
+\npscarf{} had been introduced initially to address these issues, however, the accuracy of the assembly output was affected by its greedy alignment-based scaffolding approach.
+Here we present \npgraph{}, a streaming hybrid assembly method working on the DBG assembly graph that is able to finish short-read assembly in real-time while minimizing the errors and mis-assemblies drastically.
 
-While the first approach showed improvements in terms of base's accuracy for the final results, it had limited ability in rectifying the mis-assemblies from the original version due to false positive alignments at contig level.
-The issue can be tackled by applying the assembly graph completely as in \npgraph{}.
-With a more conservative bridging method applied, the new method may consume more data to confidently construct the assembly but at the same time, the number of mis-located fragments has reduced significantly.
-Furthermore, users can monitor the assembly in an interactive manner providing the assembly GUI.
+Compared to \npscarf, \npgraph{} employs less greedy approach based on graph traversal.
+This might reduce the bridging rate when the linking conditions become more strict, but the concurrent results reported are more reliable.
+The performance of \npgraph{} is comparable to \unicycler{} while consuming much less computational resources so that it can work on streaming mode. 
+In addition, the integrated GUI allows users to interact in more efficient way.
 
-Compared to the other hybrid assemblers of similar methodology, such as $\mathtt{hybridSPAdes}$ and \unicycler{}, there are still rooms for further development of \npgraph{}. 
-More comprehensive pre-processing step is needed for a better input graph possible since it would affect the completeness of final results.
+As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
+The algorithm operates on the assumption of a high quality assembly from sufficient Illumina data that produces decent assembly graph, with a minimal amount of long reads data possible.
+A fragmented initial graph directly affects the quality of the final assembly, independant from the abundance of nanopore data.
+This issue has been reflected via our attempt to apply \npgraph{} on the zymo metagenomics data.
 
-Importantly, a robust real-time voting system should be implemented to be able to detect the most probable path amongst all candidates in an efficient way.
-This would alleviate the data consumption of the \npgraph{} while at the same time, maintain high confident and accurate scaffolding.
+%metagenomics attempt, how to improve?
 
@@
 
-Basically the work flow of \npgraph{} consists of 3 main modules: (1) assembly graph loading and preprocessing; (2) graph resolving; (3) postprocessing and reporting results. 
+The work flow of \npgraph{} consists of 3 stages: (1) assembly graph preprocessing; (2) graph resolving and simplifying; (3) postprocessing and reporting results. 
 The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
-By using this information, in combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time.
+The second step works on the processed input and augmented information from the previous one.
+In combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time.
 Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
@@
 Each population is expected to include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
-In addition, the binning phase would assist to differentiate between repetitive contigs and unique ones.
+In addition, the binning phase would assist the multiplicity estimation submodule that can differentiate repetitive contigs from unique ones.
 
-Each contig is represented as a single node in the assembly graph and an edge between two nodes indicate their overlap (link) properties.
-This step is to cluster the longest nodes (longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
+Each contig is represented as a single node in the assembly graph and an edge between two nodes indicates their overlap (link) properties.
+This step is to cluster the biggest nodes (contigs longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
 DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task by default.
@@
 In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
-\subsection*{Assembly graph resolving in real-time}
-\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that could be generated in real-time.
-Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path.
+\subsection*{Graph simplification in real-time}
+\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that can be provided in real-time.
+Whenever a bridge is finished (with a unique linking path), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path with a composite edge and removing any unique edges (edges coming from unique nodes) along the path.
 The assembly graph would have at least one edge less than the original after the reduction.
@@
 
-The final assembly output contains files in both FASTA and GFA v1 format (\url{https://github.com/GFA-spec/GFA-spec}).
-While the former only retains the actual genome sequences from the final decomposed graph, the latter output file can store almost every properties of the ultimate un-masked graph such as nodes, links and potential paths between them.
+The final assembly output contains files in both FASTA and GFAv1 format (\url{https://github.com/GFA-spec/GFA-spec}).
+While the former only retains the actual genome sequences from the final decomposed graph, the latter output file can store almost every properties of the ultimate graph such as nodes, links and potential paths between them.
+
+Other than that, if GUI mode is enabled, basic assembly statistics such as N50, N75, maximal contigs length, number of contigs can be visually reported to the users in real-time beside the Dashboard.
+The progressive simplification of the assembly graph can also be observed at the same time in the Graph view.
 

### 2019-11-19 paper.tex
bmc

@@
 Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph.
-A modified DFS (depth-first search) algorithm and a voting system with comprehensive scoringn system has been implemented to overcome these issues.
+A modified DFS (depth-first search) algorithm and a progressive voting algorithm has been implemented to overcome these issues.
 This results in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
@@
 
-Compared to \npscarf, \npgraph{} employs less greedy approach based on graph traversal.
+Compared to \npscarf, \npgraph{} algorithm employs a less greedy approach based on graph traversal.
 This might reduce the bridging rate when the linking conditions become more strict, but the concurrent results reported are more reliable.
 The performance of \npgraph{} is comparable to \unicycler{} while consuming much less computational resources so that it can work on streaming mode. 
-In addition, the integrated GUI allows users to interact in more efficient way.
+Also, the integrated GUI allows users to visualize its animated output in a  more efficient way.
 
+In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity.
+The assembler was able to handle the De Bruijin assembly graph from Illumina data generated by $\mathtt{metaSPAdes}$ and simplify it using a minimal input stream of long reads.
+The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference.
+The issue is reasoned by the insufficient short-read input to cover underpresented species in the mixture, especially in the case of Log community.
 As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
 The algorithm operates on the assumption of a high quality assembly from sufficient Illumina data that produces decent assembly graph, with a minimal amount of long reads data possible.
-A fragmented initial graph directly affects the quality of the final assembly, independant from the abundance of nanopore data.
-This issue has been reflected via our attempt to apply \npgraph{} on the zymo metagenomics data.
+A fragmented initial graph directly affects the quality of the final assembly, free from the abundance of nanopore data.
 
@@
 \subsection*{Graph simplification in real-time}
-\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that can be provided in real-time.
+\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that can be streamed in real-time.
 Whenever a bridge is finished (with a unique linking path), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path with a composite edge and removing any unique edges (edges coming from unique nodes) along the path.

### 2019-11-19 paper.tex
fsdf

@@
 A modified DFS (depth-first search) algorithm and a progressive voting algorithm has been implemented to overcome these issues.
-This results in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.  
+The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference.
-The issue is reasoned by the insufficient short-read input to cover underpresented species in the mixture, especially in the case of Log community.
+The issue is caused by the shortage of short-read sequencing input to cover underpresented species in the mixture, especially for the Log community.
+
 As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
-The algorithm operates on the assumption of a high quality assembly from sufficient Illumina data that produces decent assembly graph, with a minimal amount of long reads data possible.
-A fragmented initial graph directly affects the quality of the final assembly, free from the abundance of nanopore data.
-
-%metagenomics attempt, how to improve?
+The algorithm operates on the assumption of a high quality assembly from a well-supplied source of short-read data for a decent assembly graph to begin with.
+It then consumes a just-enought amount of data from a streaming input of nanopore reads to resolve the graph. 
+In summary, extra pre-processing and comprehensive binning for the initial graph could further improve the performance of \npgraph{}.
 

### 2019-11-20 paper.tex
proof-reading

@@
 It then consumes a just-enought amount of data from a streaming input of nanopore reads to resolve the graph. 
-In summary, extra pre-processing and comprehensive binning for the initial graph could further improve the performance of \npgraph{}.
+Finally, extra pre-processing and comprehensive binning on the initial graph could further improve the performance of the streaming assembler.
 
@@
 
-The work flow of \npgraph{} consists of 3 stages: (1) assembly graph preprocessing; (2) graph resolving and simplifying; (3) postprocessing and reporting results. 
+The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph preprocessing; (2) graph resolving and simplifying; (3) postprocessing and reporting results. 
 The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
@@
 \subsection*{Contigs binning}
-Each population is expected to include contigs of the similar abundance in the final assembly sequences, \EG{} chromosome , plasmids, or even particular species genome in a metagenomics community.
-In addition, the binning phase would assist the multiplicity estimation submodule that can differentiate repetitive contigs from unique ones.
+Contigs from each completed genome are expected to be assigned to an unique group, or \emph{bin}, that would represent the final assembly unit, \EG{} chromosome , plasmids, or even particular species genome in a metagenomic community.
+As a result, the binning phase would assist the multiplicity estimation submodule that can differentiate repetitive contigs from unique ones.
 
-Each contig is represented as a single node in the assembly graph and an edge between two nodes indicates their overlap (link) properties.
+Each contig is embeded in a single node in the assembly graph and an edge between two nodes indicates their overlap (link) properties.
 This step is to cluster the biggest nodes (contigs longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.

### 2019-11-20 paper.tex
proof-reading

@@
 It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide.
-The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level.
-In addition, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process.
+The application on synthetic and real data set of isolate genomes show improved accuracy while still maintaining the required computational cost extremely low.
+On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data.
+With \npscarf{}, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process.
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
@@
 \begin{longtable}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
-\caption[Comparison of assemblies using \npgraph{} and other comparative methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and the comparative methods on 5 synthetic data sets taken from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\
+\caption[Comparison of assemblies using \npgraph{} and other comparative methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and the comparative methods on 5 \unicycler{}`s synthetic data sets downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\
 
@@
     \cthead{3}{Run times} \\
-    & \cthead{1}{Method} & \cthead{1}{size (Mb)} & \cthead{1}{\#Contigs} &
-    \cthead{1}{(Kp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kb)} &  
+    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
+    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
     \cthead{3}{(CPU hrs)} \\
@@
 This feature is certainly more favoured to a real-time assembly as well.
-As the consequence, as long as \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it would likewise become the main aligner for \npgraph{} pipeline in the future.
+Because \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner for \npgraph{} pipeline.
 
-To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100kpb from the assembly sequences when mapping to the reference.
+To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100 Kbp from the assembly sequences when mapping to the reference.
 As expected from hybrid assembly method embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
@@
 Five out of six identical replicons were confirmed as plasmids based on the occurences of appropriate Origin of replication sequences (PlasmidFinder database).
-In detail, two megaplasmids (longer than $100$Kpb) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kpb, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
+In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
 The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or newly replicon's DNA.
@@
 While the latter were recognized by both methods, the longer plasmid sequence was fragmented running \npgraph{}.
-Similar to the previous data set, there were around $14$Kpb of data were unable to be finished by the assemblers.
+Similar to the previous data set, there were around $14$Kbp of data were unable to be finished by the assemblers.
 
@@
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will present a contig for the result (Supplementary Note \ref{supp:note6}).
-
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will spell a contig in the assembly report (Supplementary Note \ref{supp:note6}).
 The final assembly output contains files in both FASTA and GFAv1 format (\url{https://github.com/GFA-spec/GFA-spec}).

### 2019-11-20 paper.tex
proof-reading

@@
 
-%Display watermark DRAFT
-%\watermark{DRAFT}
-
 %% use \onecolumn for onecolumn paper
@@
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
-%=======
-%A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses.
-The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies.
-Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs.
-The results show improved accuracy while still minimize the required computational cost.
-The tool is available at \url{https://github.com/hsnguyen/assembly}.
-%>>>>>>> 2d4c481dd93902dfb2dabe46534a62e8a8c2058c
 } 
-
 %Set keywords
@@
 
-Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, the output of the full run can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
+Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, report for the whole comparison can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
 In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
@@
 The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
-This feature is certainly more favoured to a real-time assembly as well.
+This feature is certainly more favoured for a real-time assembly pipeline that normally requires quick responses in very short intervals.
 Because \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner for \npgraph{} pipeline.
@@
 To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100 Kbp from the assembly sequences when mapping to the reference.
-As expected from hybrid assembly method embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
+As expected from hybrid assembly methods embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
 Furthermore, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
@@
 \unicycler{}, which employs an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads, returned the second best reliable and at the same time, closest-to-complete results overall.
-\npscarf{}, on the other hand, exploited the long reads for the gap filling thus inherited the high error rates from them.
+\npscarf{}, on the other hand, employed the long reads for the gap filling thus inherited the high error rates from them.
 By integrating the assembly graph for the task, the errors were reduced in general (random sequences, \emph{M.~tuberculosis}, \emph{S.suis} from Table~\ref{table:npgraph_compare}) but not completely since the mis-placed contigs were still not resolved in other circumstances.

### 2019-11-24 paper.tex
before big change

@@
 \newcommand{\spades}{$\mathtt{SPAdes}$}
+\newcommand{\hspades}{$\mathtt{hybridSPAdes}$}
 \newcommand{\albacore}{$\mathtt{Albacore}$}
@@
 Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
-On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the former`s assembly.
+On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
 As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
@@
 
-However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s concurrent results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
 A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
 Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
-To tackle the quality issue while maintaining its streaming execution, a bridging method by assembly graph traversing is proposed. 
+To tackle the quality issue while maintaining its streaming feature, a bridging method by assembly graph traversing is proposed. 
 In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
@@
 
-Nonetheless, the challenges to adapt this approach into a real-time mechanism are obvious, mainly from building a progressive, self-updating path-finding and graph reducing method which are required for a streaming assembler on graph.
-A modified DFS (depth-first search) algorithm and a progressive voting algorithm has been implemented to overcome these issues.
+Nonetheless, the challenge to adapt this approach into a real-time mechanism is obvious, mainly from building a progressive implementation for path-finding and graph reducing module which are essential for a streaming graph assembler.
+To achieve that, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
 The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.
+
+We use different hybrid data sets to study the \npgraph{}`s performance and compare with other available tools with similar functionality, such as \npscarf{}, \unicycler{} and \hspades{}.
+Even though all data were from microbial genomes, the complexity of the input graphs range from few hundred to ten thousands of components, synthesized \emph{in silico} or sequenced from \emph{in vitro} samples.
+Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
+We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
+In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
+Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  & SPAdes  & 3.928 & 226  & 40.5  &  0 &  0.00 &  0.95 &  &  \\*
- & SPAdes-Hybrid  & 4.109 & 3  & 4,000.0  & 0  & 0.85  & 1.196  &  &  \\*
+ & SPAdes-Hybrid  & 4.108 & 3  & 3,999.6  & 0  & 0.83  & 1.196  &  &  \\*
  & Unicycler  & 4.110 & 3  & 4,000.0  &  0 &  0.47 & 6.783  &  &  \\*

### 2019-11-25 paper.tex
preprint

@@
 \fi
+
+\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
+\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
+\SetCommentSty{mycommfont}
+% For code embedding (Bash, Java...)
+\usepackage{listings}
+\lstset{basicstyle=\ttfamily,
+  showstringspaces=false,
+  commentstyle=\color{red},
+  keywordstyle=\color{blue}
+}
+\usepackage{latexsym}
+\usepackage{mathtools}
+\usepackage{amsmath}
+\DeclareMathOperator*{\argmax}{argmax}
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 \rowcolor{Gray} \multicolumn{10}{l}
-{ random sequence with repeats} \\*  
- & SPAdes  & 3.928 & 226  & 40.5  &  0 &  0.00 &  0.95 &  &  \\*
- & SPAdes-Hybrid  & 4.108 & 3  & 3,999.6  & 0  & 0.83  & 1.196  &  &  \\*
- & Unicycler  & 4.110 & 3  & 4,000.0  &  0 &  0.47 & 6.783  &  &  \\*
- & npScarf  & 4.251 &  9 & 3,952.2  &  27 &  8.74 &  0.95 & + & 0.39 \\*
- & npScarf\_wag & 4.554 & 9  &  3,999.6 &  37 &  6.16 &  0.95 & + &  0.45\\*
- & npGraph (bwa)  & 4.110 & 3  & 4,000.0  & 0  &  0.47 &  0.95 & + &  0.33\\*
- & ngGraph (minimap2)  & 4.110 & 3  & 4,000.0  & 0  & 0.47  &  0.95 & + &  0.02\\
+{\emph{Mycobacterium~tuberculosis} H37Rv: 4,411,532bp} \\*  
+& SPAdes & 4.376 & 66 & 150.7 & 0 & 0.23 & 1.42 & & \\*
+& SPAdes hybrid & 4.411 & 1 & 4410.5 & 0 & 0.86 & 1.61 & & \\*
+& Unicycler & 4.412 & 1 & 4411.5 & 0 & 2.56 & 5.52 & & \\*
+& npScarf & 4.432 & 4 & 4402.2 & 7 & 6.61 & 1.42 & + & 0.7 \\*
+& npGraph (bwa) & 4.411 & 1 & 4411.4 & 0 & 2.63 & 1.42 & + & 0.64 \\*
+& npGraph (minimap2) & 4.412 & 1 & 4411.5 & 0 & 0.68 & 1.42 & + & 0.02 \\*
 \rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Mycobacterium tuberculosis} H37Rv} \\*  
- & SPAdes  & 4.371 & 114  &  125.5 &  1 & 1.51  &  1.55 &  &  \\*
- & SPAdes-Hybrid  & 4.411 & 1  & 4,411.2  & 0  & 1.73  & 1.68  &  &  \\*
- & Unicycler  & 4.412 &  1 &  4,411.5 & 0  &  2.56 &  6.36 &  &  \\*
- & npScarf  & 4.446 & 4  & 4,389.9  & 12  &  11.41 & 1.55  & + & 0.78 \\*
- & npScarf\_wag  & 4.408 & 1  & 4,407.6  &  2 &  7.01 & 1.55  & + & 0.79 \\*
- & npGraph (bwa)  & 4.411 &  1 & 4,411.6  &  0 & 7.28  &  1.55 & + & 0.63 \\*
- & ngGraph (minimap2)  & 4.411 & 1 & 4,411.4  &  0 &  7.01 & 1.55  & + &  0.02\\
+{\emph{Saccharomyces~cerevisiae} S288c: 12,157,105 bp} \\*  
+& SPAdes & 11.675 & 194 & 260.5 & 0 & 1.57 & 3.61 & & \\*
+& SPAdes hybrid & 11.910 & 45 & 770.5 & 5 & 34.52 & 4.15 & & \\*
+& Unicycler & 11.837 & 29 & 909.1 & 0 & 22.83 & 16.34 & & \\*
+& npScarf & 11.990 & 22 & 796.8 & 53 & 85.5 & 3.61 & + & 4.35 \\*
+& npGraph (bwa) & 12.000 & 151 & 913.1 & 3 & 38.68 & 3.61 & + & 4.12 \\*
+& npGraph (minimap2) & 12.008 & 148 & 913.1 & 5 & 25.32 & 3.61 & + & 0.13 \\*
 \rowcolor{Gray} \multicolumn{10}{l}
-{\ec{} O25b H4-ST131} \\*  
- & SPAdes  & 5.173 &  159 & 191.0  &  1 &  1.69 & 1.26  &  &  \\*
- & SPAdes-Hybrid  & 5.249 &  7 &  5,109.6 & 0  & 2.65  & 1.40  &  &  \\*
- & Unicycler  & 5.249 &  3 & 5,109.8  &  0 &  4.29 &  4.70 &  &  \\*
- & npScarf  & 5.354 & 7  & 5,087.5  &  14 & 29.12  &  1.26 & + &  0.78\\*
- & npScarf\_wag  & 5.413 &  7 & 5,108.1  & 6  &  30.29 & 1.26  & + & 0.78 \\*
- & npGraph (bwa)  & 5.252 & 3  &  5,112.3 &  0 & 16.37  & 1.26  & + &  0.66\\*
- & ngGraph (minimap2)  & 5.250 & 3  & 5,111.1  & 0  & 14.61  &  1.26 & + & 0.03 \\
+{\emph{Shigella~sonnei} 53G: 5,220,473 bp} \\*  
+& SPAdes & 4.796 & 392 & 27.7 & 0 & 0.44 & 1.1 & & \\*
+& SPAdes hybrid & 5.218 & 8 & 2195.5 & 2 & 41.98 & 1.36 & & \\*
+& Unicycler & 5.221 & 5 & 4988.5 & 0 & 7.91 & 9.64 & & \\*
+& npScarf & 6.426 & 20 & 1293.8 & 84 & 366.04 & 1.1 & + & 0.52 \\*
+& npGraph (bwa) & 5.293 & 97 & 4988.5 & 3 & 14.87 & 1.1 & + & 0.57 \\*
+& npGraph (minimap2) & 5.293 & 97 & 4988.5 & 3 & 8.31 & 1.1 & + & 0.08 \\*
 \rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Streptococcus suis} BM407} \\*  
- & SPAdes  & 2.119 &  81 &  131.0 & 0  & 3.84  & 0.59  &  &  \\*
- & SPAdes-Hybrid  & 2.147 & 48  &  1,438.0 &  0 &  0.98 & 0.65  &  &  \\*
- & Unicycler  & 2.171 &  2 &  2,146.2 & 0  &  2.99 &  2.58  &  &  \\*
- & npScarf  & 2.220 &  4 &  2,120.0  & 9  & 97.20  & 0.59 & + & 0.31 \\*
- & npScarf\_wag  & 2.245 & 4  &  2,128.3  & 3  &  89.64 & 0.59 & + &  0.31\\*
- & npGraph (bwa)  & 2.167 & 6  & 2,146.7  &  0 &  26.77 & 0.59  & + &  0.21\\*
- & ngGraph (minimap2)  & 2.167 & 6  &  2,146.2 &  0 & 22.53  &  0.59 & + & 0.01 \\
-\rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Acinetobacter} AB30} \\*  
- & SPAdes  & 4.134 & 265  & 42.5  &  0 &  3.23 & 0.95  &  &  \\*
- & SPAdes-Hybrid  & 4.287 & 49  &  3,308.0 &  0 & 5.04  & 1.84  &  &  \\*
- & Unicycler  & 4.333 & 1  &  4,333.0 &  1 & 6.95  &  5.27 &  &  \\*
- & npScarf  & 4.595 & 11  & 4,299.7  & 1  & 120.99  & 0.95  & + & 0.45 \\*
- & npScarf\_wag  & - & -  &  - & -  &  - &  - &  &  \\*
- & npGraph (bwa)  & 4.317 & 6  &  2,766.9 & 1  &  39.82 &  0.95 & + & 0.41 \\*
- & ngGraph (minimap2)  & 4.337 & 1  &  4,336.8 & 0  & 24.71  & 0.95  & + & 0.03 \\
+{\emph{Shigella~dysenteriae} Sd197: 4,560,911 bp} \\*  
+& SPAdes & 4.096 & 534 & 14.4 & 1 & 0.68 & 1.19 & & \\*
+& SPAdes hybrid & 4.486 & 23 & 821.2 & 96 & 10.99 & 1.89 & & \\*
+& Unicycler & 4.561 & 3 & 4369.2 & 0 & 12.96 & 8.46 & & \\*
+& npScarf & 4.649 & 174 & 41.8 & 65 & 372.87 & 1.19 & + & 0.62 \\*
+& npGraph (bwa) & 4.553 & 3 & 4369.1 & 6 & 91.03 & 1.19 & + & 0.76 \\*
+& npGraph (minimap2) & 4.548 & 3 & 4364.1 & 8 & 83.68 & 1.19 & + & 0.14 \\*
+
 \end{longtable}
@@
 DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task by default.
-The rationale is to approximate a coverage value of a significant contig (which can be splitted into more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count).
+The rationale is to approximate a coverage value of an extremely long contig (which can be splitted into more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count).
 The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
-Other than that, external binning tools can be employed for more complicated binning task, \EG{} metagenomics, and the results can be integrated into \npgraph{} for better performance.
-More details can be found on Supplementary Note \ref{supp:note1}.
 
+Assuming there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
+The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
+$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
+or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
+The log ratio of the density functions is
+$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
+$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+The metric we used is the distance defined as
+$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
+
+We implemented a simple binning algorithm based on the clustered contigs, the graph topology as well as statistics calculated by length and coverage of each contigs. 
+Additional binning step is taken place in real-time using the long reads as well.
+In this context, the repetition or uniquess of ambigous nodes are determined with sufficient supporting evidence from the long-spanning reads.
+Generally, the algorithm performs well for isolate or simple simulated metagenomics, but ineffective for complicated community.
+In that case, external binning tools can be employed for more comprehensive binning task and the results can be augmented to \npgraph{} input.
+If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT.
+By that, each line of the file would be:
+$
+\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
+$
+where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
 \subsection*{Multiplicity estimation}
-Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially for the shorter contigs, an optimization step is carried out to alleviate this issue as shown in Supplementary Note \ref{supp:note2}.
+Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially for the shorter contigs, an optimization step is carried out to alleviate this issue.
+The re-estimation is basically carried out by following two steps.
+\begin{itemize}
+\item[1.] From nodes coverage, estimate edges' value by quadratic unconstrained optimization of the least-square function:
+$$\frac{1}{2}\sum_{i}{l_i((\sum{e^{+}_{i}}-c_i)^2+(\sum{e^{-}_{i}}-c_i)^2}$$
+where $l_i$ and $c_i$ is the length and coverage of a node $i$ in the graph;
+
+$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
+The above function and be rewritten as:
+$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
+and then being minimized by using gradient-based method.
+\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
+\end{itemize}
+The calibration is iterative until no further improvements are made or a threshold loop count is reached.
 The coverage measures of nodes (which represent contigs) are propated throughout the graph via connecting edges for calibrations prior to the multiplicity estimation. 
@@
 Furthermore, the streaming fashion of this method allows the bridge constructions (updating steps and spans) to be carried out progressively so that assembly decisions can be made immediately after having sufficient supporting data.
-The detail implementation is addressed in Supplementary Note~\ref{supp:note4}.
-
 A bridge in \npgraph{} has several completion levels.
@@
 A bridge is known as fully complete (level 4) if and only if there is a unique path connecting its two anchor nodes from two ends.
+
+\begin{figure}[!hpt]
+\centering
+\includegraphics[width=.8\textwidth]{images/bridge_merging.pdf}
+\caption[Example of bridge merging progressively]{Bridge merging progressively in real-time.
+Sequencing long reads induce alignments to the contigs where new bridges are created respectively.
+Bridges sharing same anchors can be merged together to form the ultimate, more comprehensive bridge (with more step nodes and better approximation of spans between them).}
+\label{figure:npgraph_merging}
+\end{figure}
+
+At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
+In an example from Figure~\ref{figure:npgraph_merging}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+Each of the steps therefore is assigned a weighing score based on its alignment quality.
+Due to the error rate of long reads, there should be deviations in terms of steps found and spans measured between these bridges, eventhough they represent the same connection.
+A continuous merging phase, as shown in the figure, takes advantage of a pairwise Needleman-Wunsch dynamic programming to generate a consensus list based on weight and position of each of every stepping nodes.
+The spans are calibrated accordingly by averaging out the distances.
+On the other hand, the score of the merged steps are accumulated over time as well.
+Whenever a consensus bridge is anchored by 2 unique contigs at both ends and hosting a list of steps with sufficient coverage, it is ready for a path finding in the next step.
 
@@
 As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search (Supplementary Note~\ref{supp:note5}).
+We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search.
 
-It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments.
+Due to false alignments from shorter contigs to the long reads, not all of the reported step nodes are neccessary to be appeared in the ultimate path resolved by the bridge. 
+In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
+For that reason, a strategy similar to binary searching is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
+
+Before that, we define Algorithm~\ref{algo:findpath} to demonstrates the path finding algorithm for two nodes given their estimated distance. In which, function 
+$\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n$ 
+from line 3 of the algorithm's pseudo code builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance regarding nanopore read error rate) is reached.
+This task is implemented based on Dijkstra algorithm.
+This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.
+
+\begin{algorithm}[!hpt]
+\DontPrintSemicolon
+\KwData{Assembly graph $G\{V,E\}$}
+\KwIn{Pair of bidirected nodes $\overrightarrow{v_1}, \overrightarrow{v_2}$ and estimated distance $d$ between them}
+\KwOut{Set of candidate paths connecting $\overrightarrow{v_1}$ to $\overrightarrow{v_2}$ with reasonable distances compared to $d$}
+\SetKwFunction{DFS}{DFS} 
+\SetKwProg{Fn}{Function}{:}{}
+\Fn{\DFS{$\overrightarrow{v_1}, \overrightarrow{v_2}$, $d$}}{
+$P$:=new List()\;
+$M$:=$\mathtt{shortestTree}(\overrightarrow{v_2},d)$ \tcp*{build shortest tree from $\overrightarrow{v_2}$ with range $d$}
+\If{$M.contain(\overrightarrow{v_1})$}{
+    $S$:=new $Stack()$ \tcp*{stack of sets of edges to traverse}
+    $edgesSet$:=$getEdges(\overrightarrow{v_1})$ \tcp*{get all bidirected edges going from $\overrightarrow{v_1}$}
+    $S.push(edgesSet)$\;
+    $p$:=new $Path(\overrightarrow{v_1})$ \tcp*{init a path that has $\overrightarrow{v_1}$ as root}
+    \While{true}{
+        $edgesSet$:=$S.peek()$\;
+        \If{$edgesSet.isEmpty()$}{
+            \If{$p.size() \leq 1$}{
+                $\mathbf{break}$ \tcp*{stop the loop when there is no more edge to discover}
+            }
+        $S.pop()$\;
+        $d$+=$p.peekNode.length()+p.popEdge().length()$\; 
+        }
+        \Else{
+            $curEdge \coloneqq edgesSet.remove()$\;
+            $\overrightarrow{v}$:=$curEdge.getOpposite(p.peekNode())$\;
+            $S.push(getEdges(\overrightarrow{v}).includedIn(M))$\;
+            $p.add(curEdge)$\;
+            \If{reach $\overrightarrow{v_2}$ with reasonable $d$}{
+                $P.add(p)$\;
+            }
+            $d$-=$\overrightarrow{v}.length()+curEdge.length()$\;
+        }
+    }
+}
+
+\Return{$P$}
+}
+\caption{Pseudo-code for finding paths connecting 2 nodes given their estimated distance.}
+\label{algo:findpath}
+\end{algorithm}
+
+\begin{algorithm}[!hpt]
+\DontPrintSemicolon
+\KwData{Assembly graph $G\{V,E\}$}
+\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps inbetween}
+\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_2}$ that maximize the likelihood of the step list.}
+\SetKwFunction{BinaryBridging}{BinaryBridging} 
+\SetKwProg{Fn}{Function}{:}{}
+\Fn{\BinaryBridging{B}}{
+\tcc{search for the contig with maximum score from the step list (two ends excluded)}
+$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
+\tcc{if there is no step inbetween, run path finding algorithm above directly and return the result}
+\If{$M.size() \equiv 2$}{ 
+	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
+}
+\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
+$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
+$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
+\tcc{Return the join of running recursive function on two sub-bridges}
+\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
+}
+\caption{Recursive binary bridging to connect 2 anchor nodes.}
+\label{algo:binsearch}
+\end{algorithm}
+
+Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover.
+During the traversal, a variable $d$ is updated as an estimation for the distance to the target.
+A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21).
+A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.
+
+Note that the $length()$ functions for node and edge are totally different.
+While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges).
+For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.
+
+In many cases, due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments.
 In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
@@
 
+\begin{figure}[!hpt]
+\centering
+\subfloat[Initial graph]{
+	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_0.png}
+}
+\hfill
+\subfloat[Resolved graph]{
+	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_2.png}
+}
+\caption[Assembly graph resolving on \npgraph{} Graph View]{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
+The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
+\label{figure:npgraph_graphview}
+\end{figure}
+
+Figure~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
+The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
+Smaller fragments, even unfinished but with high remaining coverage, are also presented as potential candidates for further downstream analysis.
+Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
 \subsection*{Result extraction and output}
-\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will spell a contig in the assembly report (Supplementary Note \ref{supp:note6}).
+\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will spell a contig in the assembly report.
 The final assembly output contains files in both FASTA and GFAv1 format (\url{https://github.com/GFA-spec/GFA-spec}).
 While the former only retains the actual genome sequences from the final decomposed graph, the latter output file can store almost every properties of the ultimate graph such as nodes, links and potential paths between them.
+
+A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if and only if each of every edges along the path $e_i, \forall i=1,\ldots,k$ is the only option to traverse from either $v_{i-1}$ or $v_i$, giving the transition rule.
+To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}.
+These edges are defined as branching edges which stop straight paths from further extending.
+
+\begin{figure}[!hpt]
+\centering
+\includegraphics[width=.6\textwidth]{images/decompose.pdf}
+\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths.
+Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report.
+There would be 3 contigs extracted by traversing along the straight paths here.}
+\label{figure:npgraph_decompose}
+\end{figure}
+
+The decomposed graph is only used to report the contigs that can be extracted from an assembly graph at certain time point.
+For that reason, the branching edges are only masked but not removed from the original graph as they would be used for further bridging.
 

### 2019-11-26 paper.tex
rewrite results

@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} was tested against \spades{} with its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{} with/without assembly graph integrated, and Unicycler version 0.4.6 on Unicycler`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{}, and Unicycler version 0.4.6 using Unicycler`s synthetic data set~ \cite{Wick2017unicycler} .
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references. 
@@
 \begin{longtable}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
-\caption[Comparison of assemblies using \npgraph{} and other comparative methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and the comparative methods on 5 \unicycler{}`s synthetic data sets downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\
+\caption[Comparison of assemblies using \npgraph{} and other methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\
 
@@
 
-\rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Mycobacterium~tuberculosis} H37Rv: 4,411,532bp} \\*  
+\rowcolor{Gray}
+& \emph{M.~tuberculosis} H37Rv & \multicolumn{8}{l} {4,411,532 bp} \\*  
 & SPAdes & 4.376 & 66 & 150.7 & 0 & 0.23 & 1.42 & & \\*
@@
 & npGraph (minimap2) & 4.412 & 1 & 4411.5 & 0 & 0.68 & 1.42 & + & 0.02 \\*
-\rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Saccharomyces~cerevisiae} S288c: 12,157,105 bp} \\*  
+\rowcolor{Gray} 
+& \emph{K.~pneumoniae} 30660 & \multicolumn{8}{l} {5,540,936 bp} \\*  
+& SPAdes & 5.469 & 64 & 270.2 & 0 & 0.07 & 1.36 & & \\*
+& SPAdes hybrid & 5.543 & 8 & 4229.1 & 2 & 5.04 & 1.63 & & \\*
+& Unicycler & 5.538 & 9 & 5263.2 & 0 & 1.85 & 4.34 & & \\*
+& npScarf & 5.566 & 7 & 5259.1 & 4 & 35.6 & 1.36 & + & 0.95 \\*
+& npGraph (bwa) & 5.535 & 5 & 5263.2 & 1 & 4.16 & 1.36 & + & 0.92 \\*
+& npGraph (minimap2) & 5.541 & 6 & 5263.2 & 0 & 0.85 & 1.36 & + & 0.04 \\*
+\rowcolor{Gray} 
+& \emph{S.~cerevisiae} S288c & \multicolumn{8}{l} {12,157,105 bp} \\*  
 & SPAdes & 11.675 & 194 & 260.5 & 0 & 1.57 & 3.61 & & \\*
@@
 & npGraph (minimap2) & 12.008 & 148 & 913.1 & 5 & 25.32 & 3.61 & + & 0.13 \\*
-\rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Shigella~sonnei} 53G: 5,220,473 bp} \\*  
+\rowcolor{Gray}
+& \emph{S.~sonnei} 53G & \multicolumn{8}{l} {5,220,473 bp} \\*  
 & SPAdes & 4.796 & 392 & 27.7 & 0 & 0.44 & 1.1 & & \\*
@@
 & npGraph (minimap2) & 5.293 & 97 & 4988.5 & 3 & 8.31 & 1.1 & + & 0.08 \\*
-\rowcolor{Gray} \multicolumn{10}{l}
-{\emph{Shigella~dysenteriae} Sd197: 4,560,911 bp} \\*  
+\rowcolor{Gray}
+& \emph{S.~dysenteriae} Sd197 & \multicolumn{8}{l} {4,560,911 bp} \\*  
 & SPAdes & 4.096 & 534 & 14.4 & 1 & 0.68 & 1.19 & & \\*
@@
 & Unicycler & 4.561 & 3 & 4369.2 & 0 & 12.96 & 8.46 & & \\*
-& npScarf & 4.649 & 174 & 41.8 & 65 & 372.87 & 1.19 & + & 0.62 \\*
+& npScarf & - & - & - & - & - & 1.19 & + & - \\*
 & npGraph (bwa) & 4.553 & 3 & 4369.1 & 6 & 91.03 & 1.19 & + & 0.76 \\*
@@
 
-Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, report for the whole comparison can be found in Supplementary Table~\ref{supp_tab:synthetic_benchmark}.
-In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the original scaffolder \npscarf{} was included as well as \npscarfg{} -- its modified version with assembly graph integrated.
-On the other hand, \npgraph{} can use 2 different aligners, \bwa{} and \minimap{}, for its bridging phase thus both practices were included in this comparison.
+Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from genome sequences of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
+In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
+On the other hand, 2 settings to run \npgraph{} were also considered for comparison.
 
-In general, the graph version of \npscarf{} improved the assembly results in terms of mis-assemblies and error reduction while virtually consuming similar resources compared to the original version.
-The only exception where the number of mis-assemblies being increased was the simulation of a random sequence with many repeats.
-There were 10 more mistakes detected using the later version \npscarfg{}.
-However, with additional investigations, we found that the number of mis-assemblies on the true positive circular sequences (3 from the reference) has been significant reduced by applying assembly graph for \npscarf{}.
-The errors mostly came from redundant sequences output from the software due to the failure in estimation of contig multiplicity.
-Even though using assembly graph for gap fillings, there were no changes in the way \npscarfg{} determine if a contig is unique or not. 
-Its implementation still relied on the length and coverage statistics, \IE{} \emph{Astats}~\cite{MyersSD2000} to find anchors that were critical for the backbone construction of the assembly.
-Redundant path findings for false positive replicons consequently returned additional wrong translocations in the final contigs which were reported by QUAST. 
-Other than that, the method had successfully produced better assemblies than the original.
-Regarding \emph{Mycobacterium tuberculosis} H37Rv, the number of mis-assembled breakpoints had been trimmed down from 12 to 2, while the number of final contigs had reduced from 4 to only one as in the reference.
-Results in cases of \ec{} O25b H4ST131 and \emph{Streptococcus suis} BM407 also showed enhancements in terms of those categories as well as N50 statistics.
-There was improvements considering the nucleotide errors (mismatches and indels) as well from aforementioned data sets, except for the \ec{} when slightly more mismatches had been detected.
-However, these errors can be corrected by running polishing tools with the raw Illumina data afterward.
-
-For \emph{Acinetobacter} AB30 synthetic data, it was an deficiency for \npscarfg{} in traversing the graph to find candidate paths for a bridge of long distance due to particular large search space.
-The exhaustive, naive DFS implementation for this version of \npscarf{} required a lot of memory to traverse a complex assembly graph that usually exceed a normal desktop's capacity.
-This issue has been fixed in \npgraph{} when Algorithm~\ref{algo:findpath} was used on the definitive graph.
-This resulted in completed runs of the assembly process for all data sets with the similar number of mis-assemblies compared to the best figures in this category.
-As shown in Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}, the assembly graph based methods offered significant improvements when compared to \npscarf{}.
-Not only because of the clear drops with respect to mis-assemblies and errors, but it was also reflected by the number of final contigs and their N50 as well.
-
-To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} was invoked in \npgraph{}. 
-The former option was inherited from \npscarf{} pipeline with the intact parameters
-%$-k11 -W20 -r10 -A1 -B1 -O1 -E1 -L0 -a -Y$
-while the latter was used with the recommended settings (-$\mathtt{k}$15 -$\mathtt{w}$5) for the best sensitivity working on MinION data.
-Even though, \bwa{} normally reported more hits than \minimap{} but at the same time, was responsible for more false positive alignments.
-For instance, regarding the last data set from Table~\ref{table:npgraph_compare}, the assembly of \npgraph{} using \bwa{} was suffered from the ambiguous alignments thus more fragmented than the other counterparts.
-On the other hand, referring to more complicated graphs from \emph{Acinetobacter} A1 and the yeast \emph{Saccharomyces cerevisiae} S288c from Table~\ref{supp_tab:synthetic_benchmark}, the number of mis-assemblies from using \minimap{} were increased due to the lacks of appropriate alignments to support accurate bridging process.
+To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} could be invoked from \npgraph{}.
+While \bwa{} is a well-known classic aligner that can be adapted to work with third generation sequencing data, \minimap{} is the state-of-the-art specially designed for this data type. 
+In \npgraph{}, the former option was inherited from \npscarf{} pipeline with identical parameters for the alignment algorithm
+(-$\mathtt{k}$11~-$\mathtt{W}$20~-$\mathtt{r}$10~-$\mathtt{A}$1~-$\mathtt{B}$1~-$\mathtt{O}$1~-$\mathtt{E}$1~-$\mathtt{L}$0~-$\mathtt{a}$~-$\mathtt{Y}$)
+while the latter was used with the sensitive settings (-$\mathtt{k}$15~-$\mathtt{w}$5) recommended for MinION data.
+Even though, \bwa{} normally reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
+As a result, bridging paths induced by using \bwa{} was slightly less accurate due to more noises from the smaller \emph{steps} inbetween (Figure~\ref{figure:npgraph_merging}).
+From all data sets in Table~\ref{table:npgraph_compare}, we can observe higher errors, which are the sum of mismatches and indels, per 100 Kbp from \npgraph{} using the classic tool.
 However, under almost circumstances, using either aligners would result in final assemblies with similar qualities.
-Furthermore, in terms of running time and resources required, \minimap{} proved to be the best option. 
+This is due to the fact that false possitive alignments mostly come from shorter \emph{stepping} nodes instead of long, high confident alignments with the \emph{anchor} nodes.
+In terms of running time and resources required, \minimap{} proved to be a better option. 
 The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
 This feature is certainly more favoured for a real-time assembly pipeline that normally requires quick responses in very short intervals.
-Because \minimap{} is expected to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner for \npgraph{} pipeline.
+Because \minimap{} is designed to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner in the \npgraph{} pipeline.
 
-To evaluate assembly errors, we considered the measure of the total mismatches and indels per 100 Kbp from the assembly sequences when mapping to the reference.
-As expected from hybrid assembly methods embedding Illumina data, the figures were hardly bigger than 100 (equivalent to 0.1\% error rate) in almost every cases.
-Furthermore, the indels errors, which mainly caused by TGS data, were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
+Overall, as expected from hybrid methods, the error rate of the draft assembly hardly exceeded 100 bp per 100 Kbp (equivalent to 0.1\%) in almost every cases.
+The only exception is \npscarf{} as it would sacrify the accuracy for the continuity by using the nanopore bases to fill in the gap between 2 unlinked unique contigs. 
+This happened for 2 \emph{Shigella} simulated genomes containing unusually long stretches of repetitive elements ($> 10$Kbp) for bacteria strains.
+Especially for the last case for \emph{Shigella dysenteriae}, \npscarf{} failed to finish its exhaustive path finding within reasonable time frame thus being excluded from the report.
+In fact, the indel errors (typical in nanopore sequencing) were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
 The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
 This phenomenon may root from homologous repeats or sequencing errors of the genome.
-From all the hybrid assemblers, $\mathtt{hybridSPAdes}$ reported results with highest fidelity.
-This meant that the performance its decision-rule algorithm $\mathtt{exSPAnder}$~\cite{Prjibelski2014} was the most accurate amongst all path finding methods.
-As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies in cases of \emph{Streptococcus suis} or \emph{Acinetobacter} samples (Table~\ref{table:npgraph_compare} and \ref{supp_tab:synthetic_benchmark}).
-\unicycler{}, which employs an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads, returned the second best reliable and at the same time, closest-to-complete results overall.
-\npscarf{}, on the other hand, employed the long reads for the gap filling thus inherited the high error rates from them.
-By integrating the assembly graph for the task, the errors were reduced in general (random sequences, \emph{M.~tuberculosis}, \emph{S.suis} from Table~\ref{table:npgraph_compare}) but not completely since the mis-placed contigs were still not resolved in other circumstances.
-\npgraph{} significantly reduced the errors compared to \npscarf{}, however the figures were still higher than the those of the best counterparts.
-This implied a more robust decision making system is needed in \npgraph{}'s real-time path finding module for even better output's accuracy.
+
+Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads using $\mathtt{SeqAn}$ library.
+When testing with these data sets, it was on top in terms of computational cost but returned the most reliable and complete assembly.
+$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
+As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers.
+This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.
+
+Regarding streaming algorithms, \npscarf{}, as aforementioned, employed the most greedy scaffolding approach that might introduce extra mis-assemblies and errors.
+They might be neglected for the majority of common bacterial genomes with modest repeat profiles, but in extreme cases ,\EG{} \emph{Shigella} data sets, the obtained results would be more error-proned necessitating extra post-processing, polishing steps afterward.
+On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
+For the yeast \emph{S.~ cerevisiae} data set, its assembly best covered the reference genome but the number of mis-assemblies was up to 5.
+On the other hand, the negative figures, namely number of mis-assemblies and error rate, were still high in the most extreme case of \emph{S.~dysenteriae}.
 

### 2019-11-26 paper.tex
working on results

@@
 A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses.
-The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods.
+The previous approach from \npscarf{} provided a fast-response streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods.
 Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs.
@@
 
-Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from genome sequences of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
+Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
 In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
-On the other hand, 2 settings to run \npgraph{} were also considered for comparison.
+On the other hand, 2 settings to run \npgraph{} were considered for comparison.
 
@@
 while the latter was used with the sensitive settings (-$\mathtt{k}$15~-$\mathtt{w}$5) recommended for MinION data.
-Even though, \bwa{} normally reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
+For this synthetic data, \bwa{} reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
 As a result, bridging paths induced by using \bwa{} was slightly less accurate due to more noises from the smaller \emph{steps} inbetween (Figure~\ref{figure:npgraph_merging}).
 From all data sets in Table~\ref{table:npgraph_compare}, we can observe higher errors, which are the sum of mismatches and indels, per 100 Kbp from \npgraph{} using the classic tool.
-However, under almost circumstances, using either aligners would result in final assemblies with similar qualities.
-This is due to the fact that false possitive alignments mostly come from shorter \emph{stepping} nodes instead of long, high confident alignments with the \emph{anchor} nodes.
-In terms of running time and resources required, \minimap{} proved to be a better option. 
+However, under almost circumstances, using either aligners would result in final assemblies with comparable qualities.
+This is due to the fact that false possitive alignments mostly come from shorter \emph{stepping} nodes instead of longer matches from the \emph{anchors}.
+Also, in reality, the error profile of sequencing data should be varied, not following the fixed pattern from this \emph{in silico} simulation and \bwa{} might indeed perform better sometimes. 
+But in terms of running time and resources required, \minimap{} proved to be a better option. 
 The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
 This feature is certainly more favoured for a real-time assembly pipeline that normally requires quick responses in very short intervals.
-Because \minimap{} is designed to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner in the \npgraph{} pipeline.
+Because \minimap{} is supposed to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner in the \npgraph{} pipeline.
 
@@
 
-Regarding streaming algorithms, \npscarf{}, as aforementioned, employed the most greedy scaffolding approach that might introduce extra mis-assemblies and errors.
-They might be neglected for the majority of common bacterial genomes with modest repeat profiles, but in extreme cases ,\EG{} \emph{Shigella} data sets, the obtained results would be more error-proned necessitating extra post-processing, polishing steps afterward.
+Regarding streaming algorithms, \npscarf{}, as aforementioned, used the most greedy scaffolding approach that might introduce extra mis-assemblies and errors.
+They might be negligible for the majority of common bacterial genomes with modest repeat profiles, but in extreme cases ,\EG{} \emph{Shigella} data sets, the obtained results would be more error-proned necessitating extra post-processing, polishing steps afterward.
 On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
 For the yeast \emph{S.~ cerevisiae} data set, its assembly best covered the reference genome but the number of mis-assemblies was up to 5.
-On the other hand, the negative figures, namely number of mis-assemblies and error rate, were still high in the most extreme case of \emph{S.~dysenteriae}.
+The unfavourable figures, namely mis-assemblies and error, were still high in case of \emph{S.~dysenteriae}.
+The reason was due to the complicated and extremely fragmented graph components containing a large number of small-scaled contigs that were difficult to be mapped with nanopore data.
+The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments and blundered in this case.
 
 \subsection*{Hybrid assembly for real data sets}
+The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.
+Also, considering the overfitting of \unicycler{} with its own test sets, we collected real-life sample for further comparison.
 A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used in this scenario.

### 2019-11-27 paper.tex
edit results

@@
 This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
-\npscarfg{} basically scaffolds the pre-assembly contigs in the same manner with the original version thus was not discussed here.
 
-\begin{figure}[!hpt]
+\begin{figure}[!ht]
 \centering
@@
 }
-\caption[Real-time scaffolding by \npscarf{} versus \npgraph{}]{N50 statistics of real-time scaffolding by \npscarf{} versus \npgraph{}.}
+\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
 \label{F:npgraph_rt}
@@
 Apparently it took more data for \npgraph{} to finish the same genome than the other.
-The reason stems from the fact that the new algorithm implemented a more `conservative' approach of bridge construction with at least 3 supporting long-reads for each to prevent any potential mis-bridging.
+The reason stems from the fact that the new algorithm used a more `conservative' approach of bridge construction with at least 3 supporting long-reads for each to prevent any potential mis-assembly. 
 Unlike \npscarf{} when the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
@@
 The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm. 
-Once a unique path has been determined, the bridge can be formed to connect the fragments together into longer sequences.
+In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads but seeing no conflict until then.
+
+Once a unique path has been determined, the bridge can be formed to connect the fragments together into a longer sequence leading to the increase of N50.
+\npgraph{} shows stable results so that it can directly report final assembly at any timepoint.
+As can be seen from Figure~\ref{F:npgraph_rt}, the genomes were completed at slower speed at the beginning of the streaming process and faster toward the end due to the accumulation of bridging information.
+However, the plots here only depict the real-time assembly operation including one final post-processing step.
+If the process is stopped somewhere in the middle, the post-processing would be invoked to return more completed genome but with the risk of higher mis-assembly due to shortage of supporting data.
 
 \subsection*{Metagenomics assembly on mock community}
-We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
+Here, we ran \npgraph{} on mock community data to study the performance of our method in metagenomic co-assembly problem.
 In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}.
@@
 \label{table:zymo}
-\begin{tabular}{|l|r|r|r|r|}
+\begin{tabular}{|l|c|r|r|c|r|r|}
 \hline
-\multirow{2}{*}{\textbf{Community}} & \multicolumn{2}{|c|}{\textbf{ZymoEven}} & \multicolumn{2}{|c|}{\textbf{ZymoLog}} \\ \cline{2-5}
-& $\mathtt{metaSPAdes}$ & \npgraph{} & $\mathtt{metaSPAdes}$ & \npgraph{} \\ \hline
-\emph{B.~subtilis} & $23,386$ & $382,368$ & $35,390$ & $433,078$ \\ \hline
-\emph{E.~coli} & $34,776$ & $1,108,989$ & $-$ & $-$ \\ \hline
-\emph{E.~faecalis} & $23,340$ & $217,908$ & $-$ & $-$ \\ \hline
-\emph{L.~monocytogenes} & $26,480$ & $520,012$ & $23,146$ & $130,284$ \\ \hline
-\emph{P.~aeruginosa} & $59,372$ & $1,753,658$ & $161,816$ & $444,495$ \\ \hline
-\emph{S.~aureus} & $26,058$ & $175,908$ & $-$ &$-$ \\ \hline
-\emph{S.~cerevisiae} & $-$ & $-$ & $-$ & $-$ \\ \hline
-\emph{S.~enterica} & $33,363$ & $4,242,458$ & $-$ & $-$ \\ \hline
+\multirow{3}{*}{\textbf{Community}} & \multicolumn{3}{|c|}{\textbf{ZymoEven}} & \multicolumn{3}{|c|}{\textbf{ZymoLog}} \\ \cline{2-7}
+& \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} & \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} \\ \cline{3-4} \cline{6-7}
+& & $\mathtt{metaSPAdes}$ & \npgraph{} &  & $\mathtt{metaSPAdes}$ & \npgraph{} \\
+\hline
+\emph{L.~monocytogenes} & 12 & $26,480$ & $520,012$ & 89.1 & $23,146$ & $130,284$ \\ \hline
+\emph{P.~aeruginosa} & 12 & $59,372$ & $1,753,658$ & 8.9 & $161,816$ & $444,495$ \\ \hline
+\emph{B.~subtilis} & 12 & $23,386$ & $382,368$ & 0.89 & $35,390$ & $433,078$ \\ \hline
+\emph{S.~cerevisiae} & 2 & $-$ & $-$ & 0.89 & $-$ & $-$ \\ \hline
+\emph{E.~coli} & 12 & $34,776$ & $1,108,989$ & 0.089 & $-$ & $-$ \\ \hline
+\emph{S.~enterica} & 12 & $33,363$ & $4,242,458$ & 0.089 & $-$ & $-$ \\ \hline
+\emph{E.~faecalis} & 12 & $23,340$ & $217,908$ & 0.00089 & $-$ & $-$ \\ \hline
+\emph{S.~aureus} & 12 & $26,058$ & $175,908$ & 0.000089 & $-$ &$-$ \\ \hline
 \end{tabular}
@@
 
-Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$ initial graph.  
+Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$' initial graph.  
 As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 

### 2019-11-29 paper.tex
split into 2

@@
 The application on synthetic and real data set of isolate genomes show improved accuracy while still maintaining the required computational cost extremely low. 
-On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data.
+%On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data. 
 With \npscarf{}, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process.
@@
 Even though all data were from microbial genomes, the complexity of the input graphs range from few hundred to ten thousands of components, synthesized \emph{in silico} or sequenced from \emph{in vitro} samples.
-Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
-We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
+%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
+%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
 In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
-Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph.
+%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection*{Metagenomics assembly on mock community}
-Here, we ran \npgraph{} on mock community data to study the performance of our method in metagenomic co-assembly problem.
-In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}.
-The total genome size was estimated as 61.96 Mbp.
-There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
-On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}.
+%\subsection*{Metagenomics assembly on mock community}
+%Here, we ran \npgraph{} on mock community data to study the performance of our method in metagenomic co-assembly problem.
+%In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}.
+%The total genome size was estimated as 61.96 Mbp.
+%There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
+%On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}.
 We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.
-
-\begin{table}[!hpt]
-\begin{center}
-\caption{Assembly improvement, in terms of NGA50 statistics, from $\mathtt{metaSPAdes}$ to \npgraph{} contigs on two mock communities ZymoLog and ZymoEven \cite{Nick2019zymo}.
+%
+%\begin{table}[!hpt]
+%\begin{center}
+%\caption{Assembly improvement, in terms of NGA50 statistics, from $\mathtt{metaSPAdes}$ to \npgraph{} contigs on two mock communities ZymoLog and ZymoEven \cite{Nick2019zymo}.
 The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio isolate assemblies used as reference \cite{Mcintyre2019zymo}.}
-\label{table:zymo}
-\begin{tabular}{|l|c|r|r|c|r|r|}
-\hline
-\multirow{3}{*}{\textbf{Community}} & \multicolumn{3}{|c|}{\textbf{ZymoEven}} & \multicolumn{3}{|c|}{\textbf{ZymoLog}} \\ \cline{2-7}
-& \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} & \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} \\ \cline{3-4} \cline{6-7}
-& & $\mathtt{metaSPAdes}$ & \npgraph{} &  & $\mathtt{metaSPAdes}$ & \npgraph{} \\
-\hline
-\emph{L.~monocytogenes} & 12 & $26,480$ & $520,012$ & 89.1 & $23,146$ & $130,284$ \\ \hline
-\emph{P.~aeruginosa} & 12 & $59,372$ & $1,753,658$ & 8.9 & $161,816$ & $444,495$ \\ \hline
-\emph{B.~subtilis} & 12 & $23,386$ & $382,368$ & 0.89 & $35,390$ & $433,078$ \\ \hline
-\emph{S.~cerevisiae} & 2 & $-$ & $-$ & 0.89 & $-$ & $-$ \\ \hline
-\emph{E.~coli} & 12 & $34,776$ & $1,108,989$ & 0.089 & $-$ & $-$ \\ \hline
-\emph{S.~enterica} & 12 & $33,363$ & $4,242,458$ & 0.089 & $-$ & $-$ \\ \hline
-\emph{E.~faecalis} & 12 & $23,340$ & $217,908$ & 0.00089 & $-$ & $-$ \\ \hline
-\emph{S.~aureus} & 12 & $26,058$ & $175,908$ & 0.000089 & $-$ &$-$ \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-To run \npgraph{} on the metagenomics data set, we firstly augmented binning information from using $\mathtt{metaBAT}$ \cite{Kang2015metabat} on the Illumina raw reads, before applying our method to the assembly graph generated by $\mathtt{metaSPAdes}$.
+%\label{table:zymo}
+%\begin{tabular}{|l|c|r|r|c|r|r|}
+%\hline
+%\multirow{3}{*}{\textbf{Community}} & \multicolumn{3}{|c|}{\textbf{ZymoEven}} & \multicolumn{3}{|c|}{\textbf{ZymoLog}} \\ \cline{2-7}
+%& \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} & \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} \\ \cline{3-4} \cline{6-7}
+%& & $\mathtt{metaSPAdes}$ & \npgraph{} &  & $\mathtt{metaSPAdes}$ & \npgraph{} \\
+%\hline
+%\emph{L.~monocytogenes} & 12 & $26,480$ & $520,012$ & 89.1 & $23,146$ & $130,284$ \\ \hline
+%\emph{P.~aeruginosa} & 12 & $59,372$ & $1,753,658$ & 8.9 & $161,816$ & $444,495$ \\ \hline
+%\emph{B.~subtilis} & 12 & $23,386$ & $382,368$ & 0.89 & $35,390$ & $433,078$ \\ \hline
+%\emph{S.~cerevisiae} & 2 & $-$ & $-$ & 0.89 & $-$ & $-$ \\ \hline
+%\emph{E.~coli} & 12 & $34,776$ & $1,108,989$ & 0.089 & $-$ & $-$ \\ \hline
+%\emph{S.~enterica} & 12 & $33,363$ & $4,242,458$ & 0.089 & $-$ & $-$ \\ \hline
+%\emph{E.~faecalis} & 12 & $23,340$ & $217,908$ & 0.00089 & $-$ & $-$ \\ \hline
+%\emph{S.~aureus} & 12 & $26,058$ & $175,908$ & 0.000089 & $-$ &$-$ \\ \hline
+%\end{tabular}
+%\end{center}
+%\end{table}
+%
+%To run \npgraph{} on the metagenomics data set, we firstly augmented binning information from using $\mathtt{metaBAT}$ \cite{Kang2015metabat} on the Illumina raw reads, before applying our method to the assembly graph generated by $\mathtt{metaSPAdes}$.
 The default parameter setting was remained as it was for isolate assembly.
-
-In terms of Illumina data, Even community had been sequenced by MiSeq platform which generated about 43-fold coverage while the Log community`s short-read data had been obtained from an Illumina HiSeq 1500, for about 156X coverage.
-Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser.
+%
+%In terms of Illumina data, Even community had been sequenced by MiSeq platform which generated about 43-fold coverage while the Log community`s short-read data had been obtained from an Illumina HiSeq 1500, for about 156X coverage.
+%Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser.
 This happened due to the fact of under-presented microbial cells from rare species in the Log population that require much more input for their reads to be sequenced, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).
-The assembly size for the two population are approximately 41 Mbp (66\%) and 22 Mbp (36\%). 
-During pre-processing step, \npgraph{} disregarded nodes which represent short, unconnected and extremely-low-coverage contigs which were indistinguishable from sequencing errors, artifacts or the actual rare species` genomes without additional works.
-
-Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$' initial graph.  
-As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
-There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
-\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} boosted from $33$ Kbp to $4.2$ Mbp. 
-On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as distinct as for the balanced colony.
+%The assembly size for the two population are approximately 41 Mbp (66\%) and 22 Mbp (36\%). 
+%During pre-processing step, \npgraph{} disregarded nodes which represent short, unconnected and extremely-low-coverage contigs which were indistinguishable from sequencing errors, artifacts or the actual rare species` genomes without additional works.
+%
+%Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$' initial graph.  
+%As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
+%There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
+%\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} boosted from $33$ Kbp to $4.2$ Mbp. 
+%On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as distinct as for the balanced colony.
 The longest NGA50 contigs belongs to \emph{P.aeruginosa} of 445 Kbp, however, the counterpart from the Even community was 4-fold than that, at 1.75 Mbp.
-The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective statistics was 433 Kbp for the zymo log.
+%The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective statistics was 433 Kbp for the zymo log.
 However for this isolate, the initial $\mathtt{metaSPAdes}$ assembly of the former was slightly better compared to the latter`s.
-
-%how much nanopore needed indeed
+%
+%%how much nanopore needed indeed
 
@@
 
-In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity.
+%In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity.
 The assembler was able to handle the De Bruijin assembly graph from Illumina data generated by $\mathtt{metaSPAdes}$ and simplify it using a minimal input stream of long reads.
-The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference.
+%The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference.
 The issue is caused by the shortage of short-read sequencing input to cover underpresented species in the mixture, especially for the Log community.

### 2019-11-30 npgraph.tex
create npgraph paper

--- 2019-11-29 paper.tex
@@
 \usepackage{mathtools}
-\usepackage{play}
+%\usepackage{play}
 \usepackage{makeidx}
@@
 
-\title{Real-time resolving assembly graph by ONT long reads data}
+\title{
+Real-time resolving assembly graph by ONT long reads data}
 \shorttitle{Real-time Scaffolding with Assembly graph}
@@
 \section*{Introduction}
+
+%Highlight the importance of real-time/hybrid assembly
+
+%Gaps: Several tool apptemt to use long reads to
+
 % \begin{itemize}
@@
 %     \end{itemize}
-% \end{itemize}
-Streaming assembly methods had been proven to be useful in saving time and resources compared to the conventional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
-The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
-This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
-\npscarf{}, on the other hand, is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
-It functions by scaffolding the contigs using nanopore sequencing which is well-known by the real-time property.
-The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
 
-% Why hybrid???
-Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
-On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
-As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
-\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
+There is rich  connectivity information in the assembly graph resulted from short read assembly. However, existing tools
+do not make use of this. Here, we present npGraph, a novel algorithm to resolve the assembly graph in real-time long read 
+sequyencing. npGraph maintain the assembly grahp and as new long reads coming in, it untangle the knots thereby simplify
+the assembly graph. Because of this, npGraph has better estimation of multiplcity of repeat contigs and hence resulting in
+fewer misassembly (Not to mention in real-time). In addition, we develop a visualisation tool for practitioners to monitor
+the progress of assembling process.
 
-However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
-A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
-Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
-To tackle the quality issue while maintaining its streaming feature, a bridging method by assembly graph traversing is proposed. 
-In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
-
-Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
-In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
-In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained.
-In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
-On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
-The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
-While the latter method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
-For that reason, the first direction is more suitable for a real-time pipeline.
-
-Nonetheless, the challenge to adapt this approach into a real-time mechanism is obvious, mainly from building a progressive implementation for path-finding and graph reducing module which are essential for a streaming graph assembler.
-To achieve that, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
-The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.
-
-We use different hybrid data sets to study the \npgraph{}`s performance and compare with other available tools with similar functionality, such as \npscarf{}, \unicycler{} and \hspades{}.
-Even though all data were from microbial genomes, the complexity of the input graphs range from few hundred to ten thousands of components, synthesized \emph{in silico} or sequenced from \emph{in vitro} samples.
-%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
-%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
-In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
-%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph.
+.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Results}
-\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
-\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g.
-\spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
-The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed.
-These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences.
-\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.
+\subsection*{Resolving assembly graph in real-time}
+
+\npgraph{} makes use of a assembly graph resulted from assembling short reads using a de Bruijin
+graph method such as \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$~\cite{Zerbino2008}
+and $mathtt{AbySS}$~\cite{Simpson2009}. The assembly graph consists of a list of contigs, and 
+possible connections among these contigs. In building the assembly graph, the de Bruijin graph assembler attemtps to extend each contig as long as possible, until there are more than one possible
+ways of extending due to the repeatitive sequences beyond the informaion contained in short reads.
+Hence cach contig has multiple possible connections with others, creating knots in the assembly graph.
+\npgraph{} then uses the connectivity information from long reads to untangle these knots in real-time.
+With sufficient data, when all the knots are removed, the assemply graph is simplified
+to a path which represents the complete assembly.
+
+\npgraph{} aligns long reads to the contigs in the assembly graph. When a long read is aligned
+to multiple contigs, \npgraph{} constructs candidate paths that are supported by the read. This 
+stratery allows \npgraph{} to progressively update the likelihood of the paths going through a knot.
+When sufficient data are obtained, the best path is confidently identified and hence the knot is untangled.
+%TODO: two more sentences describing the bridging
+%TODO: Because of the converting long reads to contig alignment to mapping to path, npgraph is faster than unicycler, and can be done in real-time
+
+% 
+% These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
+% \npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.
 
@@
 
-The GUI includes the dashboard for control the settings of the program and another pop-up window for a simple visualization of the assembly graph in real-time (Figure~\ref{figure:npgraph_gui}).
+We also develop a Graphical User Interface (GUI) for npgraph. The GUI includes the dashboard for controling the settings of the program and a window for visualization of the assembly graph 
+in real-time (Figure~\ref{figure:npgraph_gui}). 
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
-The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
-Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
-Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format.
+A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
+the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
+
+% TODO: Extract information from here to caption
+% The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
+% Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
+% Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format.
 Another option is to run the alignment independently and provide SAM/BAM input for the next stage of bridging and assembly.
@@
 The plots from the right panel (\textbf{5}) depicts real-time statistics of the assembly contigs inferred from the graph.
-From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements.
+% From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements.
 The number of different colors (other than white) indicates the amount of abundant groups being detected as population bins (\EG{} chromosome versus different plasmids, or different bins in metagenomics).
-
-A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data.
-The practice is similar to the previous developed pipelines~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+
+% \end{itemize}
+Streaming assembly methods had been proven to be useful in saving time and resources compared to the conventional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
+This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
+\npscarf{}, on the other hand, is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
+It functions by scaffolding the contigs using nanopore sequencing which is well-known by the real-time property.
+The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
+
+% Why hybrid???
+Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
+On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
+As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
+\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
+
+However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
+Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
+To tackle the quality issue while maintaining its streaming feature, a bridging method by assembly graph traversing is proposed. 
+In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
+
+Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
+In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
+In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained.
+In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
+On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
+The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
+While the latter method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
+For that reason, the first direction is more suitable for a real-time pipeline.
+
+Nonetheless, the challenge to adapt this approach into a real-time mechanism is obvious, mainly from building a progressive implementation for path-finding and graph reducing module which are essential for a streaming graph assembler.
+To achieve that, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
+The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.
+
+We use different hybrid data sets to study the \npgraph{}`s performance and compare with other available tools with similar functionality, such as \npscarf{}, \unicycler{} and \hspades{}.
+Even though all data were from microbial genomes, the complexity of the input graphs range from few hundred to ten thousands of components, synthesized \emph{in silico} or sequenced from \emph{in vitro} samples.
+%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
+%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
+In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
+%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph
+
 \section*{Conclusion}

### 2020-03-02 paper.tex
plos

@@
 
-\title{Real-time resolving assembly graph by ONT long reads data}
-\shorttitle{Real-time Scaffolding with Assembly graph}
+\title{
+Real-time resolution of short-read assembly graph using ONT long reads}
+\shorttitle{Real-time Graph Assembly}
 
@@
 \author[1,$\ast$]{Son Hoang Nguyen}
-\author[2]{Minh Duc Cao}
-\author[1,$\ast$]{Lachlan Coin}
+\author[1]{Minh Duc Cao}
+\author[1,2,3,4,$\ast$]{Lachlan Coin}
 
@@
 E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
+}
+
+\affil[2]{
+Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia}
+
+\affil[3]{
+Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
+}
+\affil[4]{Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
 }
@@
 \abstract{
-A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses.
-The previous approach from \npscarf{} provided a fast-response streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods.
-Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs.
+A streaming assembly pipeline utilising real-time Oxford Nanopore Technology (ONT) sequencing data is important for saving sequencing resources and reducing time-to-result.
+A previous approach implemented in  \npscarf{} provided an efficient streaming algorithm for hybrid assembly but was relatively prone to mis-assemblies compared to other graph-based methods.
+Here we present \npgraph{}, a streaming hybrid assembly tool using the assembly graph instead of the separated pre-assembly contigs.
 It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide.
-The application on synthetic and real data set of isolate genomes show improved accuracy while still maintaining the required computational cost extremely low. 
+Application to synthetic and real data from bacterial isolate genomes show improved accuracy while still maintaining a low computational cost. 
 %On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data. 
-With \npscarf{}, the built-in graphical user interface (GUI) can provide users a comprehensive look-and-feel of the whole assembly process.
+\npgraph{} also provides a graphical user interface (GUI) which provides a real-time visualisation of the progress of assembly.
  The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
@@
 \section*{Introduction}
+
+%Points:
+% Sequencing is now easy and cheap. However time is still the bottlenect, especially for time critical applications
+
+%One particular application is genome assembly
+
+%Highlight the importance of real-time/hybrid assembly
+
+%Gaps: Several tool apptemt to use long reads to
+
 % \begin{itemize}
@@
 %     \end{itemize}
-% \end{itemize}
-Streaming assembly methods had been proven to be useful in saving time and resources compared to the conventional batch algorithms with examples included \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
-The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
-This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
-\npscarf{}, on the other hand, is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
-It functions by scaffolding the contigs using nanopore sequencing which is well-known by the real-time property.
-The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
 
-% Why hybrid???
-Hybrd approaches are still common practice in genome assembly and data analyses when Illumina sequencing remains the most favoured option in terms of cost and accuracy to date.
-On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
-As the consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and comptete genomes at the same time.
-\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
+Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material
+which  can be obtained. 
+%This provides the potential use of DNA sequencing into a wide range of applications in medical 
+%and scientific research. 
+However, the time from sample to result remains a barrier to adoption of 
+sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making.  While
+there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT);  algorithms for streaming analyses  of such real-time data are still
+in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use.
 
-However, due to the greedy bridging approach of the contigs-based streaming algorithm, \npscarf{}`s results might suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
-A default setting were optimzed for microbial genomes input but cannot fit for all data from various experiments in practice.
-Also, the gap filling step has to rely on the low quality nanopore reads thus the accuracy of the final assembly is affected as well. 
-To tackle the quality issue while maintaining its streaming feature, a bridging method by assembly graph traversing is proposed. 
-In which, after the construction of a compact DBG assembly graph, the next step is to traverse the graph, resolve the repeats and identify the longest possible un-branched paths that would represents contigs for the final assembly.
+One particular strength of ONT technology is the production of ultra long reads. This is complementary to the dominant
+short read sequencing technology Illumina which is cheaper and has higher per base read quality
+but is unable to resolve the complex regions of the genome due to its read length limitation. A natural combination of
+the two technologies is in hybrid assembly of genomes. Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to 
+scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.
+However, \npscarf{} ignores the rich  connectivity information in the short read assembly graph, and as a result is prone to mis-assembly.
+%The strategy proved to be
+%a time- and cost- effective methodology where practitioners need to generate only sufficient data for completing 
+%a draft genome.
 
-Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} or \unicycler{} \cite{Wick2017unicycler}. 
-In general, the available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
-In which, the \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with mininum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are attained.
-In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
-On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
-The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
-While the latter method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
-For that reason, the first direction is more suitable for a real-time pipeline.
+ Here, we present \npgraph{}, a novel algorithm to resolve the assembly graph in real-time using long read 
+sequencing. \npgraph{} uses the stream of long reads to untangle knots in the assembly graph, which is maintained in memory.
+ Because of this, \npgraph{} has better estimation of multiplicity of repeat contigs, resulting in fewer misassemblies. 
+ In addition, we develop a visualisation tool for practitioners to monitor
+the progress of the assembly process.
 
-Nonetheless, the challenge to adapt this approach into a real-time mechanism is obvious, mainly from building a progressive implementation for path-finding and graph reducing module which are essential for a streaming graph assembler.
-To achieve that, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
-The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time as long as the nanopore sequencing process is still running.
-
-We use different hybrid data sets to study the \npgraph{}`s performance and compare with other available tools with similar functionality, such as \npscarf{}, \unicycler{} and \hspades{}.
-Even though all data were from microbial genomes, the complexity of the input graphs range from few hundred to ten thousands of components, synthesized \emph{in silico} or sequenced from \emph{in vitro} samples.
-%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
-%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
-In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
-%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Results}
-\subsection*{\npgraph{} -- a tool to resolve assembly graph in real-time}
-\npgraph{}'s input consists of Illumina assembly graph resulted from running assembler, e.g.
-\spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$ \cite{Zerbino2008}, $\mathtt{AbySS}$ \cite{Simpson2009} on Illumina short reads, together with long reads from third generation sequencing technology (Oxford Nanopore Technology, Pacbio).
-The long reads will be aligned with the contigs in the assembly graph to indicate longer paths that should be traversed.
-These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences.
-\npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.
+\subsection*{Resolving assembly graph in real-time}
+\npgraph{} makes use of an assembly graph generated from assembling short reads using a de Bruijin
+graph method such as \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$~\cite{Zerbino2008}
+and $\mathtt{AbySS}$~\cite{Simpson2009}. The assembly graph consists of a list of contigs, and 
+possible connections among these contigs. In building the assembly graph, the de Bruijin graph assembler attempts to extend 
+each contig as far as possible, until there is more than one possible way of extending due to the repetitive sequences 
+beyond the information contained in short reads. Hence each contig has multiple possible connections with others,
+ creating knots in the assembly graph. \npgraph{}  uses the connectivity information from long reads to untangle these knots in real-time. 
+ With sufficient data, when all the knots are removed, the assembly graph is simplified 
+to a path which represents the complete assembly.
+
+\begin{figure}[!hpt]
+\centering
+\subfloat[Merging bridges]{
+    \label{figure:npgraph_merge}
+	\includegraphics[width=.48\textwidth]{images/bridge_merging.pdf}
+}
+\hfill
+\subfloat[Knot untangled]{
+    \label{figure:npgraph_untangle}
+	\includegraphics[width=.48\textwidth]{images/knot.pdf}
+}
+\caption{Graph resolving algorithm.
+\ref{figure:npgraph_merge} the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
+\ref{figure:npgraph_untangle} A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
+\label{figure:npgraph_pipeline}
+\end{figure}
+
+\npgraph{} aligns long reads to the contigs in the assembly graph. When a long read is aligned
+to multiple contigs, \npgraph{} constructs candidate paths that are supported by the read. This strategy allows \npgraph{} to progressively update the likelihood of the paths going through a knot.
+When sufficient data are obtained, the best path is confidently identified and hence the knot is untangled.
+%TODO: two more sentences describing the bridging
+In general, the bridging algorithm used to determine the best path is a combination of progressive merging, accumulated scoring and decision making modules.
+It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Figure~\ref{figure:npgraph_merge}.
+A set of candidate paths are listed and the best one can be selected amongst them given enough evidence. 
+The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\ref{figure:npgraph_untangle}).
+
+%TODO: Because of the converting long reads to contig alignment to mapping to path, npgraph is faster than unicycler, and can be done in real-time
+
+% 
+% These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
+% \npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.
 
@@
 
-The GUI includes the dashboard for control the settings of the program and another pop-up window for a simple visualization of the assembly graph in real-time (Figure~\ref{figure:npgraph_gui}).
+We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
+in real-time (Figure~\ref{figure:npgraph_gui}). 
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
-The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
-Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
-Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format.
+A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
+the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
+
+% TODO: Extract information from here to caption
+% The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
+% Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
+% Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format.
 Another option is to run the alignment independently and provide SAM/BAM input for the next stage of bridging and assembly.
@@
 The plots from the right panel (\textbf{5}) depicts real-time statistics of the assembly contigs inferred from the graph.
-From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements.
+% From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements.
 The number of different colors (other than white) indicates the amount of abundant groups being detected as population bins (\EG{} chromosome versus different plasmids, or different bins in metagenomics).
 
-A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data.
-The practice is similar to the previous developed pipelines~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
-
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, its hybrid assembly module~\cite{AntipovKM2015}, \npscarf{}, and Unicycler version 0.4.6 using Unicycler`s synthetic data set~ \cite{Wick2017unicycler} .
-The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on random and available microbial references. 
-We ran all hybrid assembly methods in batch-mode and the reciprocal results were examined by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others?
+using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
+The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
+We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
 
@@
 Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
-In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
-On the other hand, 2 settings to run \npgraph{} were considered for comparison.
+%FOLLOWING REPEATS WHAT YOU SAID BEFORE
+%In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
+%On the other hand, 2 settings to run \npgraph{} were studied to have insights into the effect of using different alignment methods on its result.
 
-To align the long reads to the assembly graph components, either \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} could be invoked from \npgraph{}.
-While \bwa{} is a well-known classic aligner that can be adapted to work with third generation sequencing data, \minimap{} is the state-of-the-art specially designed for this data type. 
-In \npgraph{}, the former option was inherited from \npscarf{} pipeline with identical parameters for the alignment algorithm
-(-$\mathtt{k}$11~-$\mathtt{W}$20~-$\mathtt{r}$10~-$\mathtt{A}$1~-$\mathtt{B}$1~-$\mathtt{O}$1~-$\mathtt{E}$1~-$\mathtt{L}$0~-$\mathtt{a}$~-$\mathtt{Y}$)
-while the latter was used with the sensitive settings (-$\mathtt{k}$15~-$\mathtt{w}$5) recommended for MinION data.
-For this synthetic data, \bwa{} reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
-As a result, bridging paths induced by using \bwa{} was slightly less accurate due to more noises from the smaller \emph{steps} inbetween (Figure~\ref{figure:npgraph_merging}).
-From all data sets in Table~\ref{table:npgraph_compare}, we can observe higher errors, which are the sum of mismatches and indels, per 100 Kbp from \npgraph{} using the classic tool.
-However, under almost circumstances, using either aligners would result in final assemblies with comparable qualities.
-This is due to the fact that false possitive alignments mostly come from shorter \emph{stepping} nodes instead of longer matches from the \emph{anchors}.
-Also, in reality, the error profile of sequencing data should be varied, not following the fixed pattern from this \emph{in silico} simulation and \bwa{} might indeed perform better sometimes. 
-But in terms of running time and resources required, \minimap{} proved to be a better option. 
-The total CPU hours had been cut down drastically with the new aligner, making \npgraph{} the fastest hybrid assembler available.
-This feature is certainly more favoured for a real-time assembly pipeline that normally requires quick responses in very short intervals.
-Because \minimap{} is supposed to replace \bwa{} for long-read sequencing data alignment, it likewise being chosen as the default aligner in the \npgraph{} pipeline.
+To align the long reads to the assembly graph components, both \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} were used in conjunction with \npgraph{}.
+These two methods were chosen due to their proven efficiency and compatibility with streaming data.
+While \bwa{} is a well-known classic aligner that can be adapted to work with third generation sequencing data, \minimap{} has been specially designed for this data type. 
+%In \npgraph{}, the former's application is similar to \npscarf{} pipeline with identical parameters
+%(-$\mathtt{k}$11~-$\mathtt{W}$20~-$\mathtt{r}$10~-$\mathtt{A}$1~-$\mathtt{B}$1~-$\mathtt{O}$1~-$\mathtt{E}$1~-$\mathtt{L}$0~-$\mathtt{a}$~-$\mathtt{Y}$)
+%while the latter is used with the sensitive settings 
+%(-$\mathtt{k}$15~-$\mathtt{w}$5) 
+%recommended for MinION data.
+We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_merge}).
+%For this synthetic data, \bwa{} reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
+However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
+%The reason is that false positive alignments mostly come from shorter \emph{stepping} nodes instead of longer and more important hits for the \emph{anchors} which form the skeleton of the final assembly.
+%Also, in reality, the error profile of sequencing data is varied due to many factors, not simply following a pre-defined distribution from an \emph{in silico} simulation.
+%In other words, no single setting of a tool is assured the best performance with every data sets.
+In terms of running time and resources required, \minimap{} always proved to be a better option, requiring markedly less CPU time than \bwa{}.
+Utilising \minimap, \npgraph{} is now the fastest hybrid assembler available.
 
-Overall, as expected from hybrid methods, the error rate of the draft assembly hardly exceeded 100 bp per 100 Kbp (equivalent to 0.1\%) in almost every cases.
-The only exception is \npscarf{} as it would sacrify the accuracy for the continuity by using the nanopore bases to fill in the gap between 2 unlinked unique contigs. 
-This happened for 2 \emph{Shigella} simulated genomes containing unusually long stretches of repetitive elements ($> 10$Kbp) for bacteria strains.
+% Generally for hybrid approaches, the error rate of the draft assembly hardly exceeded 100 bp per 100 Kbp (equivalent to 0.1\%).
+% The only exception is \npscarf{} as it would sacrifice the accuracy for the continuity by using the nanopore bases to fill in the gap between 2 unlinked unique contigs. 
+% This happened for 2 \emph{Shigella} simulated genomes containing unusually long stretches of repetitive elements ($> 10$Kbp) for bacteria strains.
 Especially for the last case for \emph{Shigella dysenteriae}, \npscarf{} failed to finish its exhaustive path finding within reasonable time frame thus being excluded from the report.
-In fact, the indel errors (typical in nanopore sequencing) were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
-The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
-This phenomenon may root from homologous repeats or sequencing errors of the genome.
+% In fact, the indel errors (typical in nanopore sequencing) were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
+% The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
+% This phenomenon may root from homologous repeats or sequencing errors of the genome.
 
-Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads using $\mathtt{SeqAn}$ library.
-When testing with these data sets, it was on top in terms of computational cost but returned the most reliable and complete assembly.
+Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
+With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
 $\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
@@
 
-Regarding streaming algorithms, \npscarf{}, as aforementioned, used the most greedy scaffolding approach that might introduce extra mis-assemblies and errors.
-They might be negligible for the majority of common bacterial genomes with modest repeat profiles, but in extreme cases ,\EG{} \emph{Shigella} data sets, the obtained results would be more error-proned necessitating extra post-processing, polishing steps afterward.
-On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
-For the yeast \emph{S.~ cerevisiae} data set, its assembly best covered the reference genome but the number of mis-assemblies was up to 5.
-The unfavourable figures, namely mis-assemblies and error, were still high in case of \emph{S.~dysenteriae}.
-The reason was due to the complicated and extremely fragmented graph components containing a large number of small-scaled contigs that were difficult to be mapped with nanopore data.
-The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments and blundered in this case.
+Of the two streaming algorithms, \npscarf{} utilizes a fast but greedy scaffolding approach that can lead to mis-assemblies and errors.
+For bacterial genomes with modest complexity these are minimal (e.g.
+\kp), but for those with severe repetitive elements, extra calibrations are needed to prevent the mis-assembly due to ambiguous alignments.
+On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even proved to be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
+For the yeast \emph{S.~cerevisiae} data set, the \npgraph{} assembly best covered the reference genome but the number of mis-assemblies was up to 5.
+The unfavourable figures, namely mis-assemblies and error, were still high in case of \emph{S.~dysenteriae}, 
+ due to the complicated and extremely fragmented graph components containing a large number of small-scaled contigs that were difficult to map with nanopore data.
+The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments, without fully succeeding.
 
 \subsection*{Hybrid assembly for real data sets}
-The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.
-Also, considering the overfitting of \unicycler{} with its own test sets, we collected real-life sample for further comparison.
-A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used in this scenario.
+%The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.  %%CAN WE SUPPORT BETTER
+%Also, considering the potential for performance bias of \unicycler{} on its own test sets, we collected real-life sample for further comparison of \unicycler and \npgraph.
+A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
 The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
-Due to the unavailability of reference genomes, there were fewer statistics being reported by QUAST for the comparison of the results. 
-Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies.
-Table~\ref{tab:npgraph_real} shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.
+Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
+Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (
+Table~\ref{tab:npgraph_real}) 
+%shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
+on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.
 
@@
 
-From the first data set, there was high similarity between final contigs generated by two assemblers.
-They shared the same number of circular ultimate sequences, including the chromosomal and other six replicons contigs. 
-The only divergence lied on the biggest sequence ($\simeq 5.029$Mbp) when the \unicycler{}'s chromosome was 48 nucleotides longer than that of \npgraph{}.
-Five out of six identical replicons were confirmed as plasmids based on the occurences of appropriate Origin of replication sequences (PlasmidFinder database).
+There was high similarity between final contigs generated by two assemblers on all of these datasets.
+For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome.
+Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
 In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
-The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or newly replicon's DNA.
-Lastly, there were still $14.5$Kbp unfinished sequences resulted in 3 linear contigs from \unicycler{} and 2 for \npgraph{} respectively.
+The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
+Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.
 
-The assembly task for \emph{Enterobacter~cloacae} was observed more challenging as the chromosomal DNA sequence not been fully resolved using either method. 
-The chromosome size was estimated to be approximately $4.8$Mbp but had been broken into two smaller pieces. 
-\npgraph{} returned longer stretches of length $3.324$Mbp and $1.534$Mbp while the figures were $2.829$Mbp and $1.978$Mbp from \unicycler{}'s output.
-However, the number of circular sequences detected by \unicycler{} was one more than the other ($2$ versus $1$). They were corresponding to 2 plasmids, namely IncR and repA.
-While the latter were recognized by both methods, the longer plasmid sequence was fragmented running \npgraph{}.
-Similar to the previous data set, there were around $14$Kbp of data were unable to be finished by the assemblers.
+The assembly task for \emph{Enterobacter~cloacae} was more challenging and the chromosomal DNA remained fragmented in two contigs for both methods ( of length $3.324$Mbp and $1.534$Mbp for \npgraph{} compared to $2.829$Mbp and $1.978$Mbp for \unicycler{}).
+Both methods detected two plasmids ( IncR and repA), and \unicycler{} returned comlpete circular sequences for both plasmids, while \npgraph{} returned circular sequence for one plasmid, while the other was fragmented into two contigs.
+Similar to the assembly of \emph{Citrobacter freundii} , there was around $14$Kbp of data which was unable to be finished by the assemblers (split into 2 and 4 contigs for \unicycler{} and \npgraph{} respectively).
 
-Finally, assembly for \emph{Klebsiella oxytoca} saw fragmented chromosome using \unicycler{} but it was a fully complete contig for \npgraph{} with $6.156$Mbp of size.
-The two assemblers shared 3 common circular sequences where two of them were confirmed plasmids. 
-The first identical sequences represented a megaplasmid ($\simeq 113$Kbp) with two variations of IncFII's origin of replication DNA being identified. 
-The other agreed plasmid were IncL/M with $76$Kbp of length.
-Particularly, there was one circular contig with length greater than $100$Kbp but returned no hits to the plasmid database, suggesting the importance of \emph{de novo} replicon assembly in combination with further interrogations.
+Finally, the assembly for \emph{Klebsiella oxytoca} saw fragmented chromosome using \unicycler{} (with 5 contigs) which was a fully complete single contig for \npgraph{} with $6.156$Mbp of size.
+The two assemblers shared 3 common circular sequences of which two  were confirmed plasmids. 
+The first identical sequence represented a megaplasmid ($\simeq 113$Kbp) with two copies of IncFII origin of replication DNA being identified.
+The other $76$Kbp plasmid circularised by both was IncL/M with  of length.
+The third circular contig of length $111$Kbp returned no hits to the plasmid database, suggesting the importance of \emph{de novo} replicon assembly in combination with further interrogation.
 \unicycler{} detected another megaplasmid of size $108.4$Kbp which was fractured by \npgraph{}. 
-The dissolution was also observed in \npgraph{} for the final contig of length $11.6$Kbp where it failed to combine two smaller sequences into one.
+A fragmented contig was also observed in \npgraph{} for the final contig of length $11.6$Kbp where it failed to combine two smaller sequences into one.
 
-In addition to what presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Appendix Figure~\ref{supp_fig:npgraph_dotplot}.
-Interestingly, beside all other agreements, there was a structural difference using two methods for \emph{E.~cloacae} CAV1411 genome assembly.
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Supplementary Figure~\ref{supp_fig:npgraph_dotplot}.
+This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
 This was caused by the inconsistency of a fragment's direction on the final output contigs.
-However, when compare to a reference genome of the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), contigs generated by \npgraph{} demonstrated a consistent alignment which was not the case for \unicycler{} results (Appendix Figure~\ref{supp_fig:npgraph_ref}).
-Even though this might reflect a novel variation between bacterial samples of the same strain, it was more likely a mis-assembly by using \unicycler{}.
-
-Overall, by testing with synthetic and real data, \npgraph{} proved to be able to generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}.
-Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly. The next section will address this utility and the interactive GUI bundled in \npgraph{}.
+Comparison to a reference
+ genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{}  (Supplementary Figure~\ref{supp_fig:npgraph_ref}).
+However, we cannot at this stage rule out genuine structural variation between the two samples .
 
 \subsection*{Assembly performance on streaming data}
-Figure~\ref{F:npgraph_rt} demonstrates the real-time mode performance of \npscarf{} and \npgraph{} via N50 statistics during the assembly of 4 example data sets.
-This experiment would discover the rate of completing genome assemblies of the new method, set aside the accuracy aspect which had already been discussed previously.
+In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Figure~\ref{F:npgraph_rt}) .This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
+\npscarf{} converged more quickly than \npgraph{}, due to the fact that it is able to build bridges with only 1 spanning long-read, whereas \npgraph{} requires 3 reads.
+Unlike \npscarf{} where the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
+The plot for \ec{} data clarifies this behaviour when a fluctuation can be observed in \npscarf{} assembly at $\simeq 3$-folds data coverage.
+On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
+The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm. 
+In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
 
-\begin{figure}[!ht]
+\begin{figure}[!hbt]
 \centering
@@
 \end{figure}
-
-As can be observed from all the plots, \npgraph{} and \npscarf{} both converged to the same ultimate completeness but with different paces and patterns.
-Apparently it took more data for \npgraph{} to finish the same genome than the other.
-The reason stems from the fact that the new algorithm used a more `conservative' approach of bridge construction with at least 3 supporting long-reads for each to prevent any potential mis-assembly. 
-Unlike \npscarf{} when the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
-The plot for \ec{} data clarifies this behaviour when a fluctuation can be observed in \npscarf{} assembly at $\simeq 3$-folds data coverage.
-On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
-The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm. 
-In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads but seeing no conflict until then.
-
-Once a unique path has been determined, the bridge can be formed to connect the fragments together into a longer sequence leading to the increase of N50.
-\npgraph{} shows stable results so that it can directly report final assembly at any timepoint.
+% I removed following as I think its repetitive
+%Once a unique path has been determined, the bridge can be formed to connect the fragments together into a longer sequence leading to the increase of N50.
+\npgraph{} shows stable results so that it can directly report  the final assembly at any timepoint.
 As can be seen from Figure~\ref{F:npgraph_rt}, the genomes were completed at slower speed at the beginning of the streaming process and faster toward the end due to the accumulation of bridging information.
-However, the plots here only depict the real-time assembly operation including one final post-processing step.
-If the process is stopped somewhere in the middle, the post-processing would be invoked to return more completed genome but with the risk of higher mis-assembly due to shortage of supporting data.
+%However, the plots here only depict the real-time assembly operation including one final post-processing step.
+If the process is stopped somewhere in the middle, the post-processing would be invoked to return more completed genome but with the a greater risk of mis-assembly due to shortage of supporting data.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusion}
+\section*{Discussion}
+
+% \end{itemize}
+Streaming assembly methods have been proven to be useful in saving time and resources compared to conventional batch algorithms with examples including \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
+This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
+\npscarf{}, on the other hand, 
+is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
+It functions by scaffolding the contigs using real-time nanopore sequencing.
+The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
+
+% Why hybrid???
+Hybrid approaches are still common practice in genome assembly and data analyses while Illumina sequencing retains cost and accuracy benefits over long-read sequencing.
+On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
+As a consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and complete genomes at the same time.
+\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
+
+However, due to the greedy bridging approach of the contig-based streaming algorithm, \npscarf{}`s results can suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+A default setting was optimized for microbial genomes input but cannot fit for all data from various experiments in practice.
+Also, the gap filling step has to rely on the lower accuracy nanopore reads thus the accuracy of the final assembly is also affected. 
+To tackle the quality issue while maintaining the streaming feature of the approach, a bridging method by assembly graph traversing has been proposed in this manuscript. 
+Our approach uses as its starting point a compact DBG assembly graph, followed by graph-traveseral, repeat resolution and identification of the longest possible un-branched paths that would represents contigs for the final assembly.
+
+Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} as well as \unicycler{} \cite{Wick2017unicycler}. 
+The available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
+The \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with minimum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are retained.
+In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
+On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
+The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
+While this method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
+Hence, in theory it can be adapted to a real-time pipeline.
+
+The challenge in adapting graph-based  approaches into streaming algorithm comes mainly from building a progressive implementation for path-finding and graph reducing module . 
+To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
+%The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time while the  nanopore sequencing process is still running.
+
+By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time.
+%Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly.
+%The next section will address this utility and the interactive GUI bundled in \npgraph{}.
+
+%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
+%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
+In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
+%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph
+
+\section*{Conclusion}  %%COMMENT_LC seems repetitive here
 %npgraph: how important hybrid assembly
 Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
-On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield, however, the sequencing cost per base is still high.
+On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield and cost.
 Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
@@
 
-Compared to \npscarf, \npgraph{} algorithm employs a less greedy approach based on graph traversal.
-This might reduce the bridging rate when the linking conditions become more strict, but the concurrent results reported are more reliable.
+Compared to \npscarf, \npgraph{} algorithm employs more rigorous approach based on graph traversal.
+This might reduce the assembly errors because the bridging method is more accurate so that the reporting results are more reliable.
 The performance of \npgraph{} is comparable to \unicycler{} while consuming much less computational resources so that it can work on streaming mode. 
@@
 
-As a hybrid assembler, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
+On the other hand, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
 The algorithm operates on the assumption of a high quality assembly from a well-supplied source of short-read data for a decent assembly graph to begin with.
-It then consumes a just-enought amount of data from a streaming input of nanopore reads to resolve the graph. 
+It then consumes a just-enough amount of data from a streaming input of nanopore reads to resolve the graph. 
 Finally, extra pre-processing and comprehensive binning on the initial graph could further improve the performance of the streaming assembler.
@@
 
-The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph preprocessing; (2) graph resolving and simplifying; (3) postprocessing and reporting results. 
-The first step is to load the graph of Illumina contigs and retrieve their metadata which are helpful for the next steps, \EG binning and multiplicity estimation.
-The second step works on the processed input and augmented information from the previous one.
-In combination with path inducing from long reads, the assembly graph is then traversed and resolved in real-time.
+The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph pre-processing; (2) graph resolving and simplifying; (3) post-processing and reporting results. 
+The first step is to load the assembly graph of Illumina contigs and analyze its components' property, including binning and multiplicity estimation.
+The second step works on the processed graph and the long read data that can be provided in real-time by ONT sequencer.
+Based on the paths induced from long reads, the assembly graph will be resolved on-the-fly.
 Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
 Among three phases, only the first one must be performed prior to the MinION sequencing process in a streaming setup.
-The algorithm works on the assembly graph of Illumina contigs, so the terms \emph{contigs} and \emph{nodes} if not mentioned specifically, would be used interchangable throughout this context.
+The algorithm works on the assembly graph of Illumina contigs, so the terms \emph{contigs} and \emph{nodes} if not mentioned specifically, would be used interchangeable throughout this context.
 \subsection*{Contigs binning}
-Contigs from each completed genome are expected to be assigned to an unique group, or \emph{bin}, that would represent the final assembly unit, \EG{} chromosome , plasmids, or even particular species genome in a metagenomic community.
-As a result, the binning phase would assist the multiplicity estimation submodule that can differentiate repetitive contigs from unique ones.
+Contigs should belong to single or multiple groups, or \emph{bins}, that would represent different assembly units, \EG{} chromosome , plasmids, of different species if applying to a metagenomics dataset.
+A binning step is needed to assign membership of each contig to its corresponding group.
 
-Each contig is embeded in a single node in the assembly graph and an edge between two nodes indicates their overlap (link) properties.
-This step is to cluster the biggest nodes (contigs longer than $10$Kbp) into different sets, namely \emph{core} groups, based on the their degree (number of connections) and coverage values.
-DBSCAN clustering algorithm \cite{Ester96adensity-based} is applied for this task by default.
-The rationale is to approximate a coverage value of an extremely long contig (which can be splitted into more than 10,000 \emph{k-mers}) to be a sampled mean of a Poisson distribution (of \emph{k-mers} count).
-The metric is a distance function based on Kullback-Leibner divergence \cite{Kullback1951information}, or relative entropy, of two Poisson distributions.
+The first step is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
+To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
+ define a customised metric which is sample and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
+%The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count).
+The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.
 
-Assuming there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$
-The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
-$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
-or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
-The log ratio of the density functions is
-$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
-$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
-The metric we used is the distance defined as
+Formally, assuming there are 2 Poisson distributions $P_1$ and $P_2$ with probability mass functions (PMF) $$P_1(X=x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{x!}$$ and $$P_2(X=x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{x!}$$
+The Kullback-Leibler divergence from $P_2$ to $P_1$ is defined as:
+$$D_{KL}(P_1||P_2)=\sum_{x}{P_1(x)\log{\frac{P_1(x)}{P_2(x)}}}=\mathbb{E}_{P_1}[\log{\frac{P_1(x)}{P_2(x)}}]$$
+or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken using $P_1$.
+The log ratio of the PMFs is:
+$$\log{\frac{P_1(x)}{P_2(x)}}=\log{(e^{\lambda_2-\lambda_1}{(\frac{\lambda_1}{\lambda_2})}^x)}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+Thus the divergence between $P_1$ and $P_2$ is:
+$$D_{KL}(P_1||P_2)=\mathbb{E}_{P_1}[\log{\frac{P_1(x)}{P_2(x)}}]=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
+Thus, the metric we used is a distance function defined as:
 $$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$
 
-We implemented a simple binning algorithm based on the clustered contigs, the graph topology as well as statistics calculated by length and coverage of each contigs. 
-Additional binning step is taken place in real-time using the long reads as well.
-In this context, the repetition or uniquess of ambigous nodes are determined with sufficient supporting evidence from the long-spanning reads.
-Generally, the algorithm performs well for isolate or simple simulated metagenomics, but ineffective for complicated community.
-In that case, external binning tools can be employed for more comprehensive binning task and the results can be augmented to \npgraph{} input.
-If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT.
+% After identifying the bins, we implemented a graph traversal to assign more unique nodes to them, given the graph topology as well as statistics calculated by length and coverage of each contigs. 
+Independent from the contigs clustering in the pre-processing step, additional evidence of nodes' uniqueness can be acquired using the long reads during the assembly process.
+Given enough data, the multiplicity of an ambiguous node can be determined based on the set of all bridges rooted from itself.
+On the other hand, external binning tools such as MetaBAT~\cite{Kang2015metabat}, maxbin~\cite{Wu2014maxbin} can be employed in \npgraph{} as well.
+%If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT.
 By that, each line of the file would be:
-$
-\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
-$
-where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
+%$
+%\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
+%$
+%where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
 \subsection*{Multiplicity estimation}
-Due to the possible divergence of sequencing coverage relative to the real abundance of sequences, especially for the shorter contigs, an optimization step is carried out to alleviate this issue.
-The re-estimation is basically carried out by following two steps.
+Now bins of the main unique contigs had been identified, however, they only make up a certain proportion of the contigs set.
+From here, we need to assign bin membership and multiplicity for all other nodes of the graph, especially the repetitive ones.
+To do so, we relied on the graph's topology and the estimated read coverage of initial contigs from SPAdes.
+Given all contigs' coverage values as nodes' weight, we need to estimate those of edges and in return, using them to re-estimate the coverage for repetitive nodes if necessary.
+After this process, we will have a graph with optimized weighted components that would suggest their multiplicities more exactly.
+Basically the computation is described as in following steps:
+
 \begin{itemize}
-\item[1.] From nodes coverage, estimate edges' value by quadratic unconstrained optimization of the least-square function:
+\item[0.] Initialize every node weight as its corresponding contig coverage, all edges' weight as zeros.
+\item[1.] Calculate distributed weights for edges by quadratic unconstrained optimization of the least-square function:
 $$\frac{1}{2}\sum_{i}{l_i((\sum{e^{+}_{i}}-c_i)^2+(\sum{e^{-}_{i}}-c_i)^2}$$
-where $l_i$ and $c_i$ is the length and coverage of a node $i$ in the graph;
+where $l_i$ and $c_i$ is the length and weight of a node $i$ in the graph;
 
-$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
-The above function and be rewritten as:
+$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of weights for incoming and outgoing edges from node $i$ respectively.
+They are expected to be as close to $c_i$ as possible thus the length-weighted least-square should be minimized.
+
+The above function can be rewritten as:
 $$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
-and then being minimized by using gradient-based method.
-\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
+and then being minimized by using gradient method.
+\item[2.] Re-estimate weights of repetitive nodes based on their neighboring edges' measures and repeat previous optimization step. 
+The weights are calculated iteratively until no further significant updates are made or a threshold of loop count is reached.
 \end{itemize}
-The calibration is iterative until no further improvements are made or a threshold loop count is reached.
-The coverage measures of nodes (which represent contigs) are propated throughout the graph via connecting edges for calibrations prior to the multiplicity estimation. 
-%The assignment of coverage to edges is also helpful to induce multiplicity of nodes in later step.
 
-Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
-For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
-Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variation of coverage values.
-For that reason, in \npgraph{}'s algorithm, they are only used as augmented information to calculate likelihood scores of candidate paths containing corresponding nodes.
+At this point, we can induce the copy numbers of nodes in the final assembly.
+For each node, this could be done by investigating its adjacent edges' multiplicity to estimate how many times it should be visited and from which bin(s).
+Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) are less confident due to greater randomness in sequencing coverage. 
+For that reason, in \npgraph{}, we did not rely on them for graph transformation but as supporting information for path finding.
 
@@
 A bridge must start from a unique contig, or \emph{anchor} node, and end at another when completed.
-Located inbetween are nodes known as \emph{steps} and distances between them are called \emph{spans} of the bridge.
+Located in-between are nodes known as \emph{steps} and distances between them are called \emph{spans} of the bridge.
 Stepping nodes are normally repetitive contigs and indicative for a path finding operation later on.
-In a complicated assembly graph, the more details the bridge, \emph{a.k.a.} more steps inbetween, the faster and more accurate the linking path it would resolve.
+In a complicated assembly graph, the more details the bridge, \emph{a.k.a.} more steps in-between, the faster and more accurate the linking path it would resolve.
 A bridge's function is complete when it successfully return the ultimate linking path between 2 anchors.
@@
 
-\begin{figure}[!hpt]
-\centering
-\includegraphics[width=.8\textwidth]{images/bridge_merging.pdf}
-\caption[Example of bridge merging progressively]{Bridge merging progressively in real-time.
+% \begin{figure}[!hpt]
+% \centering
+% \includegraphics[width=.8\textwidth]{images/bridge_merging.pdf}
+% \caption[Example of bridge merging progressively]{Bridge merging progressively in real-time.
 Sequencing long reads induce alignments to the contigs where new bridges are created respectively.
 Bridges sharing same anchors can be merged together to form the ultimate, more comprehensive bridge (with more step nodes and better approximation of spans between them).}
-\label{figure:npgraph_merging}
-\end{figure}
+% \label{figure:npgraph_merging}
+% \end{figure}
 
 At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
-In an example from Figure~\ref{figure:npgraph_merging}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+In an example from Figure~\ref{figure:npgraph_merge}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
 Each of the steps therefore is assigned a weighing score based on its alignment quality.
-Due to the error rate of long reads, there should be deviations in terms of steps found and spans measured between these bridges, eventhough they represent the same connection.
+Due to the error rate of long reads, there should be deviations in terms of steps found and spans measured between these bridges, even though they represent the same connection.
 A continuous merging phase, as shown in the figure, takes advantage of a pairwise Needleman-Wunsch dynamic programming to generate a consensus list based on weight and position of each of every stepping nodes.
@@
 
-Due to false alignments from shorter contigs to the long reads, not all of the reported step nodes are neccessary to be appeared in the ultimate path resolved by the bridge. 
+Due to false alignments from shorter contigs to the long reads, not all of the reported step nodes are necessary to be appeared in the ultimate path resolved by the bridge. 
 In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
@@
 \KwData{Assembly graph $G\{V,E\}$}
-\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps inbetween}
+\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
 \KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_2}$ that maximize the likelihood of the step list.}
@@
 $m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
-\tcc{if there is no step inbetween, run path finding algorithm above directly and return the result}
+\tcc{if there is no step in-between, run path finding algorithm above directly and return the result}
 \If{$M.size() \equiv 2$}{ 

### 2020-03-02 plos_latex_template.tex
plos

--- 2020-03-02 paper.tex
@@
-\documentclass[10pt,twocolumn,twoside]{genpaper}
-\usepackage[numbers,sort&compress]{natbib}
+% Template for PLoS
+% Version 3.5 March 2018
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that 
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
+
+%% npGraph
 \newcommand{\npscarf}{$\mathtt{npScarf}$}
@@
 
-\usepackage{pdfpages} 
-\usepackage{mathtools}
-%\usepackage{play}
-\usepackage{makeidx}
-\usepackage{xcolor,colortbl}
-\usepackage{longtable}
-\usepackage{booktabs}
-\usepackage{hyperref}
-\usepackage{pdflscape}
-
-\usepackage{amsmath,amsfonts,amssymb} % this is handy for mathematicians and physicists
-			      % see http://www.ams.org/tex/amslatex.html
-
-% \usepackage{showkeys} % this shows what labels you are using for cross
-		      % references
-
-\usepackage{graphicx} % standard graphics package for inclusion of
-		      % images and eps files into LaTeX document
-
 \usepackage{multirow} 
-
 \usepackage{float}
 \usepackage[caption = false]{subfig}
-% this code hacked from that of R Chandrasekhar from UWA
-\newif\ifpdf
-\ifx\pdfoutput\undefined
-	\pdffalse    % we are not running pdfLaTeX
-\else
-	\pdfoutput=1 % we are running pdfLaTeX
-	\pdftrue
-\fi
-
-\ifpdf
-	\DeclareGraphicsExtensions{.pdf}  % this command defined in graphicx
-	\pdfcompresslevel=9  % 0: no compression, 9: highest compression
-			     % or, set compress_level 9 in file pdftex.cfg
-\else
-	\DeclareGraphicsExtensions{.ps}
-\fi
 
@@
 \usepackage{mathtools}
-\usepackage{amsmath}
 \DeclareMathOperator*{\argmax}{argmax}
@@
 
-\usepackage{xr}
-\externaldocument{supplementary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Some functions provided  by the class
+\usepackage{longtable,booktabs}
+%% End preloads
 
-%Display line numbers on the margins
-\lineno
+\begin{document}
+\vspace*{0.2in}
 
-%% use \onecolumn for onecolumn paper
-\onecolumn
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Real-time resolution of short-read assembly graph using ONT long reads} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Son Hoang Nguyen\textsuperscript{1*},
+Minh Duc Cao\textsuperscript{1},
+Lachlan Coin\textsuperscript{1,2,3,4*}
+\\
+\bigskip
+\textbf{1} Institute for Molecular Bioscience, the University of Queensland, 
+St Lucia, Brisbane, QLD 4072 Australia
+\\
+\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia
+\\
+\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
+\\
+\textbf{4} Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
+\bigskip
 
-\title{
-Real-time resolution of short-read assembly graph using ONT long reads}
-\shorttitle{Real-time Graph Assembly}
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+*s.hoangnguyen@imb.uq.edu.au,l.coin@imb.uq.edu.au
 
-%Authors
-\author[1,$\ast$]{Son Hoang Nguyen}
-\author[1]{Minh Duc Cao}
-\author[1,2,3,4,$\ast$]{Lachlan Coin}
-
-%Affiliation
-\affil[1]{Institute for Molecular Bioscience, the University of Queensland, 
-St Lucia, Brisbane, QLD 4072 Australia}
-\correspondingauthor{
-\textsuperscript{$\ast$}
-To whom correspondence should be addressed. 
-E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
-}
-
-\affil[2]{
-Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia}
-
-\affil[3]{
-Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
-}
-\affil[4]{Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
-}
-
-%Display ``This manuscript was compiled on XXXX''
-\compiledate
-
-%Set abstract (see below)
-\abstract{
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
 A streaming assembly pipeline utilising real-time Oxford Nanopore Technology (ONT) sequencing data is important for saving sequencing resources and reducing time-to-result.
@@
  The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
-} 
-%Set keywords
-\keywords{hybrid assembly, assembly graph, real-time analysis, nanopore sequencing}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+\section*{Author summary}
 
-\begin{document}
-%Abstract and keywords have to be defined before \maketitle
-\maketitle
-\thispagestyle{fancy}
+\linenumbers
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Use "Eq" instead of "Equation" for equation citations.
 \section*{Introduction}
-
-%Points:
-% Sequencing is now easy and cheap. However time is still the bottlenect, especially for time critical applications
-
-%One particular application is genome assembly
-
-%Highlight the importance of real-time/hybrid assembly
-
-%Gaps: Several tool apptemt to use long reads to
-
-% \begin{itemize}
-% \item The importance of having a real-time assembler for bacterial and small genomes: e.g. npscarf 
-% \item The difficulty to resolve assembly graph in real-time.
-% \item Available hybrid assembly methods using long reads: unicycler, ...
-% \item an online algorithm to resolve assembly graph by long reads is needed, ...
-% \item Requirements
-%     \begin{itemize}
-%     \item Support streaming: efficient with high yield (armortized analysis)
-%     \item Statistically robust: online modification of the dynamic graph, back tracking edge deletion...
-%     \item Standardisation : output GFA in real-time
-%     \end{itemize}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
-\subsection*{Resolving assembly graph in real-time}
+\section*{Materials and methods}
+\subsection*{Application overview}
 \npgraph{} makes use of an assembly graph generated from assembling short reads using a de Bruijin
@@
 
-%TODO: Because of the converting long reads to contig alignment to mapping to path, npgraph is faster than unicycler, and can be done in real-time
-
-% 
-% These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
-% \npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.
-
+We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
+in real-time (Figure~\ref{figure:npgraph_gui}). 
+In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
+A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
+the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
 \begin{figure}[!hpt]
@@
 
-We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
-in real-time (Figure~\ref{figure:npgraph_gui}). 
-In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
-A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
-the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
-
-% TODO: Extract information from here to caption
-% The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
-% Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
-% Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format.
-Another option is to run the alignment independently and provide SAM/BAM input for the next stage of bridging and assembly.
-This stage is controlled by buttons in box \textbf{4}: the START button ignites the process while the STOP button can prematurely terminate it and output the assembly result till that moment.
-The plots from the right panel (\textbf{5}) depicts real-time statistics of the assembly contigs inferred from the graph.
-% From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements.
-The number of different colors (other than white) indicates the amount of abundant groups being detected as population bins (\EG{} chromosome versus different plasmids, or different bins in metagenomics).
-
-\subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others?
-using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
-The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
-We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
-
-\LTcapwidth=\linewidth
-% \footnotesize
-\begin{longtable}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
-\caption[Comparison of assemblies using \npgraph{} and other methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\
-
- \toprule
-    &       & \cthead{1}{Assembly} &     & 
-    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
-    \cthead{3}{Run times} \\
-    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
-    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
-    \cthead{3}{(CPU hrs)} \\
-\toprule    
-\endfirsthead
-
-\multicolumn{10}{c}%
-{{\tablename\ \thetable{} -- continued from previous page}} \\
- \toprule
-    &       & \cthead{1}{Assembly} &     & 
-    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
-    \cthead{3}{Run times} \\
-    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
-    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
-    \cthead{3}{(CPU hrs)} \\
-\toprule    
-\endhead
-
-\hline \multicolumn{10}{|r|}{{Continued on next page}} \\ \hline
-\endfoot
-
-\hline \hline
-\endlastfoot
-
-\rowcolor{Gray}
-& \emph{M.~tuberculosis} H37Rv & \multicolumn{8}{l} {4,411,532 bp} \\*  
-& SPAdes & 4.376 & 66 & 150.7 & 0 & 0.23 & 1.42 & & \\*
-& SPAdes hybrid & 4.411 & 1 & 4410.5 & 0 & 0.86 & 1.61 & & \\*
-& Unicycler & 4.412 & 1 & 4411.5 & 0 & 2.56 & 5.52 & & \\*
-& npScarf & 4.432 & 4 & 4402.2 & 7 & 6.61 & 1.42 & + & 0.7 \\*
-& npGraph (bwa) & 4.411 & 1 & 4411.4 & 0 & 2.63 & 1.42 & + & 0.64 \\*
-& npGraph (minimap2) & 4.412 & 1 & 4411.5 & 0 & 0.68 & 1.42 & + & 0.02 \\*
-\rowcolor{Gray} 
-& \emph{K.~pneumoniae} 30660 & \multicolumn{8}{l} {5,540,936 bp} \\*  
-& SPAdes & 5.469 & 64 & 270.2 & 0 & 0.07 & 1.36 & & \\*
-& SPAdes hybrid & 5.543 & 8 & 4229.1 & 2 & 5.04 & 1.63 & & \\*
-& Unicycler & 5.538 & 9 & 5263.2 & 0 & 1.85 & 4.34 & & \\*
-& npScarf & 5.566 & 7 & 5259.1 & 4 & 35.6 & 1.36 & + & 0.95 \\*
-& npGraph (bwa) & 5.535 & 5 & 5263.2 & 1 & 4.16 & 1.36 & + & 0.92 \\*
-& npGraph (minimap2) & 5.541 & 6 & 5263.2 & 0 & 0.85 & 1.36 & + & 0.04 \\*
-\rowcolor{Gray} 
-& \emph{S.~cerevisiae} S288c & \multicolumn{8}{l} {12,157,105 bp} \\*  
-& SPAdes & 11.675 & 194 & 260.5 & 0 & 1.57 & 3.61 & & \\*
-& SPAdes hybrid & 11.910 & 45 & 770.5 & 5 & 34.52 & 4.15 & & \\*
-& Unicycler & 11.837 & 29 & 909.1 & 0 & 22.83 & 16.34 & & \\*
-& npScarf & 11.990 & 22 & 796.8 & 53 & 85.5 & 3.61 & + & 4.35 \\*
-& npGraph (bwa) & 12.000 & 151 & 913.1 & 3 & 38.68 & 3.61 & + & 4.12 \\*
-& npGraph (minimap2) & 12.008 & 148 & 913.1 & 5 & 25.32 & 3.61 & + & 0.13 \\*
-\rowcolor{Gray}
-& \emph{S.~sonnei} 53G & \multicolumn{8}{l} {5,220,473 bp} \\*  
-& SPAdes & 4.796 & 392 & 27.7 & 0 & 0.44 & 1.1 & & \\*
-& SPAdes hybrid & 5.218 & 8 & 2195.5 & 2 & 41.98 & 1.36 & & \\*
-& Unicycler & 5.221 & 5 & 4988.5 & 0 & 7.91 & 9.64 & & \\*
-& npScarf & 6.426 & 20 & 1293.8 & 84 & 366.04 & 1.1 & + & 0.52 \\*
-& npGraph (bwa) & 5.293 & 97 & 4988.5 & 3 & 14.87 & 1.1 & + & 0.57 \\*
-& npGraph (minimap2) & 5.293 & 97 & 4988.5 & 3 & 8.31 & 1.1 & + & 0.08 \\*
-\rowcolor{Gray}
-& \emph{S.~dysenteriae} Sd197 & \multicolumn{8}{l} {4,560,911 bp} \\*  
-& SPAdes & 4.096 & 534 & 14.4 & 1 & 0.68 & 1.19 & & \\*
-& SPAdes hybrid & 4.486 & 23 & 821.2 & 96 & 10.99 & 1.89 & & \\*
-& Unicycler & 4.561 & 3 & 4369.2 & 0 & 12.96 & 8.46 & & \\*
-& npScarf & - & - & - & - & - & 1.19 & + & - \\*
-& npGraph (bwa) & 4.553 & 3 & 4369.1 & 6 & 91.03 & 1.19 & + & 0.76 \\*
-& npGraph (minimap2) & 4.548 & 3 & 4364.1 & 8 & 83.68 & 1.19 & + & 0.14 \\*
-
-\end{longtable}
-
-\normalsize
-
-Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
-%FOLLOWING REPEATS WHAT YOU SAID BEFORE
-%In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
-%On the other hand, 2 settings to run \npgraph{} were studied to have insights into the effect of using different alignment methods on its result.
-
-To align the long reads to the assembly graph components, both \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} were used in conjunction with \npgraph{}.
-These two methods were chosen due to their proven efficiency and compatibility with streaming data.
-While \bwa{} is a well-known classic aligner that can be adapted to work with third generation sequencing data, \minimap{} has been specially designed for this data type. 
-%In \npgraph{}, the former's application is similar to \npscarf{} pipeline with identical parameters
-%(-$\mathtt{k}$11~-$\mathtt{W}$20~-$\mathtt{r}$10~-$\mathtt{A}$1~-$\mathtt{B}$1~-$\mathtt{O}$1~-$\mathtt{E}$1~-$\mathtt{L}$0~-$\mathtt{a}$~-$\mathtt{Y}$)
-%while the latter is used with the sensitive settings 
-%(-$\mathtt{k}$15~-$\mathtt{w}$5) 
-%recommended for MinION data.
-We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
-This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_merge}).
-%For this synthetic data, \bwa{} reported more but shorter hits than \minimap{} thus was responsible for higher number of false positive alignments.
-However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
-%The reason is that false positive alignments mostly come from shorter \emph{stepping} nodes instead of longer and more important hits for the \emph{anchors} which form the skeleton of the final assembly.
-%Also, in reality, the error profile of sequencing data is varied due to many factors, not simply following a pre-defined distribution from an \emph{in silico} simulation.
-%In other words, no single setting of a tool is assured the best performance with every data sets.
-In terms of running time and resources required, \minimap{} always proved to be a better option, requiring markedly less CPU time than \bwa{}.
-Utilising \minimap, \npgraph{} is now the fastest hybrid assembler available.
-
-% Generally for hybrid approaches, the error rate of the draft assembly hardly exceeded 100 bp per 100 Kbp (equivalent to 0.1\%).
-% The only exception is \npscarf{} as it would sacrifice the accuracy for the continuity by using the nanopore bases to fill in the gap between 2 unlinked unique contigs. 
-% This happened for 2 \emph{Shigella} simulated genomes containing unusually long stretches of repetitive elements ($> 10$Kbp) for bacteria strains.
-Especially for the last case for \emph{Shigella dysenteriae}, \npscarf{} failed to finish its exhaustive path finding within reasonable time frame thus being excluded from the report.
-% In fact, the indel errors (typical in nanopore sequencing) were found relatively low in the final contigs (Table~\ref{supp_tab:synthetic_benchmark}).
-% The majority of the differences accounted for the mismatched nucleotides caused by the alternative paths connecting the unique anchors from the backbone of the assembly.
-% This phenomenon may root from homologous repeats or sequencing errors of the genome.
-
-Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
-With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
-$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
-As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers.
-This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.
-
-Of the two streaming algorithms, \npscarf{} utilizes a fast but greedy scaffolding approach that can lead to mis-assemblies and errors.
-For bacterial genomes with modest complexity these are minimal (e.g.
-\kp), but for those with severe repetitive elements, extra calibrations are needed to prevent the mis-assembly due to ambiguous alignments.
-On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even proved to be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
-For the yeast \emph{S.~cerevisiae} data set, the \npgraph{} assembly best covered the reference genome but the number of mis-assemblies was up to 5.
-The unfavourable figures, namely mis-assemblies and error, were still high in case of \emph{S.~dysenteriae}, 
- due to the complicated and extremely fragmented graph components containing a large number of small-scaled contigs that were difficult to map with nanopore data.
-The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments, without fully succeeding.
-
-\subsection*{Hybrid assembly for real data sets}
-%The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.  %%CAN WE SUPPORT BETTER
-%Also, considering the potential for performance bias of \unicycler{} on its own test sets, we collected real-life sample for further comparison of \unicycler and \npgraph.
-A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
-The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
-Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
-Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (
-Table~\ref{tab:npgraph_real}) 
-%shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
-on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.
-
-\begin{table}[!hpt]
-\centering
-\caption[Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized SPAdes output]{Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized \spades{} output.
-Circular contigs are highlighted in \textbf{bold}, fragmented assemblies are presented as X$\vert$Y where X is the total length and Y is the number of supposed contigs making up X.}
-\label{tab:npgraph_real}
-\begin{tabular}{p{4cm}|r|r|l}
- & \unicycler{} & \npgraph{} & Replicons (based on $\mathtt{PlasmidFinder}$ 1.3) \\ \toprule
-\emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
-CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
- & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
- & \textbf{85,575} & \textbf{85,575} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
- & \textbf{43,621} & \textbf{43,621} & repA\_1\_pKPC-2\_CP013325 \\
- & \textbf{3,223} & \textbf{3,223} & - \\
- & \textbf{1,916} & \textbf{1,916} & ColRNAI\_1\_\_DQ298019 \\
- & 14,464$\vert$3 & 14,456$\vert$2 & - \\ \hline
-\emph{Enterobacter cloacae} & 4,806,666$\vert$2 & 4,858,438$\vert$2 & Chromosome \\
-CAV1411 & \textbf{90,451} & 90,693$\vert$2 & IncR\_1\_\_DQ449578 \\
- & \textbf{33,610} & \textbf{33,610} & repA\_1\_pKPC-2\_CP013325 \\
- & 13,129$\vert$2 & 14,542$\vert$4 & - \\ \hline
-\emph{Klebsiella oxytoca}  & 6,153,947$\vert$5 & \textbf{6,155,762} & Chromosome \\
-CAV1015 & \textbf{113,105} & \textbf{113,105} & \begin{tabular}[c]{@{}l@{}}IncFII(SARC14)\_1\_SARC14\_JQ418540;\\ IncFII(S)\_1\_\_CP000858\end{tabular} \\
- & \textbf{111,395} & \textbf{111,395} & - \\
- & \textbf{108,418} & 109,209$\vert$13 & IncFIB(K)\_1\_Kpn3\_JN233704 \\
- & \textbf{76,183} & \textbf{76,186} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
- & \textbf{11,638} & 11,892$\vert$2 & - \\ \hline
-\end{tabular}
-\end{table}
-
-There was high similarity between final contigs generated by two assemblers on all of these datasets.
-For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome.
-Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
-In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
-The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
-Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.
-
-The assembly task for \emph{Enterobacter~cloacae} was more challenging and the chromosomal DNA remained fragmented in two contigs for both methods ( of length $3.324$Mbp and $1.534$Mbp for \npgraph{} compared to $2.829$Mbp and $1.978$Mbp for \unicycler{}).
-Both methods detected two plasmids ( IncR and repA), and \unicycler{} returned comlpete circular sequences for both plasmids, while \npgraph{} returned circular sequence for one plasmid, while the other was fragmented into two contigs.
-Similar to the assembly of \emph{Citrobacter freundii} , there was around $14$Kbp of data which was unable to be finished by the assemblers (split into 2 and 4 contigs for \unicycler{} and \npgraph{} respectively).
-
-Finally, the assembly for \emph{Klebsiella oxytoca} saw fragmented chromosome using \unicycler{} (with 5 contigs) which was a fully complete single contig for \npgraph{} with $6.156$Mbp of size.
-The two assemblers shared 3 common circular sequences of which two  were confirmed plasmids. 
-The first identical sequence represented a megaplasmid ($\simeq 113$Kbp) with two copies of IncFII origin of replication DNA being identified.
-The other $76$Kbp plasmid circularised by both was IncL/M with  of length.
-The third circular contig of length $111$Kbp returned no hits to the plasmid database, suggesting the importance of \emph{de novo} replicon assembly in combination with further interrogation.
-\unicycler{} detected another megaplasmid of size $108.4$Kbp which was fractured by \npgraph{}. 
-A fragmented contig was also observed in \npgraph{} for the final contig of length $11.6$Kbp where it failed to combine two smaller sequences into one.
-
-In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Supplementary Figure~\ref{supp_fig:npgraph_dotplot}.
-This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
-This was caused by the inconsistency of a fragment's direction on the final output contigs.
-Comparison to a reference
- genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{}  (Supplementary Figure~\ref{supp_fig:npgraph_ref}).
-However, we cannot at this stage rule out genuine structural variation between the two samples .
-
-\subsection*{Assembly performance on streaming data}
-In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Figure~\ref{F:npgraph_rt}) .This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
-\npscarf{} converged more quickly than \npgraph{}, due to the fact that it is able to build bridges with only 1 spanning long-read, whereas \npgraph{} requires 3 reads.
-Unlike \npscarf{} where the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
-The plot for \ec{} data clarifies this behaviour when a fluctuation can be observed in \npscarf{} assembly at $\simeq 3$-folds data coverage.
-On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
-The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm. 
-In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
-
-\begin{figure}[!hbt]
-\centering
-\subfloat[\emph{Citrobacter~freundii} CAV1374]{
-	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
-}
-\hfill
-\subfloat[\emph{Escherichia~coli} K12 MG1655]{
-	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
-}
-\\
-\subfloat[\emph{Klebsiella} 30660 NJST258]{
-	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
-}
-\hfill
-\subfloat[\emph{Klebsiella} NTUH K2044]{
-	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
-}
-\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
-\label{F:npgraph_rt}
-\end{figure}
-% I removed following as I think its repetitive
-%Once a unique path has been determined, the bridge can be formed to connect the fragments together into a longer sequence leading to the increase of N50.
-\npgraph{} shows stable results so that it can directly report  the final assembly at any timepoint.
-As can be seen from Figure~\ref{F:npgraph_rt}, the genomes were completed at slower speed at the beginning of the streaming process and faster toward the end due to the accumulation of bridging information.
-%However, the plots here only depict the real-time assembly operation including one final post-processing step.
-If the process is stopped somewhere in the middle, the post-processing would be invoked to return more completed genome but with the a greater risk of mis-assembly due to shortage of supporting data.
-
-%\subsection*{Metagenomics assembly on mock community}
-%Here, we ran \npgraph{} on mock community data to study the performance of our method in metagenomic co-assembly problem.
-%In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}.
-%The total genome size was estimated as 61.96 Mbp.
-%There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
-%On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}.
-We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.
-%
-%\begin{table}[!hpt]
-%\begin{center}
-%\caption{Assembly improvement, in terms of NGA50 statistics, from $\mathtt{metaSPAdes}$ to \npgraph{} contigs on two mock communities ZymoLog and ZymoEven \cite{Nick2019zymo}.
-The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio isolate assemblies used as reference \cite{Mcintyre2019zymo}.}
-%\label{table:zymo}
-%\begin{tabular}{|l|c|r|r|c|r|r|}
-%\hline
-%\multirow{3}{*}{\textbf{Community}} & \multicolumn{3}{|c|}{\textbf{ZymoEven}} & \multicolumn{3}{|c|}{\textbf{ZymoLog}} \\ \cline{2-7}
-%& \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} & \multirow{2}{*}{Abundance(\%)} & \multicolumn{2}{|c|}{NGA50} \\ \cline{3-4} \cline{6-7}
-%& & $\mathtt{metaSPAdes}$ & \npgraph{} &  & $\mathtt{metaSPAdes}$ & \npgraph{} \\
-%\hline
-%\emph{L.~monocytogenes} & 12 & $26,480$ & $520,012$ & 89.1 & $23,146$ & $130,284$ \\ \hline
-%\emph{P.~aeruginosa} & 12 & $59,372$ & $1,753,658$ & 8.9 & $161,816$ & $444,495$ \\ \hline
-%\emph{B.~subtilis} & 12 & $23,386$ & $382,368$ & 0.89 & $35,390$ & $433,078$ \\ \hline
-%\emph{S.~cerevisiae} & 2 & $-$ & $-$ & 0.89 & $-$ & $-$ \\ \hline
-%\emph{E.~coli} & 12 & $34,776$ & $1,108,989$ & 0.089 & $-$ & $-$ \\ \hline
-%\emph{S.~enterica} & 12 & $33,363$ & $4,242,458$ & 0.089 & $-$ & $-$ \\ \hline
-%\emph{E.~faecalis} & 12 & $23,340$ & $217,908$ & 0.00089 & $-$ & $-$ \\ \hline
-%\emph{S.~aureus} & 12 & $26,058$ & $175,908$ & 0.000089 & $-$ &$-$ \\ \hline
-%\end{tabular}
-%\end{center}
-%\end{table}
-%
-%To run \npgraph{} on the metagenomics data set, we firstly augmented binning information from using $\mathtt{metaBAT}$ \cite{Kang2015metabat} on the Illumina raw reads, before applying our method to the assembly graph generated by $\mathtt{metaSPAdes}$.
-The default parameter setting was remained as it was for isolate assembly.
-%
-%In terms of Illumina data, Even community had been sequenced by MiSeq platform which generated about 43-fold coverage while the Log community`s short-read data had been obtained from an Illumina HiSeq 1500, for about 156X coverage.
-%Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser.
-This happened due to the fact of under-presented microbial cells from rare species in the Log population that require much more input for their reads to be sequenced, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).
-%The assembly size for the two population are approximately 41 Mbp (66\%) and 22 Mbp (36\%). 
-%During pre-processing step, \npgraph{} disregarded nodes which represent short, unconnected and extremely-low-coverage contigs which were indistinguishable from sequencing errors, artifacts or the actual rare species` genomes without additional works.
-%
-%Despite of the input graph quality, table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$' initial graph.  
-%As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
-%There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
-%\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} boosted from $33$ Kbp to $4.2$ Mbp. 
-%On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as distinct as for the balanced colony.
-The longest NGA50 contigs belongs to \emph{P.aeruginosa} of 445 Kbp, however, the counterpart from the Even community was 4-fold than that, at 1.75 Mbp.
-%The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective statistics was 433 Kbp for the zymo log.
-However for this isolate, the initial $\mathtt{metaSPAdes}$ assembly of the former was slightly better compared to the latter`s.
-%
-%%how much nanopore needed indeed
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-
-% \end{itemize}
-Streaming assembly methods have been proven to be useful in saving time and resources compared to conventional batch algorithms with examples including \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
-The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
-This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
-\npscarf{}, on the other hand, 
-is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
-It functions by scaffolding the contigs using real-time nanopore sequencing.
-The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
-
-% Why hybrid???
-Hybrid approaches are still common practice in genome assembly and data analyses while Illumina sequencing retains cost and accuracy benefits over long-read sequencing.
-On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
-As a consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and complete genomes at the same time.
-\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
-
-However, due to the greedy bridging approach of the contig-based streaming algorithm, \npscarf{}`s results can suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
-A default setting was optimized for microbial genomes input but cannot fit for all data from various experiments in practice.
-Also, the gap filling step has to rely on the lower accuracy nanopore reads thus the accuracy of the final assembly is also affected. 
-To tackle the quality issue while maintaining the streaming feature of the approach, a bridging method by assembly graph traversing has been proposed in this manuscript. 
-Our approach uses as its starting point a compact DBG assembly graph, followed by graph-traveseral, repeat resolution and identification of the longest possible un-branched paths that would represents contigs for the final assembly.
-
-Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} as well as \unicycler{} \cite{Wick2017unicycler}. 
-The available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
-The \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with minimum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are retained.
-In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
-On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
-The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
-While this method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
-Hence, in theory it can be adapted to a real-time pipeline.
-
-The challenge in adapting graph-based  approaches into streaming algorithm comes mainly from building a progressive implementation for path-finding and graph reducing module . 
-To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
-%The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time while the  nanopore sequencing process is still running.
-
-By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time.
-%Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly.
-%The next section will address this utility and the interactive GUI bundled in \npgraph{}.
-
-%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
-%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
-In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
-%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph
-
-\section*{Conclusion}  %%COMMENT_LC seems repetitive here
-%npgraph: how important hybrid assembly
-Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
-On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield and cost.
-Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
-\npscarf{} had been introduced initially to address these issues, however, the accuracy of the assembly output was affected by its greedy alignment-based scaffolding approach.
-Here we present \npgraph{}, a streaming hybrid assembly method working on the DBG assembly graph that is able to finish short-read assembly in real-time while minimizing the errors and mis-assemblies drastically.
-
-Compared to \npscarf, \npgraph{} algorithm employs more rigorous approach based on graph traversal.
-This might reduce the assembly errors because the bridging method is more accurate so that the reporting results are more reliable.
-The performance of \npgraph{} is comparable to \unicycler{} while consuming much less computational resources so that it can work on streaming mode. 
-Also, the integrated GUI allows users to visualize its animated output in a  more efficient way.
-
-%In the very first attempt to run real-time assembly on metagenomics data, \npgraph{} proved that its method can adapt to scaled-up data and complexity.
-The assembler was able to handle the De Bruijin assembly graph from Illumina data generated by $\mathtt{metaSPAdes}$ and simplify it using a minimal input stream of long reads.
-%The result has shown more complete isolate genomes reconstructed out of the graph, but the overall communities` genome coverage were dropped with several strains omitted comparing to the reference.
-The issue is caused by the shortage of short-read sequencing input to cover underpresented species in the mixture, especially for the Log community.
-
-On the other hand, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
-The algorithm operates on the assumption of a high quality assembly from a well-supplied source of short-read data for a decent assembly graph to begin with.
-It then consumes a just-enough amount of data from a streaming input of nanopore reads to resolve the graph. 
-Finally, extra pre-processing and comprehensive binning on the initial graph could further improve the performance of the streaming assembler.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Methods}
-
+\subsection*{Algorithm in details}
 The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph pre-processing; (2) graph resolving and simplifying; (3) post-processing and reporting results. 
@@
 The algorithm works on the assembly graph of Illumina contigs, so the terms \emph{contigs} and \emph{nodes} if not mentioned specifically, would be used interchangeable throughout this context.
-\subsection*{Contigs binning}
+\subsubsection*{Contigs binning}
 Contigs should belong to single or multiple groups, or \emph{bins}, that would represent different assembly units, \EG{} chromosome , plasmids, of different species if applying to a metagenomics dataset.
@@
 %where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
-\subsection*{Multiplicity estimation}
+\subsubsection*{Multiplicity estimation}
 Now bins of the main unique contigs had been identified, however, they only make up a certain proportion of the contigs set.
@@
 %\subsection*{Untangling assembly graph by stream of nanopore data.}
-\subsection*{Building bridges in real-time}
+\subsubsection*{Building bridges in real-time}
 Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
@@
 
-\subsection*{Path finding algorithm}
+\subsubsection*{Path finding algorithm}
 Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them.
@@
 In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
-\subsection*{Graph simplification in real-time}
+\subsubsection*{Graph simplification in real-time}
 \npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that can be streamed in real-time.
@@
 Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
-\subsection*{Result extraction and output}
+\subsubsection*{Result extraction and output}
 \npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will spell a contig in the assembly report.
@@
 
-\bibliographystyle{pnas2011}
-\bibliography{library}
+% Results and Discussion can be combined.
+\section*{Results}
+\subsection*{Evaluation using synthetic data}
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others?
+using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
+The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
+We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}}
+\label{table:npgraph_compare}
+\begin{tabular}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
+ \hline
+    &       & \cthead{1}{Assembly} &     & 
+    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
+    \cthead{3}{Run times} \\
+    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
+    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
+    \cthead{3}{(CPU hrs)} \\
+\thickhline
+
+\rowcolor{Gray}
+& \emph{M.~tuberculosis} H37Rv & \multicolumn{8}{l} {4,411,532 bp} \\*  
+& SPAdes & 4.376 & 66 & 150.7 & 0 & 0.23 & 1.42 & & \\*
+& SPAdes hybrid & 4.411 & 1 & 4410.5 & 0 & 0.86 & 1.61 & & \\*
+& Unicycler & 4.412 & 1 & 4411.5 & 0 & 2.56 & 5.52 & & \\*
+& npScarf & 4.432 & 4 & 4402.2 & 7 & 6.61 & 1.42 & + & 0.7 \\*
+& npGraph (bwa) & 4.411 & 1 & 4411.4 & 0 & 2.63 & 1.42 & + & 0.64 \\*
+& npGraph (minimap2) & 4.412 & 1 & 4411.5 & 0 & 0.68 & 1.42 & + & 0.02 \\*
+\rowcolor{Gray} 
+& \emph{K.~pneumoniae} 30660 & \multicolumn{8}{l} {5,540,936 bp} \\*  
+& SPAdes & 5.469 & 64 & 270.2 & 0 & 0.07 & 1.36 & & \\*
+& SPAdes hybrid & 5.543 & 8 & 4229.1 & 2 & 5.04 & 1.63 & & \\*
+& Unicycler & 5.538 & 9 & 5263.2 & 0 & 1.85 & 4.34 & & \\*
+& npScarf & 5.566 & 7 & 5259.1 & 4 & 35.6 & 1.36 & + & 0.95 \\*
+& npGraph (bwa) & 5.535 & 5 & 5263.2 & 1 & 4.16 & 1.36 & + & 0.92 \\*
+& npGraph (minimap2) & 5.541 & 6 & 5263.2 & 0 & 0.85 & 1.36 & + & 0.04 \\*
+\rowcolor{Gray} 
+& \emph{S.~cerevisiae} S288c & \multicolumn{8}{l} {12,157,105 bp} \\*  
+& SPAdes & 11.675 & 194 & 260.5 & 0 & 1.57 & 3.61 & & \\*
+& SPAdes hybrid & 11.910 & 45 & 770.5 & 5 & 34.52 & 4.15 & & \\*
+& Unicycler & 11.837 & 29 & 909.1 & 0 & 22.83 & 16.34 & & \\*
+& npScarf & 11.990 & 22 & 796.8 & 53 & 85.5 & 3.61 & + & 4.35 \\*
+& npGraph (bwa) & 12.000 & 151 & 913.1 & 3 & 38.68 & 3.61 & + & 4.12 \\*
+& npGraph (minimap2) & 12.008 & 148 & 913.1 & 5 & 25.32 & 3.61 & + & 0.13 \\*
+\rowcolor{Gray}
+& \emph{S.~sonnei} 53G & \multicolumn{8}{l} {5,220,473 bp} \\*  
+& SPAdes & 4.796 & 392 & 27.7 & 0 & 0.44 & 1.1 & & \\*
+& SPAdes hybrid & 5.218 & 8 & 2195.5 & 2 & 41.98 & 1.36 & & \\*
+& Unicycler & 5.221 & 5 & 4988.5 & 0 & 7.91 & 9.64 & & \\*
+& npScarf & 6.426 & 20 & 1293.8 & 84 & 366.04 & 1.1 & + & 0.52 \\*
+& npGraph (bwa) & 5.293 & 97 & 4988.5 & 3 & 14.87 & 1.1 & + & 0.57 \\*
+& npGraph (minimap2) & 5.293 & 97 & 4988.5 & 3 & 8.31 & 1.1 & + & 0.08 \\*
+\rowcolor{Gray}
+& \emph{S.~dysenteriae} Sd197 & \multicolumn{8}{l} {4,560,911 bp} \\*  
+& SPAdes & 4.096 & 534 & 14.4 & 1 & 0.68 & 1.19 & & \\*
+& SPAdes hybrid & 4.486 & 23 & 821.2 & 96 & 10.99 & 1.89 & & \\*
+& Unicycler & 4.561 & 3 & 4369.2 & 0 & 12.96 & 8.46 & & \\*
+& npScarf & - & - & - & - & - & 1.19 & + & - \\*
+& npGraph (bwa) & 4.553 & 3 & 4369.1 & 6 & 91.03 & 1.19 & + & 0.76 \\*
+& npGraph (minimap2) & 4.548 & 3 & 4364.1 & 8 & 83.68 & 1.19 & + & 0.14 \\*
+
+\end{tabular}
+\end{adjustwidth}
+\end{table}
+
+\normalsize
+
+Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
+
+To align the long reads to the assembly graph components, both \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} were used in conjunction with \npgraph{}.
+These two methods were chosen due to their proven efficiency and compatibility with streaming data.
+While \bwa{} is a well-known classic aligner that can be adapted to work with third generation sequencing data, \minimap{} has been specially designed for this data type. 
+We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_merge}).
+However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
+In terms of running time and resources required, \minimap{} always proved to be a better option, requiring markedly less CPU time than \bwa{}.
+Utilising \minimap, \npgraph{} is now the fastest hybrid assembler available.
+
+Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
+With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
+$\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
+As the trade-off, there were fewer connections satisfying its quality threshold, resulting in the fragmented assemblies with lower N50 compared to the other hybrid assemblers.
+This behaviour was clearly reflected in the last, also the most challenging task of assembly \emph{S.~dysenteriae}.
+
+Of the two streaming algorithms, \npscarf{} utilizes a fast but greedy scaffolding approach that can lead to mis-assemblies and errors.
+For bacterial genomes with modest complexity these are minimal (e.g.
+\kp), but for those with severe repetitive elements, extra calibrations are needed to prevent the mis-assembly due to ambiguous alignments.
+On the other hand, \npgraph{} significantly reduced the errors compared to \npscarf{}, sometimes even proved to be the best option \EG{} for \emph{M.~tuberculosis} and \kp{}.  
+For the yeast \emph{S.~cerevisiae} data set, the \npgraph{} assembly best covered the reference genome but the number of mis-assemblies was up to 5.
+The unfavourable figures, namely mis-assemblies and error, were still high in case of \emph{S.~dysenteriae}, 
+ due to the complicated and extremely fragmented graph components containing a large number of small-scaled contigs that were difficult to map with nanopore data.
+The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments, without fully succeeding.
+
+\subsection*{Hybrid assembly for real data sets}
+%The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.  %%CAN WE SUPPORT BETTER
+%Also, considering the potential for performance bias of \unicycler{} on its own test sets, we collected real-life sample for further comparison of \unicycler and \npgraph.
+A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
+The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
+Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
+Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (
+Table~\ref{tab:npgraph_real}) 
+%shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
+on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.
+
+\begin{table}[!hpt]
+\begin{adjustwidth}{-2.25in}{0in}
+\centering
+\caption[Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized SPAdes output]{Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized \spades{} output.
+Circular contigs are highlighted in \textbf{bold}, fragmented assemblies are presented as X$\vert$Y where X is the total length and Y is the number of supposed contigs making up X.}
+\label{tab:npgraph_real}
+\begin{tabular}{p{4cm}|r|r|l}
+ & \unicycler{} & \npgraph{} & Replicons (based on $\mathtt{PlasmidFinder}$ 1.3) \\ \thickhline
+\emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
+CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
+ & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
+ & \textbf{85,575} & \textbf{85,575} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
+ & \textbf{43,621} & \textbf{43,621} & repA\_1\_pKPC-2\_CP013325 \\
+ & \textbf{3,223} & \textbf{3,223} & - \\
+ & \textbf{1,916} & \textbf{1,916} & ColRNAI\_1\_\_DQ298019 \\
+ & 14,464$\vert$3 & 14,456$\vert$2 & - \\ \hline
+\emph{Enterobacter cloacae} & 4,806,666$\vert$2 & 4,858,438$\vert$2 & Chromosome \\
+CAV1411 & \textbf{90,451} & 90,693$\vert$2 & IncR\_1\_\_DQ449578 \\
+ & \textbf{33,610} & \textbf{33,610} & repA\_1\_pKPC-2\_CP013325 \\
+ & 13,129$\vert$2 & 14,542$\vert$4 & - \\ \hline
+\emph{Klebsiella oxytoca}  & 6,153,947$\vert$5 & \textbf{6,155,762} & Chromosome \\
+CAV1015 & \textbf{113,105} & \textbf{113,105} & \begin{tabular}[c]{@{}l@{}}IncFII(SARC14)\_1\_SARC14\_JQ418540;\\ IncFII(S)\_1\_\_CP000858\end{tabular} \\
+ & \textbf{111,395} & \textbf{111,395} & - \\
+ & \textbf{108,418} & 109,209$\vert$13 & IncFIB(K)\_1\_Kpn3\_JN233704 \\
+ & \textbf{76,183} & \textbf{76,186} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
+ & \textbf{11,638} & 11,892$\vert$2 & - \\ \hline
+\end{tabular}
+\end{adjustwidth}
+\end{table}
+
+There was high similarity between final contigs generated by two assemblers on all of these datasets.
+For the \emph{Citrobacter freundii}  dataset, they share the same number of circular  sequences, including the chromosomal and other six replicons contigs in the , with only 48 nucleotides  difference in the length of the main chromosome.
+Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
+In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
+The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
+Both assemblers had $14.5$Kbp of unfinished sequences split amongst 3 linear contigs from \unicycler{} and 2 for \npgraph{}.
+
+The assembly task for \emph{Enterobacter~cloacae} was more challenging and the chromosomal DNA remained fragmented in two contigs for both methods ( of length $3.324$Mbp and $1.534$Mbp for \npgraph{} compared to $2.829$Mbp and $1.978$Mbp for \unicycler{}).
+Both methods detected two plasmids ( IncR and repA), and \unicycler{} returned comlpete circular sequences for both plasmids, while \npgraph{} returned circular sequence for one plasmid, while the other was fragmented into two contigs.
+Similar to the assembly of \emph{Citrobacter freundii} , there was around $14$Kbp of data which was unable to be finished by the assemblers (split into 2 and 4 contigs for \unicycler{} and \npgraph{} respectively).
+
+Finally, the assembly for \emph{Klebsiella oxytoca} saw fragmented chromosome using \unicycler{} (with 5 contigs) which was a fully complete single contig for \npgraph{} with $6.156$Mbp of size.
+The two assemblers shared 3 common circular sequences of which two  were confirmed plasmids. 
+The first identical sequence represented a megaplasmid ($\simeq 113$Kbp) with two copies of IncFII origin of replication DNA being identified.
+The other $76$Kbp plasmid circularised by both was IncL/M with  of length.
+The third circular contig of length $111$Kbp returned no hits to the plasmid database, suggesting the importance of \emph{de novo} replicon assembly in combination with further interrogation.
+\unicycler{} detected another megaplasmid of size $108.4$Kbp which was fractured by \npgraph{}. 
+A fragmented contig was also observed in \npgraph{} for the final contig of length $11.6$Kbp where it failed to combine two smaller sequences into one.
+
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in S1 Fig.
+This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
+This was caused by the inconsistency of a fragment's direction on the final output contigs.
+Comparison to a reference
+ genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (S2 Fig.).
+However, we cannot at this stage rule out genuine structural variation between the two samples .
+
+\subsection*{Assembly performance on streaming data}
+In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Figure~\ref{F:npgraph_rt}) .This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
+\npscarf{} converged more quickly than \npgraph{}, due to the fact that it is able to build bridges with only 1 spanning long-read, whereas \npgraph{} requires 3 reads.
+Unlike \npscarf{} where the connections could be undone and rectified later if needed, a bridge in \npgraph{} will remain unchanged once created.
+The plot for \ec{} data clarifies this behaviour when a fluctuation can be observed in \npscarf{} assembly at $\simeq 3$-folds data coverage.
+On the other hand, the N50 length of \npgraph{} is always a monotonic increasing function. 
+The sharp \emph{jumping} patterns suggested that the linking information from long-read data had been stored and exploited at certain time point decided by the algorithm. 
+In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
+
+\begin{figure}[!hbt]
+\centering
+\subfloat[\emph{Citrobacter~freundii} CAV1374]{
+	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
+}
+\hfill
+\subfloat[\emph{Escherichia~coli} K12 MG1655]{
+	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
+}
+\\
+\subfloat[\emph{Klebsiella} 30660 NJST258]{
+	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
+}
+\hfill
+\subfloat[\emph{Klebsiella} NTUH K2044]{
+	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
+}
+\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
+\label{F:npgraph_rt}
+\end{figure}
+
+\section*{Discussion}
+
+% \end{itemize}
+Streaming assembly methods have been proven to be useful in saving time and resources compared to conventional batch algorithms with examples including \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
+This practice is helpful dealing with huge short-read data set because it can significantly reduce the local storage for the reads, as well as save time for a De Bruijn graph (DBG) construction while waiting for the data being retrieved.
+\npscarf{}, on the other hand, 
+is a hybrid assembler working on a pre-assembly set of short-read assembly contigs.
+It functions by scaffolding the contigs using real-time nanopore sequencing.
+The completion of genome assembly in parallel with the sequencing run provides explicit benefits in term of resource control and turn-around time for analysis~\cite{Cao2017scaffolding}.
+
+% Why hybrid???
+Hybrid approaches are still common practice in genome assembly and data analyses while Illumina sequencing retains cost and accuracy benefits over long-read sequencing.
+On the other hand, the third-generation sequencing methods such as Pacbio or Oxford Nanopore Technology are well-known for the ability to produce much longer reads that can further complete the Illumina assembly.
+As a consequence, it is rational to combine two sources of data together in a hybrid method that can offer accurate and complete genomes at the same time.
+\npscarf{}, following that philosophy, had been developed and deployed on real microbial genomes.
+
+However, due to the greedy bridging approach of the contig-based streaming algorithm, \npscarf{}`s results can suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+A default setting was optimized for microbial genomes input but cannot fit for all data from various experiments in practice.
+Also, the gap filling step has to rely on the lower accuracy nanopore reads thus the accuracy of the final assembly is also affected. 
+To tackle the quality issue while maintaining the streaming feature of the approach, a bridging method by assembly graph traversing has been proposed in this manuscript. 
+Our approach uses as its starting point a compact DBG assembly graph, followed by graph-traveseral, repeat resolution and identification of the longest possible un-branched paths that would represents contigs for the final assembly.
+
+Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} as well as \unicycler{} \cite{Wick2017unicycler}. 
+The available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
+The \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with minimum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are retained.
+In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
+On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
+The higher quality consensus reads are used to align with the assembly graph to find the best paths bridging pairs of anchored contigs.
+While this method employs the completeness of the data  set from the very beginning for a consensus step, the former only iterates over the batch of possible paths and relies on a scoring system for the final decision of graph traversal.
+Hence, in theory it can be adapted to a real-time pipeline.
+
+The challenge in adapting graph-based  approaches into streaming algorithm comes mainly from building a progressive implementation for path-finding and graph reducing module . 
+To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
+%The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time while the  nanopore sequencing process is still running.
+
+By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time.
+%Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly.
+%The next section will address this utility and the interactive GUI bundled in \npgraph{}.
+
+%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
+%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
+In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
+%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph
+
+\section*{Conclusion}  %%COMMENT_LC seems repetitive here
+%npgraph: how important hybrid assembly
+Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
+On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield and cost.
+Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
+\npscarf{} had been introduced initially to address these issues, however, the accuracy of the assembly output was affected by its greedy alignment-based scaffolding approach.
+Here we present \npgraph{}, a streaming hybrid assembly method working on the DBG assembly graph that is able to finish short-read assembly in real-time while minimizing the errors and mis-assemblies drastically.
+
+Compared to \npscarf, \npgraph{} algorithm employs more rigorous approach based on graph traversal.
+This might reduce the assembly errors because the bridging method is more accurate so that the reporting results are more reliable.
+The performance of \npgraph{} is comparable to \unicycler{} while consuming much less computational resources so that it can work on streaming mode. 
+Also, the integrated GUI allows users to visualize its animated output in a  more efficient way.
+
+On the other hand, similar to \unicycler{}, \npgraph{} relies on the initial assembly graph to generate the final assembly.
+The algorithm operates on the assumption of a high quality assembly from a well-supplied source of short-read data for a decent assembly graph to begin with.
+It then consumes a just-enough amount of data from a streaming input of nanopore reads to resolve the graph. 
+Finally, extra pre-processing and comprehensive binning on the initial graph could further improve the performance of the streaming assembler.
+
+%For more information, see \nameref{S1_Appendix}.
+
+\section*{Supporting information}
+
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+
+%\paragraph*{S1 File.}
+%\label{S1_File}
+%{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+%
+%\paragraph*{S1 Video.}
+%\label{S1_Video}
+%{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+%
+%\paragraph*{S1 Appendix.}
+%\label{S1_Appendix}
+%{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Table.}
+\label{S1_Table}
+Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+
+\section*{Acknowledgments}
+Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Nam id pretium nisi.
+Sed ac quam id nisi malesuada congue.
+Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+
+\nolinenumbers
+
+\begin{thebibliography}{10}
+
+\bibitem{Cao2017scaffolding}
+Cao MD, Nguyen SH, Ganesamoorthy D, Elliott AG, Cooper MA, Coin LJ.
+\newblock {Scaffolding and completing genome assemblies in real-time with
+  nanopore sequencing}.
+\newblock Nature Communications. 2017;8:14515.
+
+\bibitem{BankevichNA2012}
+Bankevich A, Nurk S, Antipov D, Gurevich AA, Dvorkin M, Kulikov AS, et~al.
+\newblock {SPAdes: A New Genome Assembly Algorithm and Its Applications to
+  Single-Cell Sequencing}.
+\newblock Journal of Computational Biology. 2012;19(5):455--477.
+\newblock doi:{10.1089/cmb.2012.0021}.
+
+\bibitem{Zerbino2008}
+Zerbino DR, Birney E.
+\newblock {Velvet: algorithms for de novo short read assembly using de Bruijn
+  graphs.}
+\newblock Genome research. 2008;18(5):821--9.
+
+\bibitem{Simpson2009}
+Simpson JT, Wong K, Jackman SD, Schein JE, Jones SJM, Birol I.
+\newblock {ABySS: A parallel assembler for short read sequence data}.
+\newblock Genome Research. 2009;19(6):1117--1123.
+
+\bibitem{CaoGC2016}
+Cao MD, Ganesamoorthy D, Cooper MA, Coin LJM.
+\newblock {Realtime analysis and visualization of MinION sequencing data with
+  npReader}.
+\newblock Bioinformatics. 2016;32(5):764--766.
+\newblock doi:{10.1093/bioinformatics/btv658}.
+
+\bibitem{Nguyen2017barcode}
+Nguyen SH, Duarte TP, Coin LJ, Cao MD.
+\newblock {Real-time demultiplexing Nanopore barcoded sequencing data with
+  npBarcode}.
+\newblock Bioinformatics. 2017;33(24):3988--3990.
+
+\bibitem{Ester96adensity-based}
+Ester M, Kriegel HP, Sander J, Xu X.
+\newblock A density-based algorithm for discovering clusters in large spatial
+  databases with noise.
+\newblock AAAI Press; 1996. p. 226--231.
+
+\bibitem{Kullback1951information}
+Kullback S, Leibler RA.
+\newblock On information and sufficiency.
+\newblock The annals of mathematical statistics. 1951;22(1):79--86.
+
+\bibitem{Kang2015metabat}
+Kang DD, Froula J, Egan R, Wang Z.
+\newblock {MetaBAT}, an efficient tool for accurately reconstructing single
+  genomes from complex microbial communities.
+\newblock PeerJ. 2015;3:e1165.
+
+\bibitem{Wu2014maxbin}
+Wu YW, Tang YH, Tringe SG, Simmons BA, Singer SW.
+\newblock {MaxBin}: an automated binning method to recover individual genomes
+  from metagenomes using an expectation-maximization algorithm.
+\newblock Microbiome. 2014;2(1):26.
+
+\bibitem{Dijkstra1959}
+Dijkstra EW.
+\newblock A note on two problems in connexion with graphs.
+\newblock Numerische mathematik. 1959;1(1):269--271.
+
+\bibitem{AntipovKM2015}
+Antipov D, Korobeynikov A, McLean JS, Pevzner PA.
+\newblock {hybridSPAdes: an algorithm for hybrid assembly of short and long
+  reads}.
+\newblock Bioinformatics. 2016;32(7):1009--1015.
+\newblock doi:{10.1093/bioinformatics/btv688}.
+
+\bibitem{Wick2017unicycler}
+Wick RR, Judd LM, Gorrie CL, Holt KE.
+\newblock Unicycler: resolving bacterial genome assemblies from short and long
+  sequencing reads.
+\newblock PLOS Computational Biology. 2017;13(6):e1005595.
+
+\bibitem{Mikheenko2018quast5}
+Mikheenko A, Prjibelski A, Saveliev V, Antipov D, Gurevich A.
+\newblock Versatile genome assembly evaluation with {QUAST-LG}.
+\newblock Bioinformatics. 2018;34(13):i142--i150.
+
+\bibitem{Li2013}
+Li H.
+\newblock {Aligning sequence reads, clone sequences and assembly contigs with
+  BWA-MEM}.
+\newblock arXiv. 2013; p.~3.
+
+\bibitem{Li2016}
+Li H.
+\newblock {Minimap and miniasm: fast mapping and de novo assembly for noisy
+  long sequences}.
+\newblock Bioinformatics. 2016;32(14):2103--2110.
+\newblock doi:{10.1093/bioinformatics/btw152}.
+
+\bibitem{Brudno2003glocal}
+Brudno M, Malde S, Poliakov A, Do CB, Couronne O, Dubchak I, et~al.
+\newblock {Glocal alignment: finding rearrangements during alignment}.
+\newblock Bioinformatics. 2003;19(suppl\_1):i54--i62.
+
+\bibitem{George2017M14}
+George S, Pankhurst L, Hubbard A, Votintseva A, Stoesser N, Sheppard AE, et~al.
+\newblock {Resolving plasmid structures in Enterobacteriaceae using the MinION
+  nanopore sequencer: assessment of MinION and MinION/Illumina hybrid data
+  assembly approaches}.
+\newblock Microbial genomics. 2017;3(8).
+
+\bibitem{Carattoli2014}
+Carattoli A, Zankari E, Garc{\`\i}a-Fernandez A, Larsen MV, Lund O, Villa L,
+  et~al.
+\newblock PlasmidFinder and pMLST: in silico detection and typing of plasmids.
+\newblock Antimicrobial agents and chemotherapy. 2014; p. AAC--02412.
+
+\bibitem{Potter2016rapid}
+Potter RF, D’souza AW, Dantas G.
+\newblock {The rapid spread of carbapenem-resistant Enterobacteriaceae}.
+\newblock Drug Resistance Updates. 2016;29:30--46.
+
+\bibitem{Rozov2017faucet}
+Rozov R, Goldshlager G, Halperin E, Shamir R.
+\newblock Faucet: streaming de novo assembly graph construction.
+\newblock Bioinformatics. 2017;34(1):147--154.
+
+\bibitem{Giordano2017}
+Giordano F, Aigrain L, Quail MA, Coupland P, Bonfield JK, Davies RM, et~al.
+\newblock {De novo yeast genome assemblies from MinION, PacBio and MiSeq
+  platforms}.
+\newblock Scientific reports. 2017;7(1):3935.
+
+\bibitem{Prjibelski2014}
+Prjibelski AD, Vasilinetc I, Bankevich A, Gurevich A, Krivosheeva T, Nurk S,
+  et~al.
+\newblock {ExSPAnder}: a universal repeat resolver for {DNA} fragment assembly.
+\newblock Bioinformatics. 2014;30(12):i293--i301.
+
+\end{thebibliography}
 

### 2020-03-06 plos_latex_template.tex
convert to eps

@@
 
+%\begin{figure}[!hpt]
+%\centering
+%\subfloat[Merging bridges]{
+%    \label{figure:npgraph_merge}
+%	\includegraphics[width=.48\textwidth]{images/bridge_merging.pdf}
+%}
+%\hfill
+%\subfloat[Knot untangled]{
+%    \label{figure:npgraph_untangle}
+%	\includegraphics[width=.48\textwidth]{images/knot.pdf}
+%}
+%\caption{Graph resolving algorithm.
+\ref{figure:npgraph_merge} the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
+\ref{figure:npgraph_untangle} A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
+%\label{figure:npgraph_pipeline}
+%\end{figure}
+
 \begin{figure}[!hpt]
 \centering
-\subfloat[Merging bridges]{
-    \label{figure:npgraph_merge}
-	\includegraphics[width=.48\textwidth]{images/bridge_merging.pdf}
-}
-\hfill
-\subfloat[Knot untangled]{
-    \label{figure:npgraph_untangle}
-	\includegraphics[width=.48\textwidth]{images/knot.pdf}
-}
+\includegraphics[width=\textwidth]{images/Fig1.eps}
 \caption{Graph resolving algorithm.
-\ref{figure:npgraph_merge} the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
-\ref{figure:npgraph_untangle} A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
+(a) the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
+(b) A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
 \label{figure:npgraph_pipeline}
@@
 In general, the bridging algorithm used to determine the best path is a combination of progressive merging, accumulated scoring and decision making modules.
-It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Figure~\ref{figure:npgraph_merge}.
+It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Figure~\ref{figure:npgraph_pipeline}(a).
 A set of candidate paths are listed and the best one can be selected amongst them given enough evidence. 
-The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\ref{figure:npgraph_untangle}).
+The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\ref{figure:npgraph_pipeline}(b)).
 
@@
 the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
+
 \begin{figure}[!hpt]
 \centering
-\parbox{\textwidth}{
-    \parbox{.57\textwidth}{
-        \subfloat{\includegraphics[width=\hsize]{images/dashboard.png}}
-    }
-    \hskip1em
-    \parbox{.44\textwidth}{%
-        \subfloat{\includegraphics[width=\hsize]{images/graph-view.png}}
-        \vskip1em
-        \subfloat{\includegraphics[width=\hsize]{images/console-view.png}}  
-    }
-}
-\caption[\npgraph{} user interface]{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}).
+\includegraphics[width=\textwidth]{images/Fig2.eps}
+\caption{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}).
 The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}).
@@
 At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
-In an example from Figure~\ref{figure:npgraph_merge}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+In an example from Figure~\ref{figure:npgraph_pipeline}(a), bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
 Each of the steps therefore is assigned a weighing score based on its alignment quality.
@@
 \centering
-\subfloat[Initial graph]{
-	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_0.png}
-}
-\hfill
-\subfloat[Resolved graph]{
-	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_2.png}
-}
-\caption[Assembly graph resolving on \npgraph{} Graph View]{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
+ \includegraphics[width=\textwidth]{images/Fig4.eps}
+\caption{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
 The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
@@
 \centering
-\includegraphics[width=.6\textwidth]{images/decompose.pdf}
-\caption[Example of graph decomposition into longest straight paths]{Example of graph decomposition into longest straight paths.
-Branching edges are masked out (shaded) leaving only straight paths (bold colored) to report.
+\includegraphics[width=.6\textwidth]{images/Fig5.eps}
+\caption{Example of graph decomposition into longest straight paths.
+Branching edges are masked out (faded) leaving only straight paths (bold) to report.
 There would be 3 contigs extracted by traversing along the straight paths here.}
@@
 We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
-This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_merge}).
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_pipeline}(a)).
 However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
@@
 
+%\begin{figure}[!hbt]
+%\centering
+%\subfloat[\emph{Citrobacter~freundii} CAV1374]{
+%	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
+%}
+%\hfill
+%\subfloat[\emph{Escherichia~coli} K12 MG1655]{
+%	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
+%}
+%\\
+%\subfloat[\emph{Klebsiella} 30660 NJST258]{
+%	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
+%}
+%\hfill
+%\subfloat[\emph{Klebsiella} NTUH K2044]{
+%	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
+%}
+%\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
+%\label{F:npgraph_rt}
+%\end{figure}
+
 \begin{figure}[!hbt]
 \centering
-\subfloat[\emph{Citrobacter~freundii} CAV1374]{
-	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
-}
-\hfill
-\subfloat[\emph{Escherichia~coli} K12 MG1655]{
-	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
-}
-\\
-\subfloat[\emph{Klebsiella} 30660 NJST258]{
-	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
-}
-\hfill
-\subfloat[\emph{Klebsiella} NTUH K2044]{
-	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
-}
-\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
+\includegraphics[width=\textwidth]{images/Fig3.eps}
+\caption{N50 statistics of real-time assembly by \npscarf{} and \npgraph{} for 4 bacterial samples.}
 \label{F:npgraph_rt}

### 2020-03-06 plos_latex_template.tex
mua

@@
 \usepackage{longtable,booktabs}
+\usepackage{ltablex}
+
 %% End preloads
@@
 \section*{Supporting information}
+\renewcommand{\figurename}{Supporting Figure}
+\renewcommand{\tablename}{Supporting Table}
+\renewcommand\thefigure{S\arabic{figure}}    
+\setcounter{figure}{0}
 
@@
 \paragraph*{S1 Fig.}
-\label{S1_Fig}
-Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+\label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
 Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
@@
 
+\begin{figure}[!ht]
+ \includegraphics[width=\textwidth]{images/FigS1.eps}
+ \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}}
+\end{figure}
+
 \paragraph*{S2 Fig.}
-\label{S2_Fig}
-Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
+\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
 The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
 
-%\paragraph*{S1 File.}
-%\label{S1_File}
-%{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\paragraph*{S1 Video.}
-%\label{S1_Video}
-%{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-%
-%\paragraph*{S1 Appendix.}
-%\label{S1_Appendix}
-%{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\begin{figure}[!ht]
+ \includegraphics[width=\textwidth]{images/FigS2.eps}
+ \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}}
+\end{figure}
 
@@
 Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+
+\makeatletter
+
+\newlength\oriarrayrulewidth  
+\newcount\orilowpenalty
+\newcommand\nobreakmidrule{%
+ \noalign{\global\oriarrayrulewidth\arrayrulewidth\relax
+          \global\orilowpenalty\@lowpenalty\relax  
+          \global\@lowpenalty=\numexpr-10000\relax%
+          \global\arrayrulewidth\lightrulewidth\relax}
+ \hline
+ \noalign{\global\@lowpenalty=\orilowpenalty\relax%
+          \global\arrayrulewidth\oriarrayrulewidth\relax}}
+
+\makeatother
+\setlength{\LTleft}{-1in}
+\setcounter{table}{0}
+
+\begin{longtable}[!hpt]{llcrrrrr}
+%\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
+\toprule
+    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
+    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
+    \hline  
+\endfirsthead
+\multicolumn{8}{c}%
+{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
+\hline
+    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
+    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
+\hline
+\endhead
+\hline \multicolumn{8}{r}{\textit{Continued on next page}} \\
+\endfoot
+\hline
+\endlastfoot
+
+\rowcolor{Gray}
+\multicolumn{8}{l}{random sequences no repeats} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  4110000 &  3  &  4000000  &  0  & 0.00  & 0.00\\*
+\rowcolor{Gray}
+& npScarf\_wag & 4109516  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
+\rowcolor{Gray}
+& npGraph-bwa & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
+\rowcolor{Gray}
+& hybridSPAdes & 4110231  &  3  & 4000077   &  0  & 0.00  &  0.07\\*
+\rowcolor{Gray}
+& Unicycler & 4110000  &  3  &  4000000  &  0  & 0.00  &  0.00\\
+\hline
+\multicolumn{8}{l}{random sequences some repeats} \\* %
+\nobreakmidrule
+& npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
+& npScarf\_wag & 4437094  &  7 &  2795129  &  0  &  0.00 &  1.07\\*
+& npGraph-bwa & 4110000  &  3  &  4000000  &  0 &  0.00 &  0.00\\*
+& npGraph-mm2 &  4110000 &  3  &   4000000 & 0  & 0.00  &  0.00\\*
+& hybridSPAdes & 4107566  &  3  &  3999364  &  0  & 0.02  & 0.02\\*
+& Unicycler &  4110000 &  3 & 4000000  &  0 & 0.00  &  0.00\\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{random sequences many repeats} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  4316934 &  8  &  3963485  &  24  & 11.55  & 34.54\\*
+\rowcolor{Gray}
+& npScarf\_wag &  5215965 &  16  &  1515563  &  37  & 0.32  & 7.22\\*
+\rowcolor{Gray}
+& npGraph-bwa & 4110000  &  3  &  4000000  &  0  &  0.32 & 0.15\\*
+\rowcolor{Gray}
+& npGraph-mm2 &  4110000 &  3  &  4000000  &  0  & 0.32  & 0.15\\*
+\rowcolor{Gray}
+& hybridSPAdes & 4108190  &  3  &  3999621  &  0  &  0.68 &  0.15\\*
+\rowcolor{Gray}
+& Unicycler & 4110000  &  3  &  4000000  &  0  &  0.32  & 0.15  \\
+\hline
+% \pagebreak
+% \toprule
+\multicolumn{8}{l}{\emph{Acinetobacter} A1} \\* %
+\nobreakmidrule
+& npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
+& npScarf\_wag & 3945166  &  3  &  3906368  &  1  & 7.00  & 14.02 \\*
+& npGraph-bwa & 3918374  &  2  &  3909643  &  0 & 16.34  & 0.61 \\*
+& npGraph-mm2 & 3885898  &  2  &  3877167  & 1 & 18.05  & 1.03 \\*
+& hybridSPAdes &  3929948 &  53  &  3353679  &  0  & 35.48  & 3.22\\*
+& Unicycler & 3917745  &  2 & 3909014  & 0  & 2.50  &  0.13\\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\emph{Acinetobacter} AB30} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf & 4512464  &  7  &  4304628  &  35  & 57.95  & 72.87\\*
+\rowcolor{Gray}
+& npScarf\_wag & 5315235  &  13  &  1267710  &  136  &  73.55 & 8.15\\*
+\rowcolor{Gray}
+& npGraph-bwa & 4335342  &  2  &  4148952  &  1  & 16.93  & 1.45\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 4335790  &  1  &  4335790  & 0   &  6.97 & 0.25\\*
+\rowcolor{Gray}
+& hybridSPAdes & 4337369  &  3  &  2701005  &  0  &  12.80 &  1.39\\*
+\rowcolor{Gray}
+& Unicycler &  4333041 &  1  &  4333041  &  1  &  6.42 &  0.53\\
+\hline
+\multicolumn{8}{l}{\ec{} K12 MG1655} \\* %
+\nobreakmidrule
+& npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
+& npScarf\_wag &  4687952 &  3  &  4641732  &  0  & 6.55  &  1.96\\*
+& npGraph-bwa & 4641743  &  1  &  4641743  & 0  &  4.50 & 0.43 \\*
+& npGraph-mm2 & 4641820  &  1  &  4641820  &  0 &  3.88 & 0.26 \\*
+& hybridSPAdes &  4644555 &  1  &  4641036  &  0  & 0.62  & 0.09\\*
+& Unicycler & 4641650  &  1 &  4641650 &  0 & 3.43  & 0.26 \\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\ec{} O25b H4-ST131} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  5245913 &  3  &  5095571  &  7  &  7.05 & 18.81\\*
+\rowcolor{Gray}
+& npScarf\_wag & 5292700  &  3  &  3469617  &  9  &  9.03 & 1.55\\*
+\rowcolor{Gray}
+& npGraph-bwa & 5237821  &  7  &  4049493  &  1  &  3.38 & 0.31\\*
+\rowcolor{Gray}
+& npGraph-mm2 &  5249799 &  3  &  5110117  &  0  &  2.40 & 0.15\\*
+\rowcolor{Gray}
+& hybridSPAdes & 5252762  &  8  &  4258948  &  2  &  5.43 &  0.57\\*
+\rowcolor{Gray}
+& Unicycler & 5249442  &  3  &  5109760  &  0  & 4.02 & 0.27 \\
+\hline
+% \pagebreak
+% \toprule
+\multicolumn{8}{l}{\emph{Klebsiella} 30660 NJST258 1} \\* %
+\nobreakmidrule
+& npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
+& npScarf\_wag & 5613780  &  7  &  5268535  &  6  & 1.59  & 1.92\\*
+& npGraph-bwa & 5534843  &  8  &  5263229  &  0  & 3.15  & 0.76\\*
+& npGraph-mm2 & 5534878  &  8  &  5263264  &  0  & 2.75  & 0.74\\*
+& hybridSPAdes &  5545668 & 8   &  5545668  &  2  & 4.95  & 0.09 \\*
+& Unicycler & 5537860  &  9  &  5263196  &  0  & 1.34  & 0.51 \\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\emph{Klebsiella} MGH 78578} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  5729304 &  5  &  5316429  &  12  & 14.90  & 20.27\\*
+\rowcolor{Gray}
+& npScarf\_wag & 5754443  &  5  &  3026286  &  16  &  8.17 & 2.56\\*
+\rowcolor{Gray}
+& npGraph-bwa &  5695801 &  7  &  5311745  &  1  & 12.65  & 1.25\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 5696302  &  6  &  5315267  &  0  &  6.06 & 0.44\\*
+\rowcolor{Gray}
+& hybridSPAdes &  5706470 &  11  &  5315273  &  1  & 3.82  &  0.67\\*
+\rowcolor{Gray}
+& Unicycler &  5694231 &  14  &  5315096  &  0  & 5.38 &  0.21\\
+\hline
+\multicolumn{8}{l}{\emph{Klebsiella} NTUH-K2044} \\* %
+\nobreakmidrule
+& npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
+& npScarf\_wag & 5530559  &  3  &  5249369  &  2  &  2.25 &  1.35\\*
+& npGraph-bwa & 5472629  &  2  &  5248476  & 0  & 2.52  &  0.31\\*
+& npGraph-mm2 &  5472655 &  2  &  5248503  &  0 &  1.21 &  0.26\\*
+& hybridSPAdes & 5473572  &  2  &  5248894  &  0  &  0.44 & 0.15\\*
+& Unicycler & 5472697  & 2  & 5248545  &  0 & 2.41  &  0.35\\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\emph{Mycobacterium tuberculosis} H37Rv} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  4498245 &  4  & 4402238   &  8  & 5.15  & 2.68\\*
+\rowcolor{Gray}
+& npScarf\_wag &  4506056 &  4  &  4410942  &  3  & 6.81  & 2.59\\*
+\rowcolor{Gray}
+& npGraph-bwa & 4411406  &  1  &  4411406  &  0  & 1.88  & 0.43\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 4411532  & 1   &  4411532  &  0  & 0.68  & 0.00\\*
+\rowcolor{Gray}
+& hybridSPAdes & 4413942  &  1  &  4410519  &  0  &  0.75 &  0.11\\*
+\rowcolor{Gray}
+& Unicycler & 4411538  &  1  &  4411538  &  0  &  2.22 &  0.34\\
+\hline
+% \pagebreak
+% \toprule
+\multicolumn{8}{l}{\emph{Saccharomyces cerevisiae} S288c} \\* %
+\nobreakmidrule
+& npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*
+& npScarf\_wag & 12003203  &  21  &  917017  &  21  & 69.14  & 5.47 \\*
+& npGraph-bwa & 11921736  &  40  &  913090  &  3 &  38.04 &  1.94\\*
+& npGraph-mm2 & 11920984  &  38  &  913198  &  2 &  20.66 &  0.95\\*
+& hybridSPAdes &  12027533 &  45  &  770543  &  5  & 32.58  & 1.94\\*
+& Unicycler &  11847655 & 72  & 909114  &  0 & 21.81  &  1.04\\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\emph{Shigella dysenteriae}  Sd197} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  4586075 &  173  & 36560   &  55  & 120.14  & 111.59\\*
+\rowcolor{Gray}
+& npScarf\_wag & 5462918  &  92  &  98791  &  105  &  147.48 & 79.28\\*
+\rowcolor{Gray}
+& npGraph-bwa & 4564058  &  6  &  4369264  &  5  & 80.64  & 11.16\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 4558920  &  6  &  4364264  &  7  & 75.51  & 10.98\\*
+\rowcolor{Gray}
+& hybridSPAdes &  4519131 & 23   &  821249  & 96   & 9.57  &  1.42\\*
+\rowcolor{Gray}
+& Unicycler & 4560901  & 3   &  4369231  &  0  & 11.88  & 1.05 \\
+\hline
+\multicolumn{8}{l}{\emph{Shigella sonnei} 53G} \\* %
+\nobreakmidrule
+& npScarf &  6441461 &  20  &  1953896  &  82  & 164.02  &  219.52\\*
+& npScarf\_wag & -  &  -  &  -  &  -  & -  &  -\\*
+& npGraph-bwa & 5211544  &   4 &  4988532  & 0  & 14.53  &  0.31\\*
+& npGraph-mm2 & 5211527  &  4  &   4988519 & 0  &  8.56 &  0.17\\*
+& hybridSPAdes & 5223875  &  8  &  2195455  &  2  & 41.92  & 0.06\\*
+& Unicycler &  5220517 &  5 &  4988548 & 0  & 7.39  &  0.52\\
+\hline
+\rowcolor{Gray}
+\multicolumn{8}{l}{\emph{Streptococcus suis} BM407} \\* %
+\nobreakmidrule
+\rowcolor{Gray}
+& npScarf &  2183951 & 3   &  2146594  &  0  & 21.51  & 9.17\\*
+\rowcolor{Gray}
+& npScarf\_wag & 2289880  &  3  &  1493189  &  1  & 3.17  & 1.96\\*
+\rowcolor{Gray}
+& npGraph-bwa & 2154623  &  6  &  2131479  &  1  & 5.25  & 0.28\\*
+\rowcolor{Gray}
+& npGraph-mm2 & 2149876  &  6  &  2146774  &  0  & 1.44  & 0.28\\*
+\rowcolor{Gray}
+& hybridSPAdes & 2172703  &  2  &  2146237  &  0  & 6.82  &  0.09\\*
+\rowcolor{Gray}
+& Unicycler &  2170829 &   2 &  2146250  &  0  &  2.67 & 0.32 \\
+\hline
+\end{longtable}
 

### 2020-03-06 plos_latex_template.tex
data availability

@@
 \centering
-\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}}
+\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on synthetic data.} 
 \label{table:npgraph_compare}
@@
 \label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
-Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
-On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
 
@@
  \includegraphics[width=\textwidth]{images/FigS1.eps}
- \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}}
+ \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}
 \end{figure}
@@
 \paragraph*{S2 Fig.}
-\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
-The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}
 
@@
  \includegraphics[width=\textwidth]{images/FigS2.eps}
- \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}}
+ \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
 \end{figure}
 
+\clearpage
 \paragraph*{S1 Table.}
@@
 %\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
+%\label{supp_tab:synthetic_benchmark}\\
 \toprule
@@
 
+\section*{Data availability}
+All data used for benchmarking were from public sources.
+The synthetic data was downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}.
+The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.
+
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
 

### 2020-07-12 plos_latex_edit.tex
Starting revision

--- 2020-03-06 plos_latex_template.tex
@@
 %% END MACROS SECTION
-
+\usepackage{cancel}
+\newcommand\replace[1]{\textcolor{red}{#1}}
 %% npGraph
@@
 To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
- define a customised metric which is sample and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
+ define a customised metric which is \cancel{sample} \replace{simple} and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
 %The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count).

### 2020-08-09 plos_latex_edit.tex
lrscaf included

@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others?
-using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+\replace{}
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
@@
  \includegraphics[width=\textwidth]{images/FigS2.eps}
- \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
+ \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\cancel{\unicycler{}}\replace{\npgraph{}} and (b)~\cancel{\npgraph{}}\replace{\unicycler{}}.
 The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
@@
 \label{S1_Table}
-Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+Benchmarking different methods using $\mathtt{\replace{lrscaf}}$, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
 
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{-} & \replace{-} & \replace{-} & \replace{-} & \replace{-} & \replace{-} \\*
+\rowcolor{Gray}
 & npScarf &  4110000 &  3  &  4000000  &  0  & 0.00  & 0.00\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{4113104} & \replace{6} & \replace{4002298} & \replace{0} & \replace{0.00} & \replace{0.00}\\*
 & npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{4119020} & \replace{12} & \replace{4002117} & \replace{0} & \replace{0.03} & \replace{0.79}\\* 
+\rowcolor{Gray}
 & npScarf &  4316934 &  8  &  3963485  &  24  & 11.55  & 34.54\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{3896799} & \replace{4} & \replace{3886381} & \replace{0} & \replace{0.47} & \replace{
+0.36}\\*
 & npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{4367657} & \replace{27} & \replace{1035967} & \replace{13} & \replace{30.11} & \replace{1.42}\\* 
+\rowcolor{Gray}
 & npScarf & 4512464  &  7  &  4304628  &  35  & 57.95  & 72.87\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{4732001} & \replace{16} & \replace{692794} & \replace{7} & \replace{3.42} & \replace{0.58}\\*
 & npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{5410854} & \replace{21} & \replace{910949} & \replace{9} & \replace{13.70} & \replace{0.87}\\*
+\rowcolor{Gray}
 & npScarf &  5245913 &  3  &  5095571  &  7  &  7.05 & 18.81\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{5512518} & \replace{20} & \replace{777919} & \replace{26} & \replace{3.52} & \replace{0.38}\\*
 & npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{5823340} & \replace{38} & \replace{559414} & \replace{7} & \replace{5.92} & \replace{1.27}\\*
+\rowcolor{Gray}
 & npScarf &  5729304 &  5  &  5316429  &  12  & 14.90  & 20.27\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{5470282} & \replace{8} & \replace{2951488} & \replace{9} & \replace{3.04} & \replace{2.62}\\*
 & npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{4260869} & \replace{12} & \replace{3215170} & \replace{8} & \replace{6.69} & \replace{2.27}\\*
+\rowcolor{Gray}
 & npScarf &  4498245 &  4  & 4402238   &  8  & 5.15  & 2.68\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{12486884} & \replace{214} & \replace{254587} & \replace{27} & \replace{16.45} & \replace{1.97}\\*
 & npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{4678609} & \replace{175} & \replace{376897} & \replace{26} & \replace{3.91} & \replace{2.35}\\*
+\rowcolor{Gray}
 & npScarf &  4586075 &  173  & 36560   &  55  & 120.14  & 111.59\\*
@@
 \nobreakmidrule
+& \replace{lrscaf} & \replace{5266645} & \replace{128} & \replace{429353} & \replace{27} & \replace{9.72} & \replace{1.19}\\*
 & npScarf &  6441461 &  20  &  1953896  &  82  & 164.02  &  219.52\\*
@@
 \rowcolor{Gray}
+& \replace{lrscaf} & \replace{2231488} & \replace{10} & \replace{683404} & \replace{6} & \replace{11.96} & \replace{1.37}\\*
+\rowcolor{Gray}
 & npScarf &  2183951 & 3   &  2146594  &  0  & 21.51  & 9.17\\*
@@
 
+\bibitem{Qin2019}
+Qin, M., Wu, S., Li, A., Zhao, F., Feng, H., Ding, L., Ruan, J
+\newblock {{LRScaf}: improving draft genomes using long noisy reads}
+\newblock BMC Genomics. 2019;20(1):955
 \end{thebibliography}

### 2020-08-11 plos_latex_edit.tex
more editting

--- 2020-03-06 plos_latex_template.tex
@@
 %% END MACROS SECTION
-
+\usepackage[normalem]{ulem}
+\newcommand\cancel[1]{\sout{#1}}
+\newcommand\addnew[1]{\textcolor{red}{#1}}
 %% npGraph
@@
 To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
- define a customised metric which is sample and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
+ define a customised metric which is \cancel{sample} \addnew{simple} and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
 %The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count).
@@
 
-Due to false alignments from shorter contigs to the long reads, not all of the reported step nodes are necessary to be appeared in the ultimate path resolved by the bridge. 
+Due to false \addnew{positive} alignments from shorter contigs to the long reads, not all of the reported step nodes \cancel{are necessary to be appeared} \addnew{would appear} in the ultimate path resolved by the bridge.
 In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
-For that reason, a strategy similar to binary searching is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
-
-Before that, we define Algorithm~\ref{algo:findpath} to demonstrates the path finding algorithm for two nodes given their estimated distance. In which, function 
-$\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n$ 
-from line 3 of the algorithm's pseudo code builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance regarding nanopore read error rate) is reached.
+For that reason, a strategy similar to binary search\cancel{ing} is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
+\addnew{Briefly, it recursively looks for sub-paths connecting pairs of step nodes in-between 2 anchors and return a final continuous path with the highest score.}
+\cancel{Before that, }We define Algorithm~\ref{algo:findpath} \addnew{as the \emph{base} sub-rountine} to \cancel{demonstrates the path finding algorithm for} \addnew{find paths between a \emph{connectable} pair of} two \addnew{step} nodes given their estimated distance.
+In which, function
+\[
+\mathtt{shortestTree}(\overrightarrow{vertex},distance) : (V,Z) \rightarrow V^n
+\]
+from line 3 \cancel{of the algorithm's pseudo code} builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance \cancel{regarding nanopore read} \addnew{for the nanopore} error rate) is reached.
 This task is implemented based on Dijkstra algorithm.
@@
 \KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
-\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_2}$ that maximize the likelihood of the step list.}
+\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
 \SetKwFunction{BinaryBridging}{BinaryBridging} 
@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others?
-using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+\addnew{}
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
@@
  \includegraphics[width=\textwidth]{images/FigS2.eps}
- \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}.
+ \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\cancel{\unicycler{}}\addnew{\npgraph{}} and (b)~\cancel{\npgraph{}}\addnew{\unicycler{}}.
 The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
@@
 \label{S1_Table}
-Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+Benchmarking different methods using $\mathtt{\addnew{lrscaf}}$, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
 
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} \\*
+\rowcolor{Gray}
 & npScarf &  4110000 &  3  &  4000000  &  0  & 0.00  & 0.00\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{4113104} & \addnew{6} & \addnew{4002298} & \addnew{0} & \addnew{0.00} & \addnew{0.00}\\*
 & npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{4119020} & \addnew{12} & \addnew{4002117} & \addnew{0} & \addnew{0.03} & \addnew{0.79}\\* 
+\rowcolor{Gray}
 & npScarf &  4316934 &  8  &  3963485  &  24  & 11.55  & 34.54\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{3896799} & \addnew{4} & \addnew{3886381} & \addnew{0} & \addnew{0.47} & \addnew{
+0.36}\\*
 & npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{4367657} & \addnew{27} & \addnew{1035967} & \addnew{13} & \addnew{30.11} & \addnew{1.42}\\* 
+\rowcolor{Gray}
 & npScarf & 4512464  &  7  &  4304628  &  35  & 57.95  & 72.87\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{4732001} & \addnew{16} & \addnew{692794} & \addnew{7} & \addnew{3.42} & \addnew{0.58}\\*
 & npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{5410854} & \addnew{21} & \addnew{910949} & \addnew{9} & \addnew{13.70} & \addnew{0.87}\\*
+\rowcolor{Gray}
 & npScarf &  5245913 &  3  &  5095571  &  7  &  7.05 & 18.81\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{5512518} & \addnew{20} & \addnew{777919} & \addnew{26} & \addnew{3.52} & \addnew{0.38}\\*
 & npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{5823340} & \addnew{38} & \addnew{559414} & \addnew{7} & \addnew{5.92} & \addnew{1.27}\\*
+\rowcolor{Gray}
 & npScarf &  5729304 &  5  &  5316429  &  12  & 14.90  & 20.27\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{5470282} & \addnew{8} & \addnew{2951488} & \addnew{9} & \addnew{3.04} & \addnew{2.62}\\*
 & npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{4260869} & \addnew{12} & \addnew{3215170} & \addnew{8} & \addnew{6.69} & \addnew{2.27}\\*
+\rowcolor{Gray}
 & npScarf &  4498245 &  4  & 4402238   &  8  & 5.15  & 2.68\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{12486884} & \addnew{214} & \addnew{254587} & \addnew{27} & \addnew{16.45} & \addnew{1.97}\\*
 & npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{4678609} & \addnew{175} & \addnew{376897} & \addnew{26} & \addnew{3.91} & \addnew{2.35}\\*
+\rowcolor{Gray}
 & npScarf &  4586075 &  173  & 36560   &  55  & 120.14  & 111.59\\*
@@
 \nobreakmidrule
+& \addnew{lrscaf} & \addnew{5266645} & \addnew{128} & \addnew{429353} & \addnew{27} & \addnew{9.72} & \addnew{1.19}\\*
 & npScarf &  6441461 &  20  &  1953896  &  82  & 164.02  &  219.52\\*
@@
 \rowcolor{Gray}
+& \addnew{lrscaf} & \addnew{2231488} & \addnew{10} & \addnew{683404} & \addnew{6} & \addnew{11.96} & \addnew{1.37}\\*
+\rowcolor{Gray}
 & npScarf &  2183951 & 3   &  2146594  &  0  & 21.51  & 9.17\\*

### 2020-08-12 plos_latex_edit.tex
edit intro for motivation

@@
 
-Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material
-which  can be obtained. 
+Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material which  can be obtained. 
 %This provides the potential use of DNA sequencing into a wide range of applications in medical 
 %and scientific research. 
-However, the time from sample to result remains a barrier to adoption of 
-sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making.  While
-there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT);  algorithms for streaming analyses  of such real-time data are still
-in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use.
-
-One particular strength of ONT technology is the production of ultra long reads. This is complementary to the dominant
-short read sequencing technology Illumina which is cheaper and has higher per base read quality
-but is unable to resolve the complex regions of the genome due to its read length limitation. A natural combination of
-the two technologies is in hybrid assembly of genomes. Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to 
-scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.
-However, \npscarf{} ignores the rich  connectivity information in the short read assembly graph, and as a result is prone to mis-assembly.
+However, the time from sample to result remains a barrier to adoption of sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making. 
+While there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT), algorithms for streaming analyses of such real-time data are still in their infancy.
+Effective streaming methodology will help bridge the gap between potential and practical use.
+\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized selective and/or enrichment sequencing on ONT platforms.
+To function properly, methods using this protocol must implement rapid-responsed operations on the streaming data, for example in ReadFish~\cite{Payne2020}.}
+
+One particular strength of ONT technology is the production of ultra long reads. 
+This is complementary to the dominant short read sequencing technology Illumina which is cheaper and has higher per base read quality but is unable to resolve the complex regions of the genome due to its read length limitation.
+A natural combination of the two technologies is in hybrid assembly of genomes.
+Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.
+However, \npscarf{} ignores the rich connectivity information in the short read assembly graph, and as a result is relatively prone to mis-assembly compared to alternative methods.
 %The strategy proved to be
@@
 
+\bibitem{Payne2020}
+Payne A, Holmes N, Clarke T, Munro R, Debebe B, Loose M.
+\newblock Nanopore adaptive sequencing for mixed samples, whole exome capture and targeted panels.
+\newblock bioRxiv 2020.02.03.926956; 
+\newblock doi: https://doi.org/10.1101/2020.02.03.926956
+
 \bibitem{Cao2017scaffolding}
@@
 Potter RF, D’souza AW, Dantas G.
-\newblock {The rapid spread of carbapenem-resistant Enterobacteriaceae}.
+\newblock The rapid spread of carbapenem-resistant \emph{Enterobacteriaceae}.
 \newblock Drug Resistance Updates. 2016;29:30--46.
@@
 Giordano F, Aigrain L, Quail MA, Coupland P, Bonfield JK, Davies RM, et~al.
-\newblock {De novo yeast genome assemblies from MinION, PacBio and MiSeq
-  platforms}.
+\newblock De novo yeast genome assemblies from MinION, PacBio and MiSeq platforms.
 \newblock Scientific reports. 2017;7(1):3935.
@@
   et~al.
-\newblock {ExSPAnder}: a universal repeat resolver for {DNA} fragment assembly.
+\newblock ExSPAnder: a universal repeat resolver for DNA fragment assembly.
 \newblock Bioinformatics. 2014;30(12):i293--i301.
@@
 \bibitem{Qin2019}
-Qin, M., Wu, S., Li, A., Zhao, F., Feng, H., Ding, L., Ruan, J
-\newblock {{LRScaf}: improving draft genomes using long noisy reads}
+Qin M, Wu S, Li A, Zhao F, Feng H, Ding L, Ruan J.
+\newblock LRScaf: improving draft genomes using long noisy reads.
 \newblock BMC Genomics. 2019;20(1):955
+
 \end{thebibliography}
-
 \end{document}

### 2020-08-12 plos_latex_edit.tex
fake motivation

@@
 Effective streaming methodology will help bridge the gap between potential and practical use.
-\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized selective and/or enrichment sequencing on ONT platforms.
-To function properly, methods using this protocol must implement rapid-responsed operations on the streaming data, for example in ReadFish~\cite{Payne2020}.}
+\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized targeted sequencing on ONT platforms.
+To function properly, such methods must implement a real-time ultrafast operation on the streaming data, \EG{} in ReadFish~\cite{Payne2020}.
+Up until now, there is a shortage of similar tools that can utilize this distinctive feature.}
 

### 2020-09-06 plos_latex_edit.tex
update

--- 2020-08-12 plos_latex_edit.tex
@@
 Effective streaming methodology will help bridge the gap between potential and practical use.
-\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized selective and/or enrichment sequencing on ONT platforms.
-To function properly, methods using this protocol must implement rapid-responsed operations on the streaming data, for example in ReadFish~\cite{Payne2020}.}
 
@@
 This is complementary to the dominant short read sequencing technology Illumina which is cheaper and has higher per base read quality but is unable to resolve the complex regions of the genome due to its read length limitation.
-A natural combination of the two technologies is in hybrid assembly of genomes.
+\addnew{Hybrid assembly with ONT reads provides the opportunity to use long reads to fully resolve existing microbial genome assemblies.
+However, in order achieve this in an effective manner it is necessary to avoid both under-sequencing (and thus not completely resolving the assembly) or over-sequencing (and thus incurring unnecessary costs and time-to -results).
+In addition, the release of Read Until API provides the opportunity to selectively enrich parts of the genome, as has been implemented in customised targeted sequencing applications ~\cite{Payne2020}.
+The combination of ReadUntil with  streaming hybrid assembly opens the possibility for further efficiency gains by targeting sequencing to unresolved regions of the genome.
+}
+
 Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.
@@
 
-\subsection*{Algorithm in details}
+\subsection*{Algorithm  details}
 The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph pre-processing; (2) graph resolving and simplifying; (3) post-processing and reporting results. 

### 2020-09-08 plos_latex_clean.tex
Lachlan revision 1

--- 2020-09-06 plos_latex_edit.tex
@@
 \usepackage[normalem]{ulem}
-\newcommand\cancel[1]{\sout{#1}}
-\newcommand\addnew[1]{\textcolor{red}{#1}}
 %% npGraph
@@
 \newcommand{\npgraph}{$\mathtt{npGraph}$}
+\newcommand{\lrscaf}{$\mathtt{npGraph}$}
 \newcommand{\canu}{$\mathtt{Canu}$}
@@
 \newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}
+\newcommand{\lrscarf}{$\mathtt{LRScaf}$}
 
@@
 This is complementary to the dominant short read sequencing technology Illumina which is cheaper and has higher per base read quality but is unable to resolve the complex regions of the genome due to its read length limitation.
-\addnew{Hybrid assembly with ONT reads provides the opportunity to use long reads to fully resolve existing microbial genome assemblies.
+Hybrid assembly with ONT reads provides the opportunity to use long reads to fully resolve existing microbial genome assemblies.
 However, in order achieve this in an effective manner it is necessary to avoid both under-sequencing (and thus not completely resolving the assembly) or over-sequencing (and thus incurring unnecessary costs and time-to -results).
@@
 The combination of ReadUntil with  streaming hybrid assembly opens the possibility for further efficiency gains by targeting sequencing to unresolved regions of the genome.
-}
 
@@
 To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
- define a customised metric which is \cancel{sample} \addnew{simple} and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
+ define a customised metric which is simple and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
 %The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count).
@@
 
-Due to false \addnew{positive} alignments from shorter contigs to the long reads, not all of the reported step nodes \cancel{are necessary to be appeared} \addnew{would appear} in the ultimate path resolved by the bridge.
+Due to false positive alignments from shorter contigs to the long reads, not all of the reported step nodes would appear in the ultimate path resolved by the bridge. 
 In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
-For that reason, a strategy similar to binary search\cancel{ing} is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
-\addnew{Briefly, it recursively looks for sub-paths connecting pairs of step nodes in-between 2 anchors and return a final continuous path with the highest score.}
-\cancel{Before that, }We define Algorithm~\ref{algo:findpath} \addnew{as the \emph{base} sub-rountine} to \cancel{demonstrates the path finding algorithm for} \addnew{find paths between a \emph{connectable} pair of} two \addnew{step} nodes given their estimated distance.
-In which, function
+For that reason, a strategy similar to binary search is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
+Briefly, it recursively looks for sub-paths connecting pairs of step nodes in-between 2 anchors and return a final continuous path with the highest score.
+We define Algorithm~\ref{algo:findpath} as the \emph{base} sub-rountine to find paths between a \emph{connectable} pair of two step nodes given their estimated distance. In which, function 
 \[
@@
 \]
-from line 3 \cancel{of the algorithm's pseudo code} builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance \cancel{regarding nanopore read} \addnew{for the nanopore} error rate) is reached.
+from line 3 builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance for the nanopore error rate) is reached.
 This task is implemented based on Dijkstra algorithm.
@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
-\addnew{}
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
@@
 The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments, without fully succeeding.
+
+\lrscaf{} has been designed as a computationally efficient hybrid assembly tool which is scalable to large genomes.
+We ran \lrscaf{} using default parameters on the extended benchmarking set presented in Supplementary table 1.
+We observed that  \lrscaf{} assemblies had fewer misassemblies than \npscarf{}, and also exhibited a low mismatch and indel rate, but produced more fragmented assemblies than either \npgraph{} or \unicycler{}.
 
@@
  \includegraphics[width=\textwidth]{images/FigS2.eps}
- \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\cancel{\unicycler{}}\addnew{\npgraph{}} and (b)~\cancel{\npgraph{}}\addnew{\unicycler{}}.
+ \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
 The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
@@
 \label{S1_Table}
-Benchmarking different methods using $\mathtt{\addnew{lrscaf}}$, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
 
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} & \addnew{-} \\*
+& LRScaf & - & - & - & - & - & - \\*
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{4113104} & \addnew{6} & \addnew{4002298} & \addnew{0} & \addnew{0.00} & \addnew{0.00}\\*
+& LRScaf & 4113104 & 6 & 4002298 & 0 & 0.00 & 0.00\\*
 & npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{4119020} & \addnew{12} & \addnew{4002117} & \addnew{0} & \addnew{0.03} & \addnew{0.79}\\* 
+& LRScaf & 4119020 & 12 & 4002117 & 0 & 0.03 & 0.79\\* 
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{3896799} & \addnew{4} & \addnew{3886381} & \addnew{0} & \addnew{0.47} & \addnew{
-0.36}\\*
+& LRScaf & 3896799 & 4 & 3886381 & 0 & 0.47 & 0.36\\*
 & npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{4367657} & \addnew{27} & \addnew{1035967} & \addnew{13} & \addnew{30.11} & \addnew{1.42}\\* 
+& LRScaf & 4367657 & 27 & 1035967 & 13 & 30.11 & 1.42\\* 
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{4732001} & \addnew{16} & \addnew{692794} & \addnew{7} & \addnew{3.42} & \addnew{0.58}\\*
+& LRScaf & 4732001 & 16 & 692794 & 7 & 3.42 & 0.58\\*
 & npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{5410854} & \addnew{21} & \addnew{910949} & \addnew{9} & \addnew{13.70} & \addnew{0.87}\\*
+& LRScaf & 5410854 & 21 & 910949 & 9 & 13.70 & 0.87\\*
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{5512518} & \addnew{20} & \addnew{777919} & \addnew{26} & \addnew{3.52} & \addnew{0.38}\\*
+& LRScaf & 5512518 & 20 & 777919 & 26 & 3.52 & 0.38\\*
 & npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{5823340} & \addnew{38} & \addnew{559414} & \addnew{7} & \addnew{5.92} & \addnew{1.27}\\*
+& LRScaf & 5823340 & 38 & 559414 & 7 & 5.92 & 1.27\\*
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{5470282} & \addnew{8} & \addnew{2951488} & \addnew{9} & \addnew{3.04} & \addnew{2.62}\\*
+& LRScaf & 5470282 & 8 & 2951488 & 9 & 3.04 & 2.62\\*
 & npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{4260869} & \addnew{12} & \addnew{3215170} & \addnew{8} & \addnew{6.69} & \addnew{2.27}\\*
+& LRScaf & 4260869 & 12 & 3215170 & 8 & 6.69 & 2.27\\*
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{12486884} & \addnew{214} & \addnew{254587} & \addnew{27} & \addnew{16.45} & \addnew{1.97}\\*
+& LRScaf & 12486884 & 214 & 254587 & 27 & 16.45 & 1.97\\*
 & npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{4678609} & \addnew{175} & \addnew{376897} & \addnew{26} & \addnew{3.91} & \addnew{2.35}\\*
+& LRScaf & 4678609 & 175 & 376897 & 26 & 3.91 & 2.35\\*
 \rowcolor{Gray}
@@
 \nobreakmidrule
-& \addnew{lrscaf} & \addnew{5266645} & \addnew{128} & \addnew{429353} & \addnew{27} & \addnew{9.72} & \addnew{1.19}\\*
+& LRScaf & 5266645 & 128 & 429353 & 27 & 9.72 & 1.19\\*
 & npScarf &  6441461 &  20  &  1953896  &  82  & 164.02  &  219.52\\*
@@
 \rowcolor{Gray}
-& \addnew{lrscaf} & \addnew{2231488} & \addnew{10} & \addnew{683404} & \addnew{6} & \addnew{11.96} & \addnew{1.37}\\*
+& LRScaf & 2231488 & 10 & 683404 & 6 & 11.96 & 1.37\\*
 \rowcolor{Gray}

### 2020-09-08 plos_latex_edit.tex
Lachlan revision 1

@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \addnew{\lrscaf{} version 1.1.9} and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
 \addnew{}
@@
 The progressive path finding module tried to induce the most likely solution from a stream of coarse-grained alignments, without fully succeeding.
+
+\addnew{\lrscaf{} has been designed as a computationally efficient hybrid assembly tool which is scalable to large genomes.
+We ran \lrscaf{} using default parameters on the extended benchmarking set presented in Supplementary table 1.
+We observed that  \lrscaf{} assemblies had fewer misassemblies than \npscarf{}, and also exhibited a low mismatch and indel rate, but produced more fragmented assemblies than either \npgraph{} or \unicycler{}.
+}
 

### 2020-09-13 plos_latex_clean.tex
reorder algorithm1&2

@@
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
-A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
+A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. This is designed to support the real-time monitoring of
 the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
@@
 \subsubsection*{Building bridges in real-time}
-Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
-A bridge must start from a unique contig, or \emph{anchor} node, and end at another when completed.
+Bridge is the data structure designed to identify the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
+A bridge must start from a unique contig, or \emph{anchor} node, and end at another if completed.
 Located in-between are nodes known as \emph{steps} and distances between them are called \emph{spans} of the bridge.
@@
 \subsubsection*{Path finding algorithm}
-Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them.
-Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
-As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search.
-
-Due to false positive alignments from shorter contigs to the long reads, not all of the reported step nodes would appear in the ultimate path resolved by the bridge. 
-In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
-For that reason, a strategy similar to binary search is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
-Briefly, it recursively looks for sub-paths connecting pairs of step nodes in-between 2 anchors and return a final continuous path with the highest score.
-We define Algorithm~\ref{algo:findpath} as the \emph{base} sub-rountine to find paths between a \emph{connectable} pair of two step nodes given their estimated distance. In which, function 
+Given a proposed bridge with 2 anchors $B=\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_n}\rbrace$ identified from previous step, a searching algorithm is implemented to find the final bridging solution, \IE{} an ungapped path among all possiblities.
+To do so, each of the candidates is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
+As more nanopore data arrives, the score divergence increases and only the highest one would be selected for the next round.
+
+Overall, the algorithm employs a binary search strategy as shown in Algorithm~\ref{algo:binsearch}.
+Starting with the original bridge $\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_n}\rbrace$, we recursively break the target bridge in half at one of its \emph{step} $\overrightarrow{v_k}$ in-between then find the sub-paths of $\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_k}\rbrace$ and $\lbrace\overrightarrow{v_k}\,..., \overrightarrow{v_n}\rbrace$.
+Algorithm~\ref{algo:binsearch} will call Algorithm~\ref{algo:findpath} when the base condition is met, meaning the target bridge is unbreakable (no more in-between \emph{step} available).
+
+\begin{algorithm}[!hpt]
+\DontPrintSemicolon
+\KwData{Assembly graph $G\{V,E\}$}
+\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
+\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
+\SetKwFunction{BinaryBridging}{BinaryBridging} 
+\SetKwProg{Fn}{Function}{:}{}
+\Fn{\BinaryBridging{B}}{
+\tcc{search for the contig with maximum score from the step list (two ends excluded)}
+$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
+\tcc{if there is no step in-between, run Algorithm~\ref{algo:findpath} and return the result}
+\If{$M.size() \equiv 2$}{ 
+	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
+}
+\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
+$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
+$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
+\tcc{Return the join of running recursive function on two sub-bridges}
+\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
+}
+\caption{Recursive binary bridging to connect 2 anchor nodes.}
+\label{algo:binsearch}
+\end{algorithm}
+
+In Algorithm~\ref{algo:findpath}, we implement a modified stack-based Depth-First Search (DFS) using Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space.
+In which, function 
 \[
@@
 \]
-from line 3 builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance for the nanopore error rate) is reached.
-This task is implemented based on Dijkstra algorithm.
+from line 3 builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance for the nanopore error rate) is reached, similar to the Dijkstra algorithm.
 This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.
@@
 
-\begin{algorithm}[!hpt]
-\DontPrintSemicolon
-\KwData{Assembly graph $G\{V,E\}$}
-\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
-\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
-\SetKwFunction{BinaryBridging}{BinaryBridging} 
-\SetKwProg{Fn}{Function}{:}{}
-\Fn{\BinaryBridging{B}}{
-\tcc{search for the contig with maximum score from the step list (two ends excluded)}
-$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
-\tcc{if there is no step in-between, run path finding algorithm above directly and return the result}
-\If{$M.size() \equiv 2$}{ 
-	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
-}
-\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
-$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
-$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
-\tcc{Return the join of running recursive function on two sub-bridges}
-\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
-}
-\caption{Recursive binary bridging to connect 2 anchor nodes.}
-\label{algo:binsearch}
-\end{algorithm}
-
 Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover.

### 2020-09-13 plos_latex_edit.tex
reorder algorithm1&2

@@
 \subsubsection*{Path finding algorithm}
-Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them.
+\cancel{Given a bridge with 2 anchors, a path finding algorithm is used to find all candidate paths between them.
 Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
-As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
-We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search.
-
-Due to false \addnew{positive} alignments from shorter contigs to the long reads, not all of the reported step nodes \cancel{are necessary to be appeared} \addnew{would appear} in the ultimate path resolved by the bridge.
+As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.}
+\cancel{We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm to reduce the search space when using Depth-First Search.}
+
+\cancel{Due to false alignments from shorter contigs to the long reads, not all of the reported step nodes are necessary to be appeared in the ultimate path resolved by the bridge. 
 In most cases, the accumulated score of each step indicates its likelihood to be the true component of the final solution.
-For that reason, a strategy similar to binary search\cancel{ing} is employed to find a path across 2 anchors of a bridge as shown in Algorithm~\ref{algo:binsearch}.
-\addnew{Briefly, it recursively looks for sub-paths connecting pairs of step nodes in-between 2 anchors and return a final continuous path with the highest score.}
-\cancel{Before that, }We define Algorithm~\ref{algo:findpath} \addnew{as the \emph{base} sub-rountine} to \cancel{demonstrates the path finding algorithm for} \addnew{find paths between a \emph{connectable} pair of} two \addnew{step} nodes given their estimated distance.
+For that reason, a strategy similar to binary searching is employed to find a path across 2 anchors of a bridge as shown in Algorithm~2.
+Before that, we define Algorithm~1 to demonstrates the path finding algorithm for two nodes given their estimated distance.}
+
+\addnew{Given a proposed bridge with 2 anchors $B=\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_n}\rbrace$ identified from previous step, a searching algorithm is implemented to find the final bridging solution, \IE{} an ungapped path among all possiblities.
+To do so, each of the candidates is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer.
+As more nanopore data arrives, the score divergence increases and only the highest one would be selected for the next round.}
+
+\addnew{Overall, the algorithm employs a binary search strategy as shown in Algorithm~\ref{algo:binsearch}.
+Starting with the original bridge $\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_n}\rbrace$, we recursively break the target bridge in half at one of its \emph{step} $\overrightarrow{v_k}$ in-between then find the sub-paths of $\lbrace\overrightarrow{v_0}\,..., \overrightarrow{v_k}\rbrace$ and $\lbrace\overrightarrow{v_k}\,..., \overrightarrow{v_n}\rbrace$.
+Algorithm~\ref{algo:binsearch} will call Algorithm~\ref{algo:findpath} when the base condition is met, meaning the target bridge is unbreakable (no more in-between \emph{step} available).}
+
+\begin{algorithm}[!hpt]
+\DontPrintSemicolon
+\KwData{Assembly graph $G\{V,E\}$}
+\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
+\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
+\SetKwFunction{BinaryBridging}{BinaryBridging} 
+\SetKwProg{Fn}{Function}{:}{}
+\Fn{\BinaryBridging{B}}{
+\tcc{search for the contig with maximum score from the step list (two ends excluded)}
+$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
+\tcc{if there is no step in-between, run Algorithm~\ref{algo:findpath} and return the result}
+\If{$M.size() \equiv 2$}{ 
+	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
+}
+\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
+$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
+$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
+\tcc{Return the join of running recursive function on two sub-bridges}
+\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
+}
+\caption{Recursive binary bridging to connect 2 anchor nodes.}
+\label{algo:binsearch}
+\end{algorithm}
+
+\addnew{In Algorithm~\ref{algo:findpath}, we implement a modified stack-based Depth-First Search (DFS) using Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space.}
 In which, function 
@@
 \]
-from line 3 \cancel{of the algorithm's pseudo code} builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance \cancel{regarding nanopore read} \addnew{for the nanopore} error rate) is reached.
-This task is implemented based on Dijkstra algorithm.
+from line 3 builds a shortest tree rooted from $\overrightarrow{v}$, following its direction until a distance of approximately $d$ (with a tolerance for the nanopore error rate) is reached, similar to the Dijkstra algorithm.
 This tree is used on line 4 and in function $includedIn()$ on line 19 to filter out any node or edge with ending nodes that do not belong to the tree.

### 2020-09-14 plos_latex_clean.tex
more editting

@@
 \newcommand{\npgraph}{$\mathtt{npGraph}$}
-\newcommand{\lrscaf}{$\mathtt{npGraph}$}
 \newcommand{\canu}{$\mathtt{Canu}$}
@@
 \newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}
-\newcommand{\lrscarf}{$\mathtt{LRScaf}$}
+\newcommand{\lrscaf}{$\mathtt{LRScaf}$}
 
@@
 A binning step is needed to assign membership of each contig to its corresponding group. 
-
-The first step is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
+This information can aid the bridging stage later, as member contigs of a bridge are expected to appear in the same group.
+However, the criteria can be relaxed between closed groups given strong connecting evidence from long read alignments.
+
+The first step in our binning procedure is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
 To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 

### 2020-09-14 plos_latex_edit.tex
more editting

@@
 A binning step is needed to assign membership of each contig to its corresponding group. 
-
-The first step is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
+\addnew{This information can aid the bridging phase later, as member contigs of a bridge are expected to appear in the same group.
+However, the criteria can be relaxed between closed groups given strong connecting evidence from long read alignments.}
+
+The first step \addnew{in our binning procedure} is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
 To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 

### 2020-10-25 paper_clean.tex
Begin minor revision

--- 2020-09-14 plos_latex_clean.tex
@@
 \section*{Author summary}
+Hybrid genome assembly algorithms combine high accuracy short reads with error-prone long reads with the goal of generating highly contiguous assemblies with low error rates.  
+Short read sequence data is relatively inexpensive in comparison to long-read sequence data, and, moreover short-read sequence data has already been collected for many bacterial species, thus motivating development of methods wh
+ich are frugal with respect to acquisition of long-read sequence data.
+One of the attractive features of the Oxford Nanopore Technology’s sequencers is that they generate sequence data in real-time, and in principle sequencing can be stopped once enough data is acquired.
+However, there is only one previous attempt for greedy genome scaffolding of contigs in real-time, which was prone to assembly errors.
+In this paper we describe a new tool – \npgraph{} – which resolves the assembly graph in real-time as sequence is generated; coupled with assembly visualisation showing assembly graph resolution in real-time.
+We show that \npgraph{} generates completed bacterial assemblies which are as accurate as state-of-the-art batch hybrid assembly pipelines, and also provides substantial computational speed-up.
 
@@
 However, \npscarf{} ignores the rich connectivity information in the short read assembly graph, and as a result is relatively prone to mis-assembly compared to alternative methods.
-%The strategy proved to be
-%a time- and cost- effective methodology where practitioners need to generate only sufficient data for completing 
-%a draft genome.
 
@@
 
-%\begin{figure}[!hpt]
-%\centering
-%\subfloat[Merging bridges]{
-%    \label{figure:npgraph_merge}
-%	\includegraphics[width=.48\textwidth]{images/bridge_merging.pdf}
-%}
-%\hfill
-%\subfloat[Knot untangled]{
-%    \label{figure:npgraph_untangle}
-%	\includegraphics[width=.48\textwidth]{images/knot.pdf}
-%}
-%\caption{Graph resolving algorithm.
-\ref{figure:npgraph_merge} the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
-\ref{figure:npgraph_untangle} A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
-%\label{figure:npgraph_pipeline}
-%\end{figure}
-
-\begin{figure}[!hpt]
-\centering
-\includegraphics[width=\textwidth]{images/Fig1.eps}
-\caption{Graph resolving algorithm.
-(a) the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
-(b) A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
-\label{figure:npgraph_pipeline}
-\end{figure}
-
 \npgraph{} aligns long reads to the contigs in the assembly graph. When a long read is aligned
@@
 the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
-
-\begin{figure}[!hpt]
-\centering
-\includegraphics[width=\textwidth]{images/Fig2.eps}
-\caption{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}).
-The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}).
-From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
-\label{figure:npgraph_gui}
-\end{figure}
 
@@
  define a customised metric which is simple and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage.
-%The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count).
 The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.
@@
 
-% After identifying the bins, we implemented a graph traversal to assign more unique nodes to them, given the graph topology as well as statistics calculated by length and coverage of each contigs. 
 Independent from the contigs clustering in the pre-processing step, additional evidence of nodes' uniqueness can be acquired using the long reads during the assembly process.
@@
 On the other hand, external binning tools such as MetaBAT~\cite{Kang2015metabat}, maxbin~\cite{Wu2014maxbin} can be employed in \npgraph{} as well.
-%If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT.
-By that, each line of the file would be:
-%$
-%\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
-%$
-%where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
+
 \subsubsection*{Multiplicity estimation}
@@
 A bridge is known as fully complete (level 4) if and only if there is a unique path connecting its two anchor nodes from two ends.
-
-% \begin{figure}[!hpt]
-% \centering
-% \includegraphics[width=.8\textwidth]{images/bridge_merging.pdf}
-% \caption[Example of bridge merging progressively]{Bridge merging progressively in real-time.
-Sequencing long reads induce alignments to the contigs where new bridges are created respectively.
-Bridges sharing same anchors can be merged together to form the ultimate, more comprehensive bridge (with more step nodes and better approximation of spans between them).}
-% \label{figure:npgraph_merging}
-% \end{figure}
 
@@
 }
-\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
+\tcc{break the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
 $BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
 $BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
-\tcc{Return the join of running recursive function on two sub-bridges}
+\tcc{recursively invoke the procedure and join the results together}
 \Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
@@
 A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21).
-A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.
-
-Note that the $length()$ functions for node and edge are totally different.
-While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges).
-For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.
+Another threshold for the maximum traversing depth is set and heuristic cut-off can be used to preven exceptional combinatorial explosion when traversing extremely complex graph components.
+
+It worths noting that from the pseudo code in Algorithm~\ref{algo:findpath}, despite of identical name,, procedure $length()$ used for nodes are different than for edges.
+The former would return the contig length while the latter measure the overlap or distance between a pair of contigs thus can be negative or positive respectively.
+From De Bruijin graph for instance, all edges have same the length value of $-k$.
+In \npgraph{}'s algorithm, an edge's length can vary as we allow additional connection types on top of the original \spades{} assembly graph input.
 
@@
 The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications.
-
-\begin{figure}[!hpt]
-\centering
- \includegraphics[width=\textwidth]{images/Fig4.eps}
-\caption{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
-The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
-\label{figure:npgraph_graphview}
-\end{figure}
 
@@
 These edges are defined as branching edges which stop straight paths from further extending.
-
-\begin{figure}[!hpt]
-\centering
-\includegraphics[width=.6\textwidth]{images/Fig5.eps}
-\caption{Example of graph decomposition into longest straight paths.
-Branching edges are masked out (faded) leaving only straight paths (bold) to report.
-There would be 3 contigs extracted by traversing along the straight paths here.}
-\label{figure:npgraph_decompose}
-\end{figure}
 
@@
 \subsection*{Hybrid assembly for real data sets}
-%The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.  %%CAN WE SUPPORT BETTER
-%Also, considering the potential for performance bias of \unicycler{} on its own test sets, we collected real-life sample for further comparison of \unicycler and \npgraph.
 A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
@@
 Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
-Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (
-Table~\ref{tab:npgraph_real}) 
+Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (Table~\ref{tab:npgraph_real})
 %shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
@@
 
-In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in S1 Fig.
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Figure S1.
 This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
@@
 Comparison to a reference
- genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (S2 Fig.).
+ genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (Figure S2).
 However, we cannot at this stage rule out genuine structural variation between the two samples .
@@
 
-%\begin{figure}[!hbt]
-%\centering
-%\subfloat[\emph{Citrobacter~freundii} CAV1374]{
-%	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
-%}
-%\hfill
-%\subfloat[\emph{Escherichia~coli} K12 MG1655]{
-%	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
-%}
-%\\
-%\subfloat[\emph{Klebsiella} 30660 NJST258]{
-%	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
-%}
-%\hfill
-%\subfloat[\emph{Klebsiella} NTUH K2044]{
-%	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
-%}
-%\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
-%\label{F:npgraph_rt}
-%\end{figure}
-
-\begin{figure}[!hbt]
-\centering
-\includegraphics[width=\textwidth]{images/Fig3.eps}
-\caption{N50 statistics of real-time assembly by \npscarf{} and \npgraph{} for 4 bacterial samples.}
-\label{F:npgraph_rt}
-\end{figure}
-
 \section*{Discussion}
@@
 To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
-%The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time while the  nanopore sequencing process is still running.
 
 By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time.
-%Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly.
-%The next section will address this utility and the interactive GUI bundled in \npgraph{}.
-
-%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
-%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps.
-In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
-%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph
-
-\section*{Conclusion}  %%COMMENT_LC seems repetitive here
+
+\section*{Conclusion}
 %npgraph: how important hybrid assembly
@@
 
-%For more information, see \nameref{S1_Appendix}.
-
-\section*{Supporting information}
-\renewcommand{\figurename}{Supporting Figure}
-\renewcommand{\tablename}{Supporting Table}
-\renewcommand\thefigure{S\arabic{figure}}    
-\setcounter{figure}{0}
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
-
-\begin{figure}[!ht]
- \includegraphics[width=\textwidth]{images/FigS1.eps}
- \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
-Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
-On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}
-\end{figure}
-
-\paragraph*{S2 Fig.}
-\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}
-
-\begin{figure}[!ht]
- \includegraphics[width=\textwidth]{images/FigS2.eps}
- \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
-The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
-\end{figure}
-
-\clearpage
-\paragraph*{S1 Table.}
-\label{S1_Table}
-Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
-
-\makeatletter
-
-\newlength\oriarrayrulewidth  
-\newcount\orilowpenalty
-\newcommand\nobreakmidrule{%
- \noalign{\global\oriarrayrulewidth\arrayrulewidth\relax
-          \global\orilowpenalty\@lowpenalty\relax  
-          \global\@lowpenalty=\numexpr-10000\relax%
-          \global\arrayrulewidth\lightrulewidth\relax}
- \hline
- \noalign{\global\@lowpenalty=\orilowpenalty\relax%
-          \global\arrayrulewidth\oriarrayrulewidth\relax}}
-
-\makeatother
-\setlength{\LTleft}{-1in}
-\setcounter{table}{0}
-
-\begin{longtable}[!hpt]{llcrrrrr}
-%\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
-%\label{supp_tab:synthetic_benchmark}\\
-\toprule
-    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
-    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
-    \hline  
-\endfirsthead
-\multicolumn{8}{c}%
-{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
-\hline
-    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
-    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
-\hline
-\endhead
-\hline \multicolumn{8}{r}{\textit{Continued on next page}} \\
-\endfoot
-\hline
-\endlastfoot
-
-\rowcolor{Gray}
-\multicolumn{8}{l}{random sequences no repeats} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & - & - & - & - & - & - \\*
-\rowcolor{Gray}
-& npScarf &  4110000 &  3  &  4000000  &  0  & 0.00  & 0.00\\*
-\rowcolor{Gray}
-& npScarf\_wag & 4109516  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
-\rowcolor{Gray}
-& npGraph-bwa & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
-\rowcolor{Gray}
-& hybridSPAdes & 4110231  &  3  & 4000077   &  0  & 0.00  &  0.07\\*
-\rowcolor{Gray}
-& Unicycler & 4110000  &  3  &  4000000  &  0  & 0.00  &  0.00\\
-\hline
-\multicolumn{8}{l}{random sequences some repeats} \\* %
-\nobreakmidrule
-& LRScaf & 4113104 & 6 & 4002298 & 0 & 0.00 & 0.00\\*
-& npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
-& npScarf\_wag & 4437094  &  7 &  2795129  &  0  &  0.00 &  1.07\\*
-& npGraph-bwa & 4110000  &  3  &  4000000  &  0 &  0.00 &  0.00\\*
-& npGraph-mm2 &  4110000 &  3  &   4000000 & 0  & 0.00  &  0.00\\*
-& hybridSPAdes & 4107566  &  3  &  3999364  &  0  & 0.02  & 0.02\\*
-& Unicycler &  4110000 &  3 & 4000000  &  0 & 0.00  &  0.00\\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{random sequences many repeats} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 4119020 & 12 & 4002117 & 0 & 0.03 & 0.79\\* 
-\rowcolor{Gray}
-& npScarf &  4316934 &  8  &  3963485  &  24  & 11.55  & 34.54\\*
-\rowcolor{Gray}
-& npScarf\_wag &  5215965 &  16  &  1515563  &  37  & 0.32  & 7.22\\*
-\rowcolor{Gray}
-& npGraph-bwa & 4110000  &  3  &  4000000  &  0  &  0.32 & 0.15\\*
-\rowcolor{Gray}
-& npGraph-mm2 &  4110000 &  3  &  4000000  &  0  & 0.32  & 0.15\\*
-\rowcolor{Gray}
-& hybridSPAdes & 4108190  &  3  &  3999621  &  0  &  0.68 &  0.15\\*
-\rowcolor{Gray}
-& Unicycler & 4110000  &  3  &  4000000  &  0  &  0.32  & 0.15  \\
-\hline
-% \pagebreak
-% \toprule
-\multicolumn{8}{l}{\emph{Acinetobacter} A1} \\* %
-\nobreakmidrule
-& LRScaf & 3896799 & 4 & 3886381 & 0 & 0.47 & 0.36\\*
-& npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
-& npScarf\_wag & 3945166  &  3  &  3906368  &  1  & 7.00  & 14.02 \\*
-& npGraph-bwa & 3918374  &  2  &  3909643  &  0 & 16.34  & 0.61 \\*
-& npGraph-mm2 & 3885898  &  2  &  3877167  & 1 & 18.05  & 1.03 \\*
-& hybridSPAdes &  3929948 &  53  &  3353679  &  0  & 35.48  & 3.22\\*
-& Unicycler & 3917745  &  2 & 3909014  & 0  & 2.50  &  0.13\\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\emph{Acinetobacter} AB30} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 4367657 & 27 & 1035967 & 13 & 30.11 & 1.42\\* 
-\rowcolor{Gray}
-& npScarf & 4512464  &  7  &  4304628  &  35  & 57.95  & 72.87\\*
-\rowcolor{Gray}
-& npScarf\_wag & 5315235  &  13  &  1267710  &  136  &  73.55 & 8.15\\*
-\rowcolor{Gray}
-& npGraph-bwa & 4335342  &  2  &  4148952  &  1  & 16.93  & 1.45\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 4335790  &  1  &  4335790  & 0   &  6.97 & 0.25\\*
-\rowcolor{Gray}
-& hybridSPAdes & 4337369  &  3  &  2701005  &  0  &  12.80 &  1.39\\*
-\rowcolor{Gray}
-& Unicycler &  4333041 &  1  &  4333041  &  1  &  6.42 &  0.53\\
-\hline
-\multicolumn{8}{l}{\ec{} K12 MG1655} \\* %
-\nobreakmidrule
-& LRScaf & 4732001 & 16 & 692794 & 7 & 3.42 & 0.58\\*
-& npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
-& npScarf\_wag &  4687952 &  3  &  4641732  &  0  & 6.55  &  1.96\\*
-& npGraph-bwa & 4641743  &  1  &  4641743  & 0  &  4.50 & 0.43 \\*
-& npGraph-mm2 & 4641820  &  1  &  4641820  &  0 &  3.88 & 0.26 \\*
-& hybridSPAdes &  4644555 &  1  &  4641036  &  0  & 0.62  & 0.09\\*
-& Unicycler & 4641650  &  1 &  4641650 &  0 & 3.43  & 0.26 \\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\ec{} O25b H4-ST131} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 5410854 & 21 & 910949 & 9 & 13.70 & 0.87\\*
-\rowcolor{Gray}
-& npScarf &  5245913 &  3  &  5095571  &  7  &  7.05 & 18.81\\*
-\rowcolor{Gray}
-& npScarf\_wag & 5292700  &  3  &  3469617  &  9  &  9.03 & 1.55\\*
-\rowcolor{Gray}
-& npGraph-bwa & 5237821  &  7  &  4049493  &  1  &  3.38 & 0.31\\*
-\rowcolor{Gray}
-& npGraph-mm2 &  5249799 &  3  &  5110117  &  0  &  2.40 & 0.15\\*
-\rowcolor{Gray}
-& hybridSPAdes & 5252762  &  8  &  4258948  &  2  &  5.43 &  0.57\\*
-\rowcolor{Gray}
-& Unicycler & 5249442  &  3  &  5109760  &  0  & 4.02 & 0.27 \\
-\hline
-% \pagebreak
-% \toprule
-\multicolumn{8}{l}{\emph{Klebsiella} 30660 NJST258 1} \\* %
-\nobreakmidrule
-& LRScaf & 5512518 & 20 & 777919 & 26 & 3.52 & 0.38\\*
-& npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
-& npScarf\_wag & 5613780  &  7  &  5268535  &  6  & 1.59  & 1.92\\*
-& npGraph-bwa & 5534843  &  8  &  5263229  &  0  & 3.15  & 0.76\\*
-& npGraph-mm2 & 5534878  &  8  &  5263264  &  0  & 2.75  & 0.74\\*
-& hybridSPAdes &  5545668 & 8   &  5545668  &  2  & 4.95  & 0.09 \\*
-& Unicycler & 5537860  &  9  &  5263196  &  0  & 1.34  & 0.51 \\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\emph{Klebsiella} MGH 78578} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 5823340 & 38 & 559414 & 7 & 5.92 & 1.27\\*
-\rowcolor{Gray}
-& npScarf &  5729304 &  5  &  5316429  &  12  & 14.90  & 20.27\\*
-\rowcolor{Gray}
-& npScarf\_wag & 5754443  &  5  &  3026286  &  16  &  8.17 & 2.56\\*
-\rowcolor{Gray}
-& npGraph-bwa &  5695801 &  7  &  5311745  &  1  & 12.65  & 1.25\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 5696302  &  6  &  5315267  &  0  &  6.06 & 0.44\\*
-\rowcolor{Gray}
-& hybridSPAdes &  5706470 &  11  &  5315273  &  1  & 3.82  &  0.67\\*
-\rowcolor{Gray}
-& Unicycler &  5694231 &  14  &  5315096  &  0  & 5.38 &  0.21\\
-\hline
-\multicolumn{8}{l}{\emph{Klebsiella} NTUH-K2044} \\* %
-\nobreakmidrule
-& LRScaf & 5470282 & 8 & 2951488 & 9 & 3.04 & 2.62\\*
-& npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
-& npScarf\_wag & 5530559  &  3  &  5249369  &  2  &  2.25 &  1.35\\*
-& npGraph-bwa & 5472629  &  2  &  5248476  & 0  & 2.52  &  0.31\\*
-& npGraph-mm2 &  5472655 &  2  &  5248503  &  0 &  1.21 &  0.26\\*
-& hybridSPAdes & 5473572  &  2  &  5248894  &  0  &  0.44 & 0.15\\*
-& Unicycler & 5472697  & 2  & 5248545  &  0 & 2.41  &  0.35\\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\emph{Mycobacterium tuberculosis} H37Rv} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 4260869 & 12 & 3215170 & 8 & 6.69 & 2.27\\*
-\rowcolor{Gray}
-& npScarf &  4498245 &  4  & 4402238   &  8  & 5.15  & 2.68\\*
-\rowcolor{Gray}
-& npScarf\_wag &  4506056 &  4  &  4410942  &  3  & 6.81  & 2.59\\*
-\rowcolor{Gray}
-& npGraph-bwa & 4411406  &  1  &  4411406  &  0  & 1.88  & 0.43\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 4411532  & 1   &  4411532  &  0  & 0.68  & 0.00\\*
-\rowcolor{Gray}
-& hybridSPAdes & 4413942  &  1  &  4410519  &  0  &  0.75 &  0.11\\*
-\rowcolor{Gray}
-& Unicycler & 4411538  &  1  &  4411538  &  0  &  2.22 &  0.34\\
-\hline
-% \pagebreak
-% \toprule
-\multicolumn{8}{l}{\emph{Saccharomyces cerevisiae} S288c} \\* %
-\nobreakmidrule
-& LRScaf & 12486884 & 214 & 254587 & 27 & 16.45 & 1.97\\*
-& npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*
-& npScarf\_wag & 12003203  &  21  &  917017  &  21  & 69.14  & 5.47 \\*
-& npGraph-bwa & 11921736  &  40  &  913090  &  3 &  38.04 &  1.94\\*
-& npGraph-mm2 & 11920984  &  38  &  913198  &  2 &  20.66 &  0.95\\*
-& hybridSPAdes &  12027533 &  45  &  770543  &  5  & 32.58  & 1.94\\*
-& Unicycler &  11847655 & 72  & 909114  &  0 & 21.81  &  1.04\\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\emph{Shigella dysenteriae}  Sd197} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 4678609 & 175 & 376897 & 26 & 3.91 & 2.35\\*
-\rowcolor{Gray}
-& npScarf &  4586075 &  173  & 36560   &  55  & 120.14  & 111.59\\*
-\rowcolor{Gray}
-& npScarf\_wag & 5462918  &  92  &  98791  &  105  &  147.48 & 79.28\\*
-\rowcolor{Gray}
-& npGraph-bwa & 4564058  &  6  &  4369264  &  5  & 80.64  & 11.16\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 4558920  &  6  &  4364264  &  7  & 75.51  & 10.98\\*
-\rowcolor{Gray}
-& hybridSPAdes &  4519131 & 23   &  821249  & 96   & 9.57  &  1.42\\*
-\rowcolor{Gray}
-& Unicycler & 4560901  & 3   &  4369231  &  0  & 11.88  & 1.05 \\
-\hline
-\multicolumn{8}{l}{\emph{Shigella sonnei} 53G} \\* %
-\nobreakmidrule
-& LRScaf & 5266645 & 128 & 429353 & 27 & 9.72 & 1.19\\*
-& npScarf &  6441461 &  20  &  1953896  &  82  & 164.02  &  219.52\\*
-& npScarf\_wag & -  &  -  &  -  &  -  & -  &  -\\*
-& npGraph-bwa & 5211544  &   4 &  4988532  & 0  & 14.53  &  0.31\\*
-& npGraph-mm2 & 5211527  &  4  &   4988519 & 0  &  8.56 &  0.17\\*
-& hybridSPAdes & 5223875  &  8  &  2195455  &  2  & 41.92  & 0.06\\*
-& Unicycler &  5220517 &  5 &  4988548 & 0  & 7.39  &  0.52\\
-\hline
-\rowcolor{Gray}
-\multicolumn{8}{l}{\emph{Streptococcus suis} BM407} \\* %
-\nobreakmidrule
-\rowcolor{Gray}
-& LRScaf & 2231488 & 10 & 683404 & 6 & 11.96 & 1.37\\*
-\rowcolor{Gray}
-& npScarf &  2183951 & 3   &  2146594  &  0  & 21.51  & 9.17\\*
-\rowcolor{Gray}
-& npScarf\_wag & 2289880  &  3  &  1493189  &  1  & 3.17  & 1.96\\*
-\rowcolor{Gray}
-& npGraph-bwa & 2154623  &  6  &  2131479  &  1  & 5.25  & 0.28\\*
-\rowcolor{Gray}
-& npGraph-mm2 & 2149876  &  6  &  2146774  &  0  & 1.44  & 0.28\\*
-\rowcolor{Gray}
-& hybridSPAdes & 2172703  &  2  &  2146237  &  0  & 6.82  &  0.09\\*
-\rowcolor{Gray}
-& Unicycler &  2170829 &   2 &  2146250  &  0  &  2.67 & 0.32 \\
-\hline
-\end{longtable}
-
 \section*{Data availability}
@@
 \section*{Acknowledgments}
+This work was supported by an ARC grant to LC and MDC (DP170102626).
+LC is funded by NHMRC CDF (GNT1130084).
+This research was supported by the use of the NeCTAR Research Cloud, by QCIF and by the University of Queensland’s Research Computing Centre (RCC).
 
 \nolinenumbers
+\pagebreak
+\section*{List of figures}
+
+\begin{figure}[!hpt]
+\centering
+%\includegraphics[width=\textwidth]{images/Fig1.eps}
+\caption{Graph resolving algorithm.
+(a) the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors.
+(b) A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
+\label{figure:npgraph_pipeline}
+\end{figure}
+
+\begin{figure}[!hpt]
+\centering
+%\includegraphics[width=\textwidth]{images/Fig2.eps}
+\caption{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}).
+The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}).
+From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
+\label{figure:npgraph_gui}
+\end{figure}
+
+\begin{figure}[!hpt]
+\centering
+ %\includegraphics[width=\textwidth]{images/Fig3.eps}
+\caption{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View.
+The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
+\label{figure:npgraph_graphview}
+\end{figure}
+
+\begin{figure}[!hpt]
+\centering
+%\includegraphics[width=.6\textwidth]{images/Fig4.eps}
+\caption{Example of graph decomposition into longest straight paths.
+Branching edges are masked out (faded) leaving only straight paths (bold) to report.
+There would be 3 contigs extracted by traversing along the straight paths here.}
+\label{figure:npgraph_decompose}
+\end{figure}
+
+\begin{figure}[!hbt]
+\centering
+%\includegraphics[width=\textwidth]{images/Fig5.eps}
+\caption{N50 statistics of real-time assembly by \npscarf{} and \npgraph{} for 4 bacterial samples.}
+\label{F:npgraph_rt}
+\end{figure}
+
+\clearpage
 

### 2020-10-26 paper_clean.tex
last edit

@@
 Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
+The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.
 
@@
 Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
-With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
+With all of the data sets tested, \unicycler{} required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
 $\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
@@
 Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
-In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
+In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$Kbp of length as ColRNAI plasmid.
 The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 

### 2020-10-26 paper_edit.tex
last edit

--- 2020-10-25 paper_clean.tex
@@
 Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
+\review{The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.}
 
@@
 Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
-With all of the data sets tested, \unicycler required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
+With all of the data sets tested, \review{\unicycler{} required} the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
 $\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
@@
 Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
-In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2Kbp$ of length as ColRNAI plasmid.
+In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$\review{Kbp} of length as ColRNAI plasmid.
 The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 

### 2020-11-20 paper_clean.tex

@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.

### 2020-11-22 paper_clean.tex

@@
 \emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
-CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
+CAV1741 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
  & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\

### 2020-11-22 Revision_1/plos_latex_edit.tex

--- 2020-09-14 plos_latex_edit.tex
@@
 A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21).
-A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.
-
-Note that the $length()$ functions for node and edge are totally different.
+\cancel{A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.}
+\addnew{Another threshold for the maximum traversing depth is set and heuristic cut-off can be used to preven exceptional combinatorial explosion when traversing extremely complex graph components.}
+
+\cancel{Note that the $length()$ functions for node and edge are totally different.
 While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges).
-For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.
+For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.}
+\addnew{It worths noting that from the pseudo code in Algorithm~\ref{algo:findpath}, despite of identical name, procedure $length()$ used for nodes are different than for edges.
+The former would return the contig length while the latter measure the overlap or distance between a pair of contigs thus can be negative or positive respectively.
+From De Bruijin graph for instance, all edges have same the length value of $-k$.
+In \npgraph{}'s algorithm, an edge's length can vary as we allow additional connection types on top of the original \spades{} assembly graph input.}
 

### 2020-11-22 paper_edit.tex

@@
 \emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
-CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
+CAV\review{1741} & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
  & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\

### 2020-11-23 paper_clean.tex
done

@@
 \pagebreak
-\section*{List of figures}
+\section*{List of legends}
 
@@
 \end{figure}
+
+\paragraph*{Fig S1}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+
+\paragraph*{Fig S2}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+
+\paragraph*{Table S1}
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
 

### 2020-11-23 paper_edit.tex
done

@@
 \pagebreak
-\section*{List of figures}
+\section*{List of \review{legends}}
 
@@
 \end{figure}
+
+\review{
+\paragraph*{Fig S1}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+}
+
+\review{
+\paragraph*{Fig S2}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+}
+
+\review{
+\paragraph*{Table S1}
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+}
 

### 2020-11-23 paper_edit.tex
add supporting info legends

--- 2020-11-22 paper_edit.tex
@@
 \end{thebibliography}
+
+\clearpage
+\section*{\review{Supporting information}}
+
+\paragraph*{\review{Fig S1}}
+\review{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}
+
+\paragraph*{\review{Fig S2}}
+\review{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
+
+\paragraph*{\review{Table S1}}
+\review{Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
+
 \end{document}

### 2020-12-18 PCOMPBIOL-D-20-00393/paper_clean.tex
final change

--- 2020-11-22 paper_clean.tex
@@
 \usepackage[normalem]{ulem}
+
 %% npGraph
@@
 \newcommand{\EG}{\emph{e.g.}}
-\newcommand{\review}[1]{\textcolor{red}{#1}}
 
@@
 
+%% For tracked changes
+\usepackage{changes}
+\definechangesauthor[name={Son Nguyen}, color=red]{SN}
+\colorlet{Changes@Color}{red}
 %% End preloads
@@
 \textbf{1} Institute for Molecular Bioscience, the University of Queensland, 
-St Lucia, Brisbane, QLD 4072 Australia
+St Lucia, Brisbane, Australia
 \\
-\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia
+\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, Australia
 \\
-\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
+\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, Australia
 \\
-\textbf{4} Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
+\textbf{4} Department of Infectious Disease, Imperial College London, London, UK
 \bigskip
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-*s.hoangnguyen@imb.uq.edu.au,l.coin@imb.uq.edu.au
+*SHN: s.hoangnguyen@imb.uq.edu.au, LC: l.coin@imb.uq.edu.au
 
@@
 In general, the bridging algorithm used to determine the best path is a combination of progressive merging, accumulated scoring and decision making modules.
-It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Figure~\ref{figure:npgraph_pipeline}(a).
+It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Fig~\ref{figure:npgraph_pipeline}A.
 A set of candidate paths are listed and the best one can be selected amongst them given enough evidence. 
-The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\ref{figure:npgraph_pipeline}(b)).
+The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (Fig~\ref{figure:npgraph_pipeline}B).
 
 We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
-in real-time (Figure~\ref{figure:npgraph_gui}). 
+in real-time (Fig~\ref{figure:npgraph_gui}). 
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
@@
 At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
-In an example from Figure~\ref{figure:npgraph_pipeline}(a), bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+In an example from Fig~\ref{figure:npgraph_pipeline}A, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
 Each of the steps therefore is assigned a weighing score based on its alignment quality.
@@
 
-Figure~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
+Fig~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
 The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
@@
 A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if and only if each of every edges along the path $e_i, \forall i=1,\ldots,k$ is the only option to traverse from either $v_{i-1}$ or $v_i$, giving the transition rule.
-To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}.
+To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Fig~\ref{figure:npgraph_decompose}.
 These edges are defined as branching edges which stop straight paths from further extending.
@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9~\cite{Qin2019} and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~\cite{Wick2017unicycler} .
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
@@
 We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
-This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_pipeline}(a)).
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Fig~\ref{figure:npgraph_pipeline}A).
 However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
@@
 
-In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Figure S1.
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in S1 Fig.
 This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
@@
 Comparison to a reference
- genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (Figure S2).
+ genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (S2 Fig).
 However, we cannot at this stage rule out genuine structural variation between the two samples .
@@
 \subsection*{Assembly performance on streaming data}
-In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Figure~\ref{F:npgraph_rt}) .This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
+In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Fig~\ref{F:npgraph_rt}).
+This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
 \npscarf{} converged more quickly than \npgraph{}, due to the fact that it is able to build bridges with only 1 spanning long-read, whereas \npgraph{} requires 3 reads.
@@
 In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
+S1 Data provides the results in detail and were used to generate Fig~\ref{F:npgraph_rt}.
 
@@
 
-\section*{Data availability}
-All data used for benchmarking were from public sources.
-The synthetic data was downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}.
-The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.
-
 \section*{Acknowledgments}
-This work was supported by an ARC grant to LC and MDC (DP170102626).
-LC is funded by NHMRC CDF (GNT1130084).
 This research was supported by the use of the NeCTAR Research Cloud, by QCIF and by the University of Queensland’s Research Computing Centre (RCC).
@@
 \end{thebibliography}
+
+\clearpage
+\section*{Supporting information}
+
+\paragraph*{S1 Fig}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+
+\paragraph*{S2 Fig}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+
+\paragraph*{S1 Table}
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+
+\paragraph*{S1 Data}
+Spreadsheet contains data used to generate Fig 5.
+
 \end{document}

### 2020-12-18 paper_edit.tex
final change

--- 2020-11-22 paper_edit.tex
@@
 \textbf{1} Institute for Molecular Bioscience, the University of Queensland, 
-St Lucia, Brisbane, QLD 4072 Australia
+St Lucia, Brisbane, \deleted[id=SN]{QLD 4072} Australia
 \\
-\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia
+\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, \deleted[id=SN]{3010,} Australia
 \\
-\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
+\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, \deleted[id=SN]{3010,} Australia
 \\
-\textbf{4} Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
+\textbf{4} Department of Infectious Disease, Imperial College London, London, \deleted[id=SN]{W2 1NY,} UK
 \bigskip
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-*s.hoangnguyen@imb.uq.edu.au,l.coin@imb.uq.edu.au
+*\added[id=SN]{SHN:} s.hoangnguyen@imb.uq.edu.au, \added[id=SN]{LC:} l.coin@imb.uq.edu.au
 
@@
 In general, the bridging algorithm used to determine the best path is a combination of progressive merging, accumulated scoring and decision making modules.
-It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Figure~\ref{figure:npgraph_pipeline}(a).
+It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}.
 A set of candidate paths are listed and the best one can be selected amongst them given enough evidence. 
-The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\ref{figure:npgraph_pipeline}(b)).
+The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\added[id=SN]{Fig~}\ref{figure:npgraph_pipeline}\replaced[id=SN]{B}{(b)}).
 
 We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
-in real-time (Figure~\ref{figure:npgraph_gui}). 
+in real-time (Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_gui}). 
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
@@
 At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
-In an example from Figure~\ref{figure:npgraph_pipeline}(a), bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+In an example from Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
 Each of the steps therefore is assigned a weighing score based on its alignment quality.
@@
 
-Figure~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
+Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
 The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
@@
 A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if and only if each of every edges along the path $e_i, \forall i=1,\ldots,k$ is the only option to traverse from either $v_{i-1}$ or $v_i$, giving the transition rule.
-To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Figure~\ref{figure:npgraph_decompose}.
+To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_decompose}.
 These edges are defined as branching edges which stop straight paths from further extending.
@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 \added[id=SN]{\cite{Qin2019}} and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
@@
 Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
-\review{The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.}
+The nanopore read depth for each data set is approximately 65-fold coverage even though much less data were needed to generate these final results by the aforementioned hybrid methods.
 
@@
 We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
-This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Figure~\ref{figure:npgraph_pipeline}(a)).
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}).
 However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
@@
 Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
-With all of the data sets tested, \review{\unicycler{} required} the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
+With all of the data sets tested, \unicycler{} required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
 $\mathtt{hybridSPAdes}$ reported decent results with high fidelity at base level.
@@
 \emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
-CAV\review{1741} & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
+CAV1741 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
  & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
@@
 Five out of six identical replicons could be confirmed as plasmids based on the occurence of  origin of replication sequences from  the PlasmidFinder database.
-In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$\review{Kbp} of length as ColRNAI plasmid.
+In detail, two megaplasmids (longer than $100$Kbp) were classified as IncFIB while the other two mid-size replicons, $85.6$Kbp and $43.6$Kbp, were incL and repA respectively, leaving the shortest one with $2$Kbp of length as ColRNAI plasmid.
 The remaining circular sequence without any hits to the database was $3.2$Kbp long suggesting that it could be phage or a cryptic plasmid. 
@@
 
-In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Figure S1.
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in \replaced[id=SN]{S1 Fig}{Figure S1}.
 This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
@@
 Comparison to a reference
- genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (Figure S2).
+ genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (\replaced[id=SN]{S2 Fig}{Figure S2}).
 However, we cannot at this stage rule out genuine structural variation between the two samples .
@@
 \subsection*{Assembly performance on streaming data}
-In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Figure~\ref{F:npgraph_rt}) .This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
+In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Fig\deleted[id=SN]{ure}~\ref{F:npgraph_rt}).
+This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
 \npscarf{} converged more quickly than \npgraph{}, due to the fact that it is able to build bridges with only 1 spanning long-read, whereas \npgraph{} requires 3 reads.
@@
 In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
+\added[id=SN]{S1 Data provides the results in detail and were used to generate Fig~\ref{F:npgraph_rt}.}
 
@@
 
-\section*{Data availability}
-All data used for benchmarking were from public sources.
+\section*{\deleted[id=SN]{Data availability}}
+\deleted[id=SN]{All data used for benchmarking were from public sources.
 The synthetic data was downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}.
-The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.
-
+The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.}
 \section*{Acknowledgments}
-This work was supported by an ARC grant to LC and MDC (DP170102626).
-LC is funded by NHMRC CDF (GNT1130084).
+\deleted[id=SN]{This work was supported by an ARC grant to LC and MDC (DP170102626).  LC is funded by NHMRC CDF (GNT1130084).}  
 This research was supported by the use of the NeCTAR Research Cloud, by QCIF and by the University of Queensland’s Research Computing Centre (RCC).
@@
 \end{thebibliography}
+
+\clearpage
+\section*{Supporting information}
+
+\paragraph*{\replaced[id=SN]{S1 Fig}{Fig S1}}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+
+\paragraph*{\replaced[id=SN]{S2 Fig}{Fig S2}}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+
+\paragraph*{\replaced[id=SN]{S1 Table}{Table S1}}
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+
+\paragraph*{\replaced[id=SN]{S1 Data}{Fig5.csv}}
+Spreadsheet contains data used to generate Fig 5.
+
 \end{document}

### 2021-01-04 paper_clean.tex
add supporting info legends
sick

--- 2020-11-22 paper_clean.tex
@@
 %% END MACROS SECTION
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
+
 %% npGraph
@@
 
+\bibitem{Qin2019}
+Qin M, Wu S, Li A, Zhao F, Feng H, Ding L, Ruan J.
+\newblock LRScaf: improving draft genomes using long noisy reads.
+\newblock BMC Genomics. 2019;20(1):955
+
 \bibitem{Wick2017unicycler}
@@
 
-\bibitem{Qin2019}
-Qin M, Wu S, Li A, Zhao F, Feng H, Ding L, Ruan J.
-\newblock LRScaf: improving draft genomes using long noisy reads.
-\newblock BMC Genomics. 2019;20(1):955
+\end{thebibliography}
 
-\end{thebibliography}
+\clearpage
+\section*{Supporting information}
+
+\paragraph*{S1 Fig.}
+Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
+Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs.
+On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
+
+\paragraph*{S2 Fig.}
+Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
+The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
+
+\paragraph*{S1 Table.}
+Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
+
+\paragraph*{S1 Data.}
+Spreadsheet contains data used to generate Fig 5.
+
 \end{document}

### 2021-01-04 paper_edit.tex
sick

@@
 %% END MACROS SECTION
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
 
@@
 \textbf{1} Institute for Molecular Bioscience, the University of Queensland, 
-St Lucia, Brisbane, \deleted[id=SN]{QLD 4072} Australia
+St Lucia, Brisbane, Australia
 \\
-\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, \deleted[id=SN]{3010,} Australia
+\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, Australia
 \\
-\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, \deleted[id=SN]{3010,} Australia
+\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, Australia
 \\
-\textbf{4} Department of Infectious Disease, Imperial College London, London, \deleted[id=SN]{W2 1NY,} UK
+\textbf{4} Department of Infectious Disease, Imperial College London, London, UK
 \bigskip
@@
 % Use the asterisk to denote corresponding authorship and provide email address in note below.
-*\added[id=SN]{SHN:} s.hoangnguyen@imb.uq.edu.au, \added[id=SN]{LC:} l.coin@imb.uq.edu.au
+*SHN: s.hoangnguyen@imb.uq.edu.au, LC: l.coin@imb.uq.edu.au
 
@@
 In general, the bridging algorithm used to determine the best path is a combination of progressive merging, accumulated scoring and decision making modules.
-It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}.
+It operates on each pair of unique contigs, or \emph{anchors}, by using a \emph{bridge} data structure maintaining 2 anchors and a list of \emph{steps} in-between as shown in Fig~\ref{figure:npgraph_pipeline}A.
 A set of candidate paths are listed and the best one can be selected amongst them given enough evidence. 
-The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (\added[id=SN]{Fig~}\ref{figure:npgraph_pipeline}\replaced[id=SN]{B}{(b)}).
+The de Bruijin graph is subsequently simplified when the bridge is replaced by a single edge representing the best path (Fig~\ref{figure:npgraph_pipeline}B).
 
 We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
-in real-time (Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_gui}). 
+in real-time (Fig~\ref{figure:npgraph_gui}). 
 In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
@@
 At early stages (level 1 or 2), a bridge is constructed progressively by alignments from long reads that spanning its corresponding anchor(s).
-In an example from Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
+In an example from Fig~\ref{figure:npgraph_pipeline}A, bridges from a certain anchor (highlighted in red) are created by extracting appropriate alignments from incoming long reads to the contigs.
 Each of the steps therefore is assigned a weighing score based on its alignment quality.
@@
 
-Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
+Fig~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
 The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
@@
 A path $p=\{v_0,e_1,v_1,\ldots,v_{k-1},e_k,v_k\}$ of size $k$ is considered as straight if and only if each of every edges along the path $e_i, \forall i=1,\ldots,k$ is the only option to traverse from either $v_{i-1}$ or $v_i$, giving the transition rule.
-To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_decompose}.
+To decompose the graph, the tool simply mask out all incoming/outgoing edges rooted from any node with in/out degree greater than 1 as demonstrated in Fig~\ref{figure:npgraph_decompose}.
 These edges are defined as branching edges which stop straight paths from further extending.
@@
 \subsection*{Evaluation using synthetic data}
-To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9 \added[id=SN]{\cite{Qin2019}} and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} .
+To evaluate the performance of the method, \npgraph{} was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), \lrscaf{} version 1.1.9~[\replaced[id=SN]{14}{25}] and \unicycler{} version 0.4.6 using \unicycler{}`s synthetic data set~[\replaced[id=SN]{15}{14}].
 The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
-We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.
+We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~[\replaced[id=SN]{16}{15}].
 
@@
 
-To align the long reads to the assembly graph components, both \bwa{}~\cite{Li2013} or \minimap{}~\cite{Li2016} were used in conjunction with \npgraph{}.
+To align the long reads to the assembly graph components, both \bwa{}~[\replaced[id=SN]{17}{16}] or \minimap{}~[\replaced[id=SN]{18}{17}] were used in conjunction with \npgraph{}.
 These two methods were chosen due to their proven efficiency and compatibility with streaming data.
@@
 We observed a slightly higher error rate (comprising the sum of mismatches and indels per 100kb) using \bwa{} in comparison to \minimap{} for all simulations in Table~\ref{table:npgraph_compare}.
-This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Fig\deleted[id=SN]{ure}~\ref{figure:npgraph_pipeline}\replaced[id=SN]{A}{(a)}).
+This is due to the fact that bridging paths induced using \bwa{} were slightly less accurate due to more noise from the smaller \emph{steps} in-between (Fig~\ref{figure:npgraph_pipeline}A).
 However, under almost circumstances, using either aligner resulted in final assemblies with comparable qualities.
@@
 
-Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~\cite{Brudno2003glocal} with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
+Amongst all assemblers, \unicycler{} applies an algorithm based on semi-global (or glocal) alignments~[\replaced[id=SN]{19}{18}] with the consensus long reads generated with the $\mathtt{SeqAn}$ library.
 With all of the data sets tested, \unicycler{} required the most computational resources, but it also returned  fewer mis-assemblies than the other approaches with a comparable rate of error (indels and mismatches) to \npgraph{}.
@@
 \subsection*{Hybrid assembly for real data sets}
-A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
+A number of sequencing data sets from \emph{in vitro} bacterial samples~[\replaced[id=SN]{20}{19}] were used to further explore differences in performance between \npgraph{} and \unicycler{}.
 The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
 Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
-Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (Table~\ref{tab:npgraph_real})
+Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~[\replaced[id=SN]{21}{20}] mappings to obtain an evaluation on the accuracy and completeness of the assemblies (Table~\ref{tab:npgraph_real})
 %shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
@@
 
-In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in \replaced[id=SN]{S1 Fig}{Figure S1}.
+In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in S1 Fig.
 This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly.
@@
 Comparison to a reference
- genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (\replaced[id=SN]{S2 Fig}{Figure S2}).
+ genome from the same bacteria strain (GenBank ID: CP011581.1~[\replaced[id=SN]{22}{21}]), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (S2 Fig).
 However, we cannot at this stage rule out genuine structural variation between the two samples .
@@
 \subsection*{Assembly performance on streaming data}
-In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Fig\deleted[id=SN]{ure}~\ref{F:npgraph_rt}).
+In order to investigate the rate at which the two streaming hybrid assembly algorithms completed bacterial assemblies, we plot the N50 as a function of long-read coverage on the 4 datasets described in the previous section ( Fig~\ref{F:npgraph_rt}).
 This revealed that \npgraph{} and \npscarf{} both converge to the same ultimate completeness but at different rates.
@@
 In addition, at the end of the streaming when the sequencing is finished, \npgraph{} will try for the last time to connect bridges with less than 3 supporting reads which are otherwise not part of conflicting bridges.
-\added[id=SN]{S1 Data provides the results in detail and were used to generate Fig~\ref{F:npgraph_rt}.}
+S1 Data provides the results in detail and were used to generate Fig~\ref{F:npgraph_rt}.
 
@@
 % \end{itemize}
-Streaming assembly methods have been proven to be useful in saving time and resources compared to conventional batch algorithms with examples including \EG{} $\mathtt{Faucet}$~\cite{Rozov2017faucet} and \npscarf{}~\cite{Cao2017scaffolding}.
+Streaming assembly methods have been proven to be useful in saving time and resources compared to conventional batch algorithms with examples including \EG{} $\mathtt{Faucet}$~[\replaced[id=SN]{23}{22}] and \npscarf{}~\cite{Cao2017scaffolding}.
 The first method allows the assembly graph to be constructed incrementally as long as reads are retrieved and processed.
@@
 
-However, due to the greedy bridging approach of the contig-based streaming algorithm, \npscarf{}`s results can suffer from mis-assemblies~\cite{Wick2017unicycler,Giordano2017}. 
+However, due to the greedy bridging approach of the contig-based streaming algorithm, \npscarf{}`s results can suffer from mis-assemblies~[\replaced[id=SN]{15,24}{14,23}]. 
 A default setting was optimized for microbial genomes input but cannot fit for all data from various experiments in practice.
@@
 
-Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} as well as \unicycler{} \cite{Wick2017unicycler}. 
+Hybrid assembler using nanopore data to resolve the graph has been implemented in $\mathtt{hybridSPAdes}$ \cite{AntipovKM2015} as well as \unicycler{}~[\replaced[id=SN]{15}{14}]. 
 The available tools employ batch-mode algorithms on the whole long-read data set to generate the final genome assembly. 
 The \spades{} hybrid assembly module, from its first step, exhaustively looks for the most likely paths (with minimum edit distance) on the graph for each of the long read given but only ones supported by at least two reads are retained.
-In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~\cite{Prjibelski2014}, for repeat resolution by step-by-step expansion, before output the final assembly.
+In the next step, these paths will be subjected to a decision-rule algorithm, namely $\mathtt{exSPAnder}$~[\replaced[id=SN]{25}{24}], for repeat resolution by step-by-step expansion, before output the final assembly.
 On the other hand, \unicycler{}'s hybrid assembler will initially generate a consensus long read for each of the bridge from the batch data. 
@@
 
-\section*{\deleted[id=SN]{Data availability}}
-\deleted[id=SN]{All data used for benchmarking were from public sources.
-The synthetic data was downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}.
-The real bacterial sequencing data was from NCBI under project accession number PRJNA353060.}
 \section*{Acknowledgments}
-\deleted[id=SN]{This work was supported by an ARC grant to LC and MDC (DP170102626).  LC is funded by NHMRC CDF (GNT1130084).}  
 This research was supported by the use of the NeCTAR Research Cloud, by QCIF and by the University of Queensland’s Research Computing Centre (RCC).
@@
 
-\bibitem{Qin2019}
-Qin M, Wu S, Li A, Zhao F, Feng H, Ding L, Ruan J.
-\newblock LRScaf: improving draft genomes using long noisy reads.
-\newblock BMC Genomics. 2019;20(1):955
-
 \end{thebibliography}
@@
 
-\paragraph*{\replaced[id=SN]{S1 Fig}{Fig S1}}
+\paragraph*{S1 Fig\added[id=SN]{.}}
 Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.
@@
 
-\paragraph*{\replaced[id=SN]{S2 Fig}{Fig S2}}
+\paragraph*{S2 Fig\added[id=SN]{.}}
 Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}.
@@
 
-\paragraph*{\replaced[id=SN]{S1 Table}{Table S1}}
+\paragraph*{S1 Table\added[id=SN]{.}}
 Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
 
-\paragraph*{\replaced[id=SN]{S1 Data}{Fig5.csv}}
+\paragraph*{S1 Data\added[id=SN]{.}}
 Spreadsheet contains data used to generate Fig 5.
